### 2014-02-20 mainsequence_morph.tex
Adding bbl files

\documentclass{emulateapj}
%\documentclass[manuscript]{aastex}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{amsmath}
\bibliographystyle{apj}

\shorttitle{STAR-FORMING MAIN SEQUENCE GALAXIES AND THEIR MORPHOLOGY}
\shortauthors{WILLETT ET AL.}

\begin{document}

\title{The dependence of spiral disk morphology on the mass-star formation relation}

\author{Kyle Willett\altaffilmark{1}, Kevin Schawinski\altaffilmark{2}, etc.}

\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
\altaffiltext{2}{Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 16, CH-8093, Z\"urich, Switzerland}

%%%%%%%%%%%%
%%% ABSTRACT
%%%%%%%%%%%%

\begin{abstract}
We measure the mass-star formation relation in disk galaxies at $z<0.05$, using Galaxy Zoo morphologies to separate disk galaxies by their kiloparsec-scale spiral structure. We examine the number of arms, their average pitch angle, and the presence of a galactic bar, and show that both the slope and dispersion of the SFR-$M_{\rm stellar}$ relation is constant when varying all the above parameters. We interpret this as evidence that the spiral arms, which are imperfect reflections of the galaxy's current gravitational potential, are either fully independent of the basic quenching relation or are completely overwhelmed by the combination of outflows and feedback. The arrangement of the star formation can be changed (as demonstrated by the filling factor of the disk), but the system \emph{as a whole} regulates itself. 
\end{abstract}

\keywords{galaxies:mergers}

%%%%%%%%%%%%
%%% INTRODUCTION
%%%%%%%%%%%%

\section{Introduction} \label{sec-intro}

%ORIGINAL TEXT %Mass-SFR relationship is tight, universal, and redshift-dependent (many citations). We think this is the result of the balancing of cosmological inflows of gas from the halo and feedback mechanism \citep{bou10,lil13}.

%NEW, COHERENT INTRO (hi there, @overheardonastroph!)
Observations at a range of redshifts have established that the star formation rate (SFR) of a galaxy is strongly correlated to its stellar mass ($M_{\rm stellar}$). This `main sequence' of star formation (MS) is nearly linear and at least at low redshift, has remarkably small scatter (refs). Recent observations of star-forming galaxies at high redshifts show that this main sequence remains out to high redshift with the normalisation of the main sequence shifting up so that galaxies of the same stellar mass have a higher SFR at high redshift (refs). The main sequence has been interpreted by \citet{bou10} and \citet{lil13} as the result of the balancing of inflows of cosmological gas and outflows due the feedback. Galaxies self-regulate to remain in a state of homeostasis as they convert baryons from gas to stars.

As star-forming galaxies exhibit a wide range of physical appearances in optical images, we can ask the natural question of whether the specifics of this physical appearance, and its underlying dynamical processes, have any effect on this homeostasis and therefore the galaxy's location relative to the SFR-$M_{\rm stellar}$ relation. If the details of a galaxy's physical appearance are correlated with position relative to the main sequence, then the dynamical processes that give rise to them -- such as bar formation and spiral arm pitch angle -- are a fundamental aspect of the galaxy's regulatory mechanism. If on the other hand they are not correlated, then there are two options: either they are simply not relevant, or the regulatory mechanism overcomes them in virtually all circumstances. This would speak to the strength of the regulator.

In this paper, we use the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with the largest database of visual classifications of galaxy structure and morphology ever assembled from the Galaxy Zoo citizen science project \citep{lin08,lin11,wil13} to test whether galaxy structure affects their star formation properties.

%%%%%%%%%%%%
%%% Data
%%%%%%%%%%%%

\section{Data} \label{sec-data}

Description of Galaxy Zoo 2 \citep{wil13}. Stellar masses and SFR from MPA-JHU \citep{kau03a,bri04}. Select starforming galaxies using BPT diagram \citep{bal81} and the standard \citet{kau03} demarcation line. Spiral galaxies are selected according to the following vote and vote thresholds.

Figure: example images of: 1-5 arms, plus arm tightness, plus barred vs. non-barred.

Table~\ref{tbl-fits}: fits for all star forming galaxies and then split by different morphologies

\begin{table}
 \begin{tabular}{@{}lrcl}
 \hline
\multicolumn{1}{c}{Sample} &
\multicolumn{1}{c}{$\alpha$} &
\multicolumn{1}{c}{$\beta$} &
\multicolumn{1}{c}{$\sigma$} 
\\ 
\\ 
\hline
\hline						
%Main (original + extra)       & 273,783 & 43  & 17.0   \\     % 43.1
All star-forming galaxies  & & & \\
\hline
$N_{arms} = 1$ & & & \\
$N_{arms} = 2$ & & & \\
$N_{arms} = 3$ & & & \\
$N_{arms} = 4$ & & & \\
$N_{arms} = 5$ & & & \\
$N_{arms} = ?$ & & & \\
\hline
Tight & & & \\
Medium & & & \\
Loose & & & \\
\hline
Barred & & & \\
Unbarred & & & \\
\hline
 \end{tabular}
 \caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies. \label{tbl-fits}}
\end{table}

Figure~\ref{fig-number}: $M_\star-SFR$ for arm multiplicity \\
Figure~\ref{fig-winding}: $M_\star-SFR$ for pitch angle ($\phi$) \\
Figure~\ref{fig-bar}: $M_\star-SFR$ for barred vs unbarred \\

How many galaxies are there in the total sample? What is the mass, color, and redshift range?

%%%%%%%%%%%%
%%% RESULTS
%%%%%%%%%%%%

\section{Results} \label{sec-results}

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{ms_arms_number.pdf}
\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the number of spiral arms. Both stellar mass and SFR are taken from the MPA-JHU catalog for DR7. 
\label{fig-number}}
\end{figure*}

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{ms_arms_winding.pdf}
\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the relative pitch angle of the spiral arms. 
\label{fig-winding}}
\end{figure*}

\begin{figure*}
\includegraphics[angle=0,width=7.0in]{ms_bar.pdf}
\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the detection of a galactic bar. 
\label{fig-bar}}
\end{figure*}

List the fits to slope and intercept for the linear version of the M-SFR relation. Also look at dispersion.

%%%%%%%%%%%%
%%% DISCUSSION
%%%%%%%%%%%%

\section{Discussion}\label{sec-discussion}

There is no significant difference between any of the morphological categories explored. Statistical test for how not different the categories are.

This is interpreted as evidence that the regulation of the star formation rate is independent of the details of galactic structure as traced by the dynamics of the spiral arms.

Conditional statements: if the situation above is true, then the following must apply.

Point that has not been made before; self-regulated systems where you can move parts around, but the total amount must be conserved. Process as a result cannot be simply regulated locally - the whole system must know about the rate of regulation. What does this say about the minimum lifetime of the features as a dynamical timescale $\tau_{dyn}$?

Connection between galaxy structure and quenching efficiency - \citet{oma14} found a simple dependence on $B/T$ for SDSS DR7 data.

%%%%%%%%%%%%
%%% ACKNOWLEDGMENTS
%%%%%%%%%%%%

\acknowledgments

The data in this paper are the result of the efforts of the Galaxy~Zoo volunteers, without whom none of this work would be possible. Their efforts are individually acknowledged at \url{http://authors.galaxyzoo.org}. Please contact the authors to request access to research materials discussed in this paper.

This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05}. 
%The development of Galaxy Zoo 2 was supported by The Leverhulme Trust. KWW and LFF would like to acknowledge support from the US National Science Foundation under grant DRL-0941610. CJL acknowledges support from the Science and Technology Facilities Council (STFC) Science in Society program. KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1. TM acknowledges funding from the STFC ST/J500665/1. RCN was partially supported by STFC grant ST/K00090X/1. BDS acknowledges support from Worcester College, Oxford, and from the Oxford Martin School program on computational cosmology.

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS website is \url{http://www.sdss.org/}.

The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions. The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.

\clearpage

%%%%%%%%%%%%
%%% BIBLIOGRAPHY
%%%%%%%%%%%%

\bibliography{kwrefs}

\end{document}

### 2014-02-20 mainsequence_morph.tex
Changed path to figures

@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{ms_arms_number.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/ms_arms_number.pdf}
 \caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the number of spiral arms. Both stellar mass and SFR are taken from the MPA-JHU catalog for DR7. 
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{ms_arms_winding.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding.pdf}
 \caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the relative pitch angle of the spiral arms. 
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{ms_bar.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
 \caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the detection of a galactic bar. 

### 2014-02-20 gz_mainsequence.py

@@ -12,6 +12,7 @@ plt.ion()
 
 gz_path = '/Users/willettk/Astronomy/Research/GalaxyZoo'
 ms_path = '%s/gz_mainsequence' % gz_path
+fig_path = '%s/gz_mainsequence/figures' % gz_path
 fits_path = '%s/fits' % gz_path
 
 
@@ -102,7 +103,7 @@ def plot_ms_arms_number(sfr_sample):
     cb = plt.colorbar(h[3],cax = axColorbar, orientation="vertical")
     cb.set_label(r'$N_\mathrm{star-forming\/galaxies}$' ,fontsize=16)
 
-    fig.savefig('%s/ms_arms_number.pdf' % ms_path, dpi=200)
+    fig.savefig('%s/ms_arms_number.pdf' % fig_path, dpi=200)
 
     return None
 
@@ -139,7 +140,7 @@ def plot_ms_bars(sfr_sample):
         ax.scatter(b['MEDIAN_MASS'],b['MEDIAN_SFR'], s=2, color=c, marker='o')
 
     fig.tight_layout()
-    fig.savefig('%s/ms_bar.pdf' % ms_path, dpi=200)
+    fig.savefig('%s/ms_bar.pdf' % fig_path, dpi=200)
 
 
     return None
@@ -193,7 +194,7 @@ def plot_ms_arms_winding(sfr_sample):
     cb.set_label(r'$N_\mathrm{star-forming\/galaxies}$' ,fontsize=16)
 
     #fig.tight_layout()
-    fig.savefig('%s/ms_arms_winding.pdf' % ms_path, dpi=200)
+    fig.savefig('%s/ms_arms_winding.pdf' % fig_path, dpi=200)
 
     return None
 

### 2014-02-20 gz_mainsequence.py
Updated bar figure

@@ -113,6 +113,7 @@ def plot_ms_bars(sfr_sample):
 
     fig = plt.figure(2)
     fig.clf()
+    fig.subplots_adjust(left=0.08,bottom=0.15,right=0.9,hspace=0,wspace=0)
 
     mass,sfr = get_mass_sfr(sfr_sample)
     mass_bins,sfr_bins = bins()
@@ -124,24 +125,33 @@ def plot_ms_bars(sfr_sample):
     unbarred = sfr_sample[notedgeon & (sfr_sample['t03_bar_a06_bar_debiased'] < 0.4)] 
 
     bar_data = (barred,unbarred)
+    bar_text = ('Barred','Unbarred')
     color = ('blue','red')
 
     # Plot barred and unbarred
-    for idx, (b,c) in enumerate(zip(bar_data,color)):
+    for idx, (b,c,t) in enumerate(zip(bar_data,color,bar_text)):
 
         ax = fig.add_subplot(1,2,idx+1)
         h = ax.hist2d(mass,sfr,bins=50,cmap = cm.gray_r, norm=LogNorm())
-        ax.set_xlim(6,13)
-        ax.set_ylim(-5,2)
+        ax.set_xlim(6,11.5)
+        ax.set_ylim(-4,2)
         ax.set_xlabel('Stellar mass (log'+r'$M/M_\odot$)',fontsize=20)
-        ax.set_ylabel('Star formation rate'+r'$M_\odot/yr$',fontsize=20)
-        fig.colorbar(h[3], ax=ax)
+
+        if idx == 0:
+            ax.set_ylabel('SFR '+r'$[M_\odot/\mathrm{yr}]$',fontsize=16)
+        else:
+            ax.get_yaxis().set_ticks([])
 
         ax.scatter(b['MEDIAN_MASS'],b['MEDIAN_SFR'], s=2, color=c, marker='o')
 
-    fig.tight_layout()
-    fig.savefig('%s/ms_bar.pdf' % fig_path, dpi=200)
+        ax.text(6.2,1.4,t,color=c,fontsize=18)
 
+    box = ax.get_position()
+    axColorbar = plt.axes([box.x0*1.05 + box.width * 0.95, box.y0, 0.01, box.height])
+    cb = plt.colorbar(h[3],cax = axColorbar, orientation="vertical")
+    cb.set_label(r'$N_\mathrm{star-forming\/galaxies}$' ,fontsize=16)
+
[…]

### 2014-02-21 mainsequence_morph.tex
Updated figures with linear MS fits

@@
 
-\begin{table}
- \begin{tabular}{@{}lrcl}
+\begin{table} \caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies.}
+ \begin{tabular}{@{}lrrrll}
  \hline
 \multicolumn{1}{c}{Sample} &
+\multicolumn{1}{c}{$N$} &
 \multicolumn{1}{c}{$\alpha$} &
 \multicolumn{1}{c}{$\beta$} &
-\multicolumn{1}{c}{$\sigma$} 
-\\ 
+\multicolumn{1}{c}{$\sigma_\alpha$} &
+\multicolumn{1}{c}{$\sigma_\beta$} 
 \\ 
@@
 \hline						
-%Main (original + extra)       & 273,783 & 43  & 17.0   \\     % 43.1
-All star-forming galaxies  & & & \\
+SF galaxies  & 52,685  & 0.81  & $-7.91$   & $7.94\times10^{-3}$   & $4.40\times10^{-4}$  \\
 \hline
-$N_{arms} = 1$ & & & \\
-$N_{arms} = 2$ & & & \\
-$N_{arms} = 3$ & & & \\
-$N_{arms} = 4$ & & & \\
-$N_{arms} = 5$ & & & \\
-$N_{arms} = ?$ & & & \\
+1 arm        &         & 0.73  & $ -6.83$  &  $7.94\times10^{-3}$  & $8.11\times10^{-1}$  \\
+2 arms       &         & 1.50  & $-15.04$  &  $3.96\times10^{-4}$  & $4.42\times10^{-2}$  \\
+3 arms       &         & 0.38  & $ -3.34$  &  $3.34\times10^{-3}$  & $3.67\times10^{-1}$  \\
+4 arms       &         & 0.55  & $ -5.24$  &  $5.52\times10^{-2}$  & $5.69\times10^{0 }$  \\
+5+ arms      &         & 0.56  & $ -5.72$  &  $2.93\times10^{-2}$  & $2.93\times10^{0 }$  \\
+can't tell   &         & 1.19  & $-12.11$  &  $2.56\times10^{-2}$  & $2.65\times10^{0 }$  \\
 \hline
-Tight & & & \\
-Medium & & & \\
-Loose & & & \\
+tight arms   &         & 0.53  & $-5.11$   &  $7.19\times10^{-4}$  & $7.55\times10^{-2}$  \\
+medium arms  &         & 0.67  & $-6.47$   &  $4.36\times10^{-3}$  & $4.75\times10^{-1}$  \\
+loose arms   &         & 0.99  & $-9.65$   &  $2.28\times10^{-3}$  & $2.46\times10^{-1}$  \\
 \hline
-Barred & & & \\
-Unbarred & & & \\
+barred       &         & 1.17  & $-11.58$  &  $1.98\times10^{-4}$  & $2.22\times10^{-2}$  \\
+unbarred     &         & 0.67  & $ -6.59$  &  $3.78\times10^{-5}$  & $3.85\times10^{-3}$  \\
 \hline
  \end{tabular}
- \caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies. \label{tbl-fits}}
+\tablecomments{Parameters are according to Equation~\ref{eqn-linearfit}.\label{tbl-fits}}
 \end{table}
+
+The linear fits to the data in Table~\ref{tbl-fits} are in the form:
+
+\begin{equation}
+SFR = \alpha(M_\star/M_\odot) + \beta \hspace{20pt}[M_\odot/yr]
+\label{eqn-linearfit}
+\end{equation}
+
+\noindent where $\alpha$ and $\beta$ are parameters fit by least-squares algorithm.
+
+\emph{Left to do: revise fits so that galaxy samples are for more robust results (ie, majority response vs.
+just the set flag) and re-run the fits.
+Also come up with a more sensible measure of the uncertainty - the formal covariance elements clearly don't represent the dispersion in the main sequence.}
 

### 2014-07-24 gz_mainsequence.py
Updating code

@@ -11,28 +11,29 @@ from astropy.io import fits
 plt.ion()
 
 gz_path = '/Users/willettk/Astronomy/Research/GalaxyZoo'
-ms_path = '%s/gz_mainsequence' % gz_path
-fig_path = '%s/gz_mainsequence/figures' % gz_path
+ms_path = '%s/gzmainsequence' % gz_path
+fig_path = '%s/gzmainsequence/figures' % gz_path
 fits_path = '%s/fits' % gz_path
 
+def get_data(mergers=False):
 
-def get_data():
+    if mergers:
+        filename = '%s/mergers/mergers_mpajhu_gz2.fits' % ms_path
+    else:
+        filename = '%s/mpajhu_gz2.fits' % fits_path
 
-    with fits.open('%s/mpajhu_gz2.fits' % fits_path) as f:
+    with fits.open(filename) as f:
         data = f[1].data
 
     return data
 
-def subsample(data):
+def get_sfr_sample(data):
 
     # Find starforming galaxies
 
     sf = (data['bpt'] == 1) #| (data['bpt'] == 2)
     redshift = data['REDSHIFT'] <= 0.1
     absmag = data['PETROMAG_MR'] < -19.5
-
-    spiral = (data['t01_smooth_or_features_a02_features_or_disk_debiased'] > 0.430) & (data['t02_edgeon_a05_no_debiased'] > 0.715) & (data['t04_spiral_a08_spiral_weight'] >= 20) & (data['t04_spiral_a08_spiral_debiased'] > 0.619)
-    notedgeon = (data['t01_smooth_or_features_a02_features_or_disk_debiased'] > 0.430) & (data['t02_edgeon_a05_no_debiased'] > 0.715) & (data['t02_edgeon_a05_no_weight'] >= 20)
 
     sfr_sample = data[sf & redshift]
 
@@ -44,8 +45,11 @@ def get_mass_sfr(sfr_sample):
 
     mass = sfr_sample[mass_sfr_good]['MEDIAN_MASS']
     sfr = sfr_sample[mass_sfr_good]['MEDIAN_SFR']
+    sfr16_err = np.abs(sfr_sample[mass_sfr_good]['P16_SFR'] - sfr_sample[mass_sfr_good]['MEDIAN_SFR'])
[…]

### 2014-07-24 zurich_plots.py

@@ -1,12 +1,15 @@
-from astropy.io import fits as pyfits
-import matplotlib
+import numpy as np
+
+from astropy.io import fits as fits
 from matplotlib import pyplot as plt
 from matplotlib.font_manager import FontProperties
-import numpy as np
+
+gzdir = '/Users/willettk/Astronomy/Research/GalaxyZoo'
+figdir = '%s/gzmainsequence/zurich_figs' % gzdir
 
 def get_mpadata():
 
-    p = pyfits.open('/Users/willettk/Astronomy/Research/GalaxyZoo/fits/mpajhu_gz2.fits')
+    p = fits.open('%s/fits/mpajhu_gz2.fits' % gzdir)
     mpajhu = p[1].data
     p.close()
 
@@ -145,13 +148,13 @@ def fit_lines(savefig=False):
     
     fig.tight_layout()
     if savefig:
-        fig.savefig('/Users/willettk/Astronomy/Research/GalaxyZoo/zurich/mainsequence_spiraltightness.pdf', dpi=200)
+        fig.savefig('%s/mainsequence_spiraltightness.pdf' % figdir, dpi=200)
 
     return None
 
 def get_lackner():
 
-    p = pyfits.open('/Users/willettk/Astronomy/Research/GalaxyZoo/fits/lackner_mpa_gz2.fits')
+    p = fits.open('/Users/willettk/Astronomy/Research/GalaxyZoo/fits/lackner_mpa_gz2.fits')
     lackner = p[1].data
     p.close()
 
@@ -218,14 +221,8 @@ def plot_bt_dispersion(savefig=False):
     
     fig.tight_layout()
     if savefig:
-        fig.savefig('/Users/willettk/Astronomy/Research/GalaxyZoo/zurich/bulgeratio_morph.pdf', dpi=200)
+        fig.savefig('%s/bulgeratio_morph.pdf' % figdir, dpi=200)
 
     return None
-
-
-
-
-
-    
 
 

### 2014-07-24 mainsequence_morph.tex
Add paper draft

@@
 \usepackage{amsmath}
+\usepackage{color}
 \bibliographystyle{apj}
@@
 \shortauthors{WILLETT ET AL.}
+
+\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
+\newcommand{\kevin}{{\color{red}\textbf{Kevin}}}
 
@@
 
-In this paper, we use the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with the largest database of visual classifications of galaxy structure and morphology ever assembled from the Galaxy Zoo citizen science project \citep{lin08,lin11,wil13} to test whether galaxy structure affects their star formation properties.
+Discuss (\kevin) seminal work of \citet{pen10a,pen12,pen14a,pen14} on gas regulator model and how mass/environment drive galaxy evolution.
+
+In this paper, we use the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with the largest database of visual classifications of galaxy structure and morphology ever assembled from the Galaxy Zoo citizen science projects \citep{lin08,lin11,wil13} to test whether galaxy structure affects their star formation properties.
 
@@
 
-Description of Galaxy Zoo 2 \citep{wil13}.
-Stellar masses and SFR from MPA-JHU \citep{kau03a,bri04}.
-Select starforming galaxies using BPT diagram \citep{bal81} and the standard \citet{kau03} demarcation line.
-Spiral galaxies are selected according to the following vote and vote thresholds.
+Data for all galaxies in this paper comes from optical observations in the SDSS~DR7.
+The morphological data is drawn from citizen science classifications in Galaxy~Zoo.
+Merging pairs of galaxies are taken from the catalog of \citet{dar10a}, all of which lie in the redshift range $0.005<z<0.1$.
+Post-merger spheroidal galaxies without an obvious, separated companion \citep{car12} are specifically excluded from the sample.
+Detailed classifications of disk morphologies (arm pitch angle, number of spiral arms, presence of a galactic bar) are taken from the successor Galaxy~Zoo~2 (GZ2) catalog \citep{wil13}.
 
-Figure: example images of: 1-5 arms, plus arm tightness, plus barred vs. non-barred.
+Spiral galaxies are selected according to the following thresholds in the spectroscopic GZ2 catalog, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
+We identify sub-classes of spiral structure using the morphology flags as given in the GZ2 catalog; these are designed to be conservative cuts, including only robust examples of each morphological class.
+
+Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04}.
+We use updated stellar masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation.
+Galaxies with low signal-to-noise ratio $(S/N > 3)$ galaxies are removed.
+
+% Figure: example images of: 1-5 arms, plus arm tightness, plus barred vs. non-barred.
+
+%%%%%%%%%%%%
+%%% RESULTS
+%%%%%%%%%%%%
+
+\section{Results} \label{sec-results}
+
+We analyze the dependence of the star-forming main sequence for three different sets of disk galaxies: splitting the sample by the observed number (multiplicity) of spiral arms, the relative pitch angle (tightness or winding) of the spiral arms, and the presence of a galactic bar.
+Both spiral arms and galactic bars can have significant effects on the local properties of a galaxy.
+Dynamical effects compress gas and trigger recent star formation within spiral arms, while longer galactic bars have redder colors and less star formation than the rest of the disk \citep{hoy11}.
+We examine whether these kpc-scale effects can be seen long-term in the galaxy's SFR-mass relationship.
+
+For the control sample, we plot in Figures~\ref{fig-number}-\ref{fig-mergers} the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local ($z<0.1$ and $M_r<-19.5$) SDSS galaxies.
+As demonstrated in previous papers, there is a fairly tight correlation between the stellar mass and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
+The relationship extends over at least 4~orders of magnitude in both $M_\star$ and SFR.
+
+\begin{figure*}
+\includegraphics[angle=0,width=7.0in]{figures/ms_arms_number.pdf}
+\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the number of spiral arms. Both stellar mass and SFR are taken from the MPA-JHU catalog for DR7. 
+\label{fig-number}}
+\end{figure*}
+
+Figure~\ref{fig-number} overplots the $M_\star-SFR$ relationship for disk galaxies separated by their arm multiplicity.
+The GZ2 data separates disk galaxies with visible spiral arms into categories of 1, 2, 3, 4, or more than four spiral arms; there is also an additional option if the number of spiral arms cannot be accurately determined.
+There are a total of 14,179 galaxies with flags for arm multiplicity (indicating a high level of agreement among classifiers) in the GZ2 data.
+Of those, two-armed spirals are by far the most common, comprising 85\% of the total.
+This is also the only multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\sun$ are detected.
+
+The fit to the star-forming main sequence for two-armed spirals tighly follows that of that for all spiral galaxies, with both the slope and offset of the linear fits completely consistent with each other (Table~\ref{tbl-fits}).
+Similarly, the fits for 3, 4, and $5+$-armed spirals are also consistent with the main relation (although all three have much lower numbers which affect the quality of the fit).
+
+1-armed spirals present an interesting case, with the majority of the population lying slightly above the fit to all star-forming spirals.
+This is consistent with the work of \citet{cas13}, who showed that 1-armed spirals in GZ2 are robust indicators of close interactions at projected distances of $r_p < 50~h^{-1}$~kpc.
+The underlying reason is that many ``1-armed spirals'' are in fact caused by bridges or tidal tails from interactions with a nearby companion; we discuss the likely role of merging/interacting galaxies in Figure~\ref{fig-mergers}.
+
+Finally, galaxies with an uncertain number of spiral arms (although also with relatively low numbers) fall slightly below the mean star-forming main sequence relation.
+We conjecture that this is a consequence of galaxies that have likely already begun the process of quenching.
+As a result, the star-formation rate is depleted and the contrast of spiral arms against the rest of the disk (which for visual identification is at least in part dependent on bright knots of recent star formation) makes the multiplicity more difficult to identify.
+(\kevin: check colors of these galaxies and see if they lie in the green valley?
+Would be a nice test to see if they're consistent with the red herring model.)
+
+\begin{figure*}
+\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding.pdf}
+\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the relative pitch angle of the spiral arms. 
+\label{fig-winding}}
+\end{figure*}
+
+The pitch angle of the spiral arms also has no significant change on the star-forming main sequence relation (Figure~\ref{fig-winding}).
+We separate galaxies by their relative pitch angles (defined as ``tight'', ``medium'', and ``loose''); the pitch angle is typically used as one of the primary drivers for separating galaxies along the Hubble tuning fork.
+\citet{wil13} show, however, that pitch angle only weakly correlates with Hubble type from expert visual classifications, and that the bulge-to-disk ratio is a more important driver.
+All three categories correlate tightly with spiral galaxies in general; we note that the small deviation above the main sequence for loosely-wound galaxies is also consistent with \citet{cas13}, who show that this morphology also correlates with close pairs and interactions.
+
+It should also be mentioned that the galaxies in GZ2 flagged as a function of pitch angle are not representative of the true vote distribution.
+The raw numbers in Figure~\ref{fig-winding} suggest that most spiral galaxies are either tightly or loosely wound.
+In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the medium option at the 80\% level which sets the flag.
+Plotting the same star-forming main sequence diagram as a function of $p_{medium}$, which more accurately tracks the pitch angle distribution, shows no significant deviations from the main sample.
+{\color{red}HAVEN'T ACTUALLY DONE THIS!}
+
+Figure~\ref{fig-bar}: $M_\star-SFR$ for barred vs unbarred \\
+Figure~\ref{fig-mergers}: $M_\star-SFR$ for merging galaxies \citet{dar10a} \\
+
+How many galaxies are there in the total sample? What is the mass, color, and redshift range?
+
+\begin{figure*}
+\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
+\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the detection of a galactic bar. 
+\label{fig-bar}}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[angle=0,width=7.0in]{figures/ms_mergers.pdf}
+\caption{Stellar mass vs.
+star formation rate for 2,978~merging galaxies in GZ, as compared to the broader star-forming population.
+When fixing the slope of the star-forming main sequence and allowing the offset to vary, mergers have higher SFR of $\sim0.2$~dex.
+\label{fig-mergers}}
+\end{figure*}
+
+List the fits to slope and intercept for the linear version of the M-SFR relation. Also look at dispersion.
 
@@
 \begin{table} \caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies.}
- \begin{tabular}{@{}lrrrll}
+ \begin{tabular}{@{}lrcrcl}
  \hline
@@
 \hline						
-SF galaxies  & 52,685  & 0.81  & $-7.91$   & $7.94\times10^{-3}$   & $4.40\times10^{-4}$  \\
+SF galaxies  & 52,685  & $0.81$  & $-7.91$   & $7.94\times10^{-3}$   & $4.40\times10^{-4}$  \\
 \hline
-1 arm        &         & 0.73  & $ -6.83$  &  $7.94\times10^{-3}$  & $8.11\times10^{-1}$  \\
-2 arms       &         & 1.50  & $-15.04$  &  $3.96\times10^{-4}$  & $4.42\times10^{-2}$  \\
-3 arms       &         & 0.38  & $ -3.34$  &  $3.34\times10^{-3}$  & $3.67\times10^{-1}$  \\
-4 arms       &         & 0.55  & $ -5.24$  &  $5.52\times10^{-2}$  & $5.69\times10^{0 }$  \\
-5+ arms      &         & 0.56  & $ -5.72$  &  $2.93\times10^{-2}$  & $2.93\times10^{0 }$  \\
-can't tell   &         & 1.19  & $-12.11$  &  $2.56\times10^{-2}$  & $2.65\times10^{0 }$  \\
+1 arm        &         & $0.66$  & $-6.31$  &  $5.11\times10^{-3}$  & $5.14\times10^{-1}$  \\
+2 arms       &         & $0.79$  & $-7.74$  &  $1.11\times10^{-4}$  & $1.14\times10^{-2}$  \\
+3 arms       &         & $0.57$  & $-5.47$  &  $4.17\times10^{-3}$  & $4.49\times10^{-1}$  \\
+4 arms       &         & $0.35$  & $-3.29$  &  $9.18\times10^{-2}$  & $9.58\times10^{0 }$  \\
+5+ arms      &         & $0.64$  & $-6.88$  &  $7.20\times10^{-2}$  & $6.91\times10^{0 }$  \\
+can't tell   &         & $0.69$  & $-7.10$  &  $1.06\times10^{-2}$  & $1.04\times10^{0 }$  \\
 \hline
-tight arms   &         & 0.53  & $-5.11$   &  $7.19\times10^{-4}$  & $7.55\times10^{-2}$  \\
-medium arms  &         & 0.67  & $-6.47$   &  $4.36\times10^{-3}$  & $4.75\times10^{-1}$  \\
-loose arms   &         & 0.99  & $-9.65$   &  $2.28\times10^{-3}$  & $2.46\times10^{-1}$  \\
+tight arms   &         & $0.53$  & $-5.11$   &  $7.19\times10^{-4}$  & $7.55\times10^{-2}$  \\
+medium arms  &         & $0.67$  & $-6.47$   &  $4.36\times10^{-3}$  & $4.75\times10^{-1}$  \\
+loose arms   &         & $0.99$  & $-9.65$   &  $2.28\times10^{-3}$  & $2.46\times10^{-1}$  \\
 \hline
-barred       &         & 1.17  & $-11.58$  &  $1.98\times10^{-4}$  & $2.22\times10^{-2}$  \\
-unbarred     &         & 0.67  & $ -6.59$  &  $3.78\times10^{-5}$  & $3.85\times10^{-3}$  \\
+barred       &         & $1.17$  & $-11.58$  &  $1.98\times10^{-4}$  & $2.22\times10^{-2}$  \\
+unbarred     &         & $0.67$  & $ -6.59$  &  $3.78\times10^{-5}$  & $3.85\times10^{-3}$  \\
+\hline
+merger       &         & --      & $ -7.91$  &  --                   & $4.40\times10^{-4}$  \\
 \hline
@@
 
-The linear fits to the data in Table~\ref{tbl-fits} are in the form:
+Linear fits to the data in Table~\ref{tbl-fits} are in the form:
 
 \begin{equation}
-SFR = \alpha(M_\star/M_\odot) + \beta \hspace{20pt}[M_\odot/yr]
+\log(SFR) = \alpha(\log[M_\star/M_\odot]) + \beta \hspace{20pt}[M_\odot/yr]
 \label{eqn-linearfit}
@@
 Also come up with a more sensible measure of the uncertainty - the formal covariance elements clearly don't represent the dispersion in the main sequence.}
-
-Figure~\ref{fig-number}: $M_\star-SFR$ for arm multiplicity \\
-Figure~\ref{fig-winding}: $M_\star-SFR$ for pitch angle ($\phi$) \\
-Figure~\ref{fig-bar}: $M_\star-SFR$ for barred vs unbarred \\
-
-How many galaxies are there in the total sample? What is the mass, color, and redshift range?
-
-%%%%%%%%%%%%
-%%% RESULTS
-%%%%%%%%%%%%
-
-\section{Results} \label{sec-results}
-
-\begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_arms_number.pdf}
-\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the number of spiral arms. Both stellar mass and SFR are taken from the MPA-JHU catalog for DR7. 
-\label{fig-number}}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding.pdf}
-\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the relative pitch angle of the spiral arms. 
-\label{fig-winding}}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
-\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the detection of a galactic bar. 
-\label{fig-bar}}
-\end{figure*}
-
-List the fits to slope and intercept for the linear version of the M-SFR relation. Also look at dispersion.
 
@@
 
+The biggest forcing we can think of for the system is a major merger. Even that doesn't push it too far off the main sequence, indicating short timescales and higher levels of feedback.
+
+We know that this is true at low redshift, but not at higher redshift.
+\citet{rod11} show a significant increase at $1.5<z<2.5$, likely due to the \emph{higher gas fraction} in galaxies at these redshifts.
+Also significant difference in disks at low/high redshift when using disk surface density instead of mass \citep{dad10}.
+\citet{elb11} show that ``compact'' galaxies lie significantly off the SFR-MS using {\it Herschel} data.
+In the local Universe, the green peas are the only galaxies that significantly exceed the main sequence, as evidenced by their sSFR \citep{car09}.
+
 Connection between galaxy structure and quenching efficiency - \citet{oma14} found a simple dependence on $B/T$ for SDSS DR7 data.
+
+\citet{abr14} find that the sSFR in galactic disks is independent of mass.
+
+Check the mergers against the IR-derived star formation rates of \citet{jar13}?
 
@@
 
-This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05}. 
+We thank Lucio Mayer and Rory Smith for useful discussions. This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05}. 
 %The development of Galaxy Zoo 2 was supported by The Leverhulme Trust.

### 2014-07-25 mainsequence_morph.tex
Remade bar, arms winding plots

@@
 
-% Figure: example images of: 1-5 arms, plus arm tightness, plus barred vs. non-barred.
+% Figure: example images?
+
+How many galaxies are there in the total sample? What is the mass, color, and redshift range?
+
+List the fits to slope and intercept for the linear version of the M-SFR relation. Also look at dispersion.
+
+Table~\ref{tbl-fits}: fits for all star forming galaxies and then split by different morphologies
+
+\begin{table} \caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies.}
+ \begin{tabular}{@{}lrcrcl}
+ \hline
+\multicolumn{1}{c}{Sample} &
+\multicolumn{1}{c}{$N$} &
+\multicolumn{1}{c}{$\alpha$} &
+\multicolumn{1}{c}{$\beta$} &
+\multicolumn{1}{c}{$\sigma_\alpha$} &
+\multicolumn{1}{c}{$\sigma_\beta$} 
+\\ 
+\hline
+\hline						
+SF galaxies  & 52,685  & $0.81$  & $-7.91$   & $7.94\times10^{-3}$   & $4.40\times10^{-4}$  \\
+\hline
+1 arm        &         & $0.66$  & $-6.31$  &  $5.11\times10^{-3}$  & $5.14\times10^{-1}$  \\
+2 arms       &         & $0.79$  & $-7.74$  &  $1.11\times10^{-4}$  & $1.14\times10^{-2}$  \\
+3 arms       &         & $0.57$  & $-5.47$  &  $4.17\times10^{-3}$  & $4.49\times10^{-1}$  \\
+4 arms       &         & $0.35$  & $-3.29$  &  $9.18\times10^{-2}$  & $9.58\times10^{0 }$  \\
+5+ arms      &         & $0.64$  & $-6.88$  &  $7.20\times10^{-2}$  & $6.91\times10^{0 }$  \\
+can't tell   &         & $0.69$  & $-7.10$  &  $1.06\times10^{-2}$  & $1.04\times10^{0 }$  \\
+\hline
+tight arms   &         & $0.53$  & $-5.11$   &  $7.19\times10^{-4}$  & $7.55\times10^{-2}$  \\
+medium arms  &         & $0.67$  & $-6.47$   &  $4.36\times10^{-3}$  & $4.75\times10^{-1}$  \\
+loose arms   &         & $0.99$  & $-9.65$   &  $2.28\times10^{-3}$  & $2.46\times10^{-1}$  \\
+\hline
+barred       &         & $1.17$  & $-11.58$  &  $1.98\times10^{-4}$  & $2.22\times10^{-2}$  \\
+unbarred     &         & $0.67$  & $ -6.59$  &  $3.78\times10^{-5}$  & $3.85\times10^{-3}$  \\
+\hline
+merger       &         & --      & $ -7.91$  &  --                   & $4.40\times10^{-4}$  \\
+\hline
+ \end{tabular}
+\tablecomments{Parameters are according to Equation~\ref{eqn-linearfit}.\label{tbl-fits}}
+\end{table}
+
+Linear fits to the data in Table~\ref{tbl-fits} are in the form:
+
+\begin{equation}
+\log(SFR) = \alpha(\log[M_\star/M_\odot]) + \beta \hspace{20pt}[M_\odot/yr]
+\label{eqn-linearfit}
+\end{equation}
+
+\noindent where $\alpha$ and $\beta$ are parameters fit by least-squares algorithm.
+
+\emph{Left to do: revise fits so that galaxy samples are for more robust results (ie, majority response vs.
+just the set flag) and re-run the fits.
+Also come up with a more sensible measure of the uncertainty - the formal covariance elements clearly don't represent the dispersion in the main sequence.}
 
@@
 In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the medium option at the 80\% level which sets the flag.
-Plotting the same star-forming main sequence diagram as a function of $p_{medium}$, which more accurately tracks the pitch angle distribution, shows no significant deviations from the main sample.
-{\color{red}HAVEN'T ACTUALLY DONE THIS!}
-
-Figure~\ref{fig-bar}: $M_\star-SFR$ for barred vs unbarred \\
-Figure~\ref{fig-mergers}: $M_\star-SFR$ for merging galaxies \citet{dar10a} \\
-
-How many galaxies are there in the total sample? What is the mass, color, and redshift range?
+Plotting the same star-forming main sequence diagram as a function of $p_{medium}$, which more accurately tracks the pitch angle distribution, also closely follows the main star-forming main sequence.
+% Figure ms_arms_winding_weighted_pmed.pdf shows this.
+Not sure if we need to put it in the paper?
 
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
+%\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/ms_bar_contour.pdf}
 \caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the detection of a galactic bar. 
@@
 \end{figure*}
+
+Finally, we examine the effect of a large-scale galactic bar on the star-forming main sequence.
+This sample is significantly larger than those including spiral arm morphology, since the classification is at a higher level in the GZ2 tree and has only two choices; this results in a higher percentage of consensus classifications that set the flag.
+Figure~\ref{fig-bar} shows the star-forming main sequence for both barred and unbarred galaxies.
+Although the fraction of barred galaxies potentially varies as a function of stellar mass \citep{mas11c}, both the linear fits and ranges of the sub-populations are consistent with all star-forming galaxies.
+In other words, the presence of a bar does not affect the galaxy's position on the star-forming main sequence.
+
+%%%%%%%%%%%%
+%%% DISCUSSION
+%%%%%%%%%%%%
+
+\section{Discussion}\label{sec-discussion}
+
+There is no significant difference between any of the morphological categories explored. Statistical test for how ``not different'' the categories are.
+
+This is interpreted as evidence that the regulation of the star formation rate is independent of the details of galactic structure as traced by the dynamics of the spiral arms.
+
+Conditional statements: if the situation above is true, then the following must apply.
+
+Point that has not been made before; self-regulated systems where you can move parts around, but the total amount must be conserved.
+Process as a result cannot be simply regulated locally - the whole system must know about the rate of regulation.
+What does this say about the minimum lifetime of the features as a dynamical timescale $\tau_{dyn}$?
+
+The biggest forcing we can think of for the system is a major merger.
+Even that doesn't push it too far off the main sequence, indicating short timescales and higher levels of feedback.
+Figure~\ref{fig-mergers} shows the relation for 3,003~systems of merging galaxies \citep{dar10a}.
+For these systems, there is a small increase in the offset of the $M_\star-SFR$ relation, but none in the slope.
+The difference is $\sim0.2$~dex, an increase of only $\sim70\%$ in star-formation rate for a given mass.
+There are a very small number of galaxies whose star formation rates lie more than an order of magnitude above the standard relation, but the numbers are too small to make a significant contribution to the SFR density of the local Universe.
 
@@
 
-List the fits to slope and intercept for the linear version of the M-SFR relation. Also look at dispersion.
-
-Table~\ref{tbl-fits}: fits for all star forming galaxies and then split by different morphologies
-
-\begin{table} \caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies.}
- \begin{tabular}{@{}lrcrcl}
- \hline
-\multicolumn{1}{c}{Sample} &
-\multicolumn{1}{c}{$N$} &
-\multicolumn{1}{c}{$\alpha$} &
-\multicolumn{1}{c}{$\beta$} &
-\multicolumn{1}{c}{$\sigma_\alpha$} &
-\multicolumn{1}{c}{$\sigma_\beta$} 
-\\ 
-\hline
-\hline						
-SF galaxies  & 52,685  & $0.81$  & $-7.91$   & $7.94\times10^{-3}$   & $4.40\times10^{-4}$  \\
-\hline
-1 arm        &         & $0.66$  & $-6.31$  &  $5.11\times10^{-3}$  & $5.14\times10^{-1}$  \\
-2 arms       &         & $0.79$  & $-7.74$  &  $1.11\times10^{-4}$  & $1.14\times10^{-2}$  \\
-3 arms       &         & $0.57$  & $-5.47$  &  $4.17\times10^{-3}$  & $4.49\times10^{-1}$  \\
-4 arms       &         & $0.35$  & $-3.29$  &  $9.18\times10^{-2}$  & $9.58\times10^{0 }$  \\
-5+ arms      &         & $0.64$  & $-6.88$  &  $7.20\times10^{-2}$  & $6.91\times10^{0 }$  \\
-can't tell   &         & $0.69$  & $-7.10$  &  $1.06\times10^{-2}$  & $1.04\times10^{0 }$  \\
-\hline
-tight arms   &         & $0.53$  & $-5.11$   &  $7.19\times10^{-4}$  & $7.55\times10^{-2}$  \\
-medium arms  &         & $0.67$  & $-6.47$   &  $4.36\times10^{-3}$  & $4.75\times10^{-1}$  \\
-loose arms   &         & $0.99$  & $-9.65$   &  $2.28\times10^{-3}$  & $2.46\times10^{-1}$  \\
-\hline
-barred       &         & $1.17$  & $-11.58$  &  $1.98\times10^{-4}$  & $2.22\times10^{-2}$  \\
-unbarred     &         & $0.67$  & $ -6.59$  &  $3.78\times10^{-5}$  & $3.85\times10^{-3}$  \\
-\hline
-merger       &         & --      & $ -7.91$  &  --                   & $4.40\times10^{-4}$  \\
-\hline
- \end{tabular}
-\tablecomments{Parameters are according to Equation~\ref{eqn-linearfit}.\label{tbl-fits}}
-\end{table}
-
-Linear fits to the data in Table~\ref{tbl-fits} are in the form:
-
-\begin{equation}
-\log(SFR) = \alpha(\log[M_\star/M_\odot]) + \beta \hspace{20pt}[M_\odot/yr]
-\label{eqn-linearfit}
-\end{equation}
-
-\noindent where $\alpha$ and $\beta$ are parameters fit by least-squares algorithm.
-
-\emph{Left to do: revise fits so that galaxy samples are for more robust results (ie, majority response vs.
-just the set flag) and re-run the fits.
-Also come up with a more sensible measure of the uncertainty - the formal covariance elements clearly don't represent the dispersion in the main sequence.}
-
-%%%%%%%%%%%%
-%%% DISCUSSION
-%%%%%%%%%%%%
-
-\section{Discussion}\label{sec-discussion}
-
-There is no significant difference between any of the morphological categories explored. Statistical test for how not different the categories are.
-
-This is interpreted as evidence that the regulation of the star formation rate is independent of the details of galactic structure as traced by the dynamics of the spiral arms.
-
-Conditional statements: if the situation above is true, then the following must apply.
-
-Point that has not been made before; self-regulated systems where you can move parts around, but the total amount must be conserved.
-Process as a result cannot be simply regulated locally - the whole system must know about the rate of regulation.
-What does this say about the minimum lifetime of the features as a dynamical timescale $\tau_{dyn}$?
-
-The biggest forcing we can think of for the system is a major merger. Even that doesn't push it too far off the main sequence, indicating short timescales and higher levels of feedback.
-
+These results confirm the trend in specific star formation rate seen by \citet{dar10}.
 We know that this is true at low redshift, but not at higher redshift.
@@
 \citet{elb11} show that ``compact'' galaxies lie significantly off the SFR-MS using {\it Herschel} data.
-In the local Universe, the green peas are the only galaxies that significantly exceed the main sequence, as evidenced by their sSFR \citep{car09}.
+In the local Universe, green pea galaxies are the only objects that significantly exceed the main sequence, as evidenced by their sSFR \citep{car09}.
 

### 2014-07-25 gz_mainsequence.py

@@ -156,13 +156,14 @@ def plot_ms_arms_number(sfr_sample):
 
     return None
 
-def plot_ms_bars(sfr_sample):
+def plot_ms_bars(sfr_sample,contour=False):
 
     # Plot
 
     fig = plt.figure(2,(11,6))
     fig.clf()
     fig.subplots_adjust(left=0.08,bottom=0.15,right=0.9,hspace=0,wspace=0)
+    filestr=''
 
     mass,sfr,sfr_err = get_mass_sfr(sfr_sample)
     mass_bins,sfr_bins = bins()
@@ -181,7 +182,7 @@ def plot_ms_bars(sfr_sample):
     for idx, (b,c,t) in enumerate(zip(bar_data,color,bar_text)):
 
         ax = fig.add_subplot(1,2,idx+1)
-        h = ax.hist2d(mass,sfr,bins=50,cmap = cm.gray_r, norm=LogNorm())
+        h2 = ax.hist2d(mass,sfr,bins=50,cmap = cm.gray_r, norm=LogNorm())
         ax.set_xlim(6,11.5)
         ax.set_ylim(-4,2)
         ax.set_xlabel('Stellar mass (log'+r'$\/M/M_\odot$)',fontsize=20)
@@ -191,7 +192,15 @@ def plot_ms_bars(sfr_sample):
         else:
             ax.get_yaxis().set_ticks([])
 
-        ax.scatter(b['MEDIAN_MASS'],b['MEDIAN_SFR'], s=2, color=c, marker='o')
+        # Try a contour plot??
+
+        if contour:
+            hb,xb,yb = np.histogram2d(b['MEDIAN_MASS'],b['MEDIAN_SFR'],bins=(mass_bins,sfr_bins))
+            levels=10**(np.linspace(0,2,8))
+            CS = ax.contour(mass_bins[1:],sfr_bins[1:],hb.T,levels,colors=c)
+            filestr='_contour'
+        else:
+            ax.scatter(b['MEDIAN_MASS'],b['MEDIAN_SFR'], s=2, color=c, marker='o')
 
         ax.text(6.2,1.4,t,color=c,fontsize=18)
 
@@ -203,19 +212,20 @@ def plot_ms_bars(sfr_sample):
 
     box = ax.get_position()
     axColorbar = plt.axes([box.x0*1.05 + box.width * 0.95, box.y0, 0.01, box.height])
[…]

### 2014-07-25 mainsequence_morph.tex
Update on text and figs

@@
 
-\title{The dependence of spiral disk morphology on the mass-star formation relation}
+\title{The dependence of spiral disk morphology on the star formation-stellar mass relation}
 
@@
 
+% Hello, @overheardonastroph!
+
 %%%%%%%%%%%%
@@
 \begin{abstract}
-We measure the mass-star formation relation in disk galaxies at $z<0.05$, using Galaxy Zoo morphologies to separate disk galaxies by their kiloparsec-scale spiral structure.
-We examine the number of arms, their average pitch angle, and the presence of a galactic bar, and show that both the slope and dispersion of the SFR-$M_{\rm stellar}$ relation is constant when varying all the above parameters.
+We measure the mass-star formation relation in disk galaxies at $z<0.05$, using Galaxy Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
+We examine the number of arms, their average pitch angle, and the presence of a galactic bar, and show that both the slope and dispersion of the SFR-$M_\star$ relation is constant when varying all the above parameters.
 We interpret this as evidence that the spiral arms, which are imperfect reflections of the galaxy's current gravitational potential, are either fully independent of the basic quenching relation or are completely overwhelmed by the combination of outflows and feedback.
 The arrangement of the star formation can be changed (as demonstrated by the filling factor of the disk), but the system \emph{as a whole} regulates itself.
+We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only drive the galaxies off the main relation by $\sim0.3$~dex; this is a significant reduction over merging systems at $z>1$.
 \end{abstract}
@@
 
-%ORIGINAL TEXT %Mass-SFR relationship is tight, universal, and redshift-dependent (many citations).
-We think this is the result of the balancing of cosmological inflows of gas from the halo and feedback mechanism \citep{bou10,lil13}.
-
-%NEW, COHERENT INTRO (hi there, @overheardonastroph!)
-Observations at a range of redshifts have established that the star formation rate (SFR) of a galaxy is strongly correlated to its stellar mass ($M_{\rm stellar}$).
-This `main sequence' of star formation (MS) is nearly linear and at least at low redshift, has remarkably small scatter (refs).
-Recent observations of star-forming galaxies at high redshifts show that this main sequence remains out to high redshift with the normalisation of the main sequence shifting up so that galaxies of the same stellar mass have a higher SFR at high redshift (refs).
+Observations at a range of redshifts have established that the star formation rate (SFR) of a galaxy is strongly correlated to its stellar mass ($M_\star$).
+This `main sequence' of star formation is nearly linear and at least at low redshift, has remarkably small scatter (refs).
+Recent observations of star-forming galaxies at high redshifts show that this main sequence remains out to high redshift with the normalisation of the main sequence shifting up so that galaxies of the same $M_\star$ have a higher SFR at high redshift (refs).
 The main sequence has been interpreted by \citet{bou10} and \citet{lil13} as the result of the balancing of inflows of cosmological gas and outflows due the feedback.
@@
 
-As star-forming galaxies exhibit a wide range of physical appearances in optical images, we can ask the natural question of whether the specifics of this physical appearance, and its underlying dynamical processes, have any effect on this homeostasis and therefore the galaxy's location relative to the SFR-$M_{\rm stellar}$ relation.
+As star-forming galaxies exhibit a wide range of physical appearances in optical images, we can ask the natural question of whether the specifics of this physical appearance, and its underlying dynamical processes, have any effect on this homeostasis and therefore the galaxy's location relative to the SFR-$M_\star$ relation.
 If the details of a galaxy's physical appearance are correlated with position relative to the main sequence, then the dynamical processes that give rise to them -- such as bar formation and spiral arm pitch angle -- are a fundamental aspect of the galaxy's regulatory mechanism.
@@
 Post-merger spheroidal galaxies without an obvious, separated companion \citep{car12} are specifically excluded from the sample.
-Detailed classifications of disk morphologies (arm pitch angle, number of spiral arms, presence of a galactic bar) are taken from the successor Galaxy~Zoo~2 (GZ2) catalog \citep{wil13}.
+Detailed classifications of disk morphologies (arm pitch angle, number of spiral arms, presence of a galactic bar) are taken from the Galaxy~Zoo~2 (GZ2) catalog \citep{wil13}.
 
-Spiral galaxies are selected according to the following thresholds in the spectroscopic GZ2 catalog, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
+Spiral galaxies are selected according to the following thresholds in the spectroscopic GZ2 sample, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
 We identify sub-classes of spiral structure using the morphology flags as given in the GZ2 catalog; these are designed to be conservative cuts, including only robust examples of each morphological class.
@@
 Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04}.
-We use updated stellar masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation.
+We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation.
 Galaxies with low signal-to-noise ratio $(S/N > 3)$ galaxies are removed.
+For both $M_\star$ and $SFR$, we use median values extracted from the PDF.
 
-% Figure: example images?
-
-How many galaxies are there in the total sample? What is the mass, color, and redshift range?
-
-List the fits to slope and intercept for the linear version of the M-SFR relation. Also look at dispersion.
-
-Table~\ref{tbl-fits}: fits for all star forming galaxies and then split by different morphologies
+%How many galaxies are there in the total sample? What is the mass, color, and redshift range?
+The total sample analyzed contains 52,685 star-forming galaxies.
+These are selected from the GZ2 spectroscopic sample with $z<0.1$, $M_r<-19.5$, and classified as actively star-forming (BPT$=1$) from the MPA-JHU emission line measurements.
+The average color for the star-forming galaxies is relatively blue, with $(u-r)=1.7\pm0.6$.
+Subsets of the star-forming galaxies are listed in Table~\ref{tbl-fits}.
 
@@
 \hline						
-SF galaxies  & 52,685  & $0.81$  & $-7.91$   & $7.94\times10^{-3}$   & $4.40\times10^{-4}$  \\
+SF galaxies  & 52685   & $0.73$  & $-7.19$   & $5.27\times10^{-6}$  & $5.18\times10^{-4}$  \\
 \hline
-1 arm        &         & $0.66$  & $-6.31$  &  $5.11\times10^{-3}$  & $5.14\times10^{-1}$  \\
-2 arms       &         & $0.79$  & $-7.74$  &  $1.11\times10^{-4}$  & $1.14\times10^{-2}$  \\
-3 arms       &         & $0.57$  & $-5.47$  &  $4.17\times10^{-3}$  & $4.49\times10^{-1}$  \\
-4 arms       &         & $0.35$  & $-3.29$  &  $9.18\times10^{-2}$  & $9.58\times10^{0 }$  \\
-5+ arms      &         & $0.64$  & $-6.88$  &  $7.20\times10^{-2}$  & $6.91\times10^{0 }$  \\
-can't tell   &         & $0.69$  & $-7.10$  &  $1.06\times10^{-2}$  & $1.04\times10^{0 }$  \\
+1 arm        & 39      & $0.66$  & $-6.31$  &  $5.11\times10^{-3}$  & $5.14\times10^{-1}$  \\
+2 arms       & 2914    & $0.79$  & $-7.74$  &  $1.11\times10^{-4}$  & $1.14\times10^{-2}$  \\
+3 arms       & 89      & $0.57$  & $-5.47$  &  $4.17\times10^{-3}$  & $4.49\times10^{-1}$  \\
+4 arms       & 9       & $0.35$  & $-3.29$  &  $9.18\times10^{-2}$  & $9.58\times10^{0 }$  \\
+5+ arms      & 9       & $0.64$  & $-6.88$  &  $7.20\times10^{-2}$  & $6.91\times10^{0 }$  \\
+can't tell   & 40      & $0.69$  & $-7.10$  &  $1.06\times10^{-2}$  & $1.04\times10^{0 }$  \\
 \hline
-tight arms   &         & $0.53$  & $-5.11$   &  $7.19\times10^{-4}$  & $7.55\times10^{-2}$  \\
-medium arms  &         & $0.67$  & $-6.47$   &  $4.36\times10^{-3}$  & $4.75\times10^{-1}$  \\
-loose arms   &         & $0.99$  & $-9.65$   &  $2.28\times10^{-3}$  & $2.46\times10^{-1}$  \\
+tight arms   &  308    & $0.73$  & $-7.26$  &  $1.68\times10^{-3}$  & $1.75\times10^{-1}$  \\
+medium arms  &  44     & $0.80$  & $-7.83$  &  $5.23\times10^{-3}$  & $5.37\times10^{-1}$  \\
+loose arms   &  470    & $0.74$  & $-7.14$  &  $5.16\times10^{-3}$  & $5.18\times10^{-2}$  \\
 \hline
-barred       &         & $1.17$  & $-11.58$  &  $1.98\times10^{-4}$  & $2.22\times10^{-2}$  \\
-unbarred     &         & $0.67$  & $ -6.59$  &  $3.78\times10^{-5}$  & $3.85\times10^{-3}$  \\
+barred       &  4473   & $0.76$  & $-7.54$  &  $7.60\times10^{-5}$  & $7.57\times10^{-3}$  \\
+unbarred     &  11593  & $0.70$  & $-6.92$  &  $2.65\times10^{-5}$  & $2.66\times10^{-3}$  \\
 \hline
-merger       &         & --      & $ -7.91$  &  --                   & $4.40\times10^{-4}$  \\
+merger       &  2978   & --      & $-7.91$  &  --                   & $4.40\times10^{-4}$  \\
 \hline
@@
 
-Linear fits to the data in Table~\ref{tbl-fits} are in the form:
+To analyze the $M_\star-SFR$ relationship, we apply a simple linear model for the total sample and subsamples.
+We apply a least-squares fit where the data are weighted by the uncertainty in SFR (computed as the mean difference in the 16th and 84th percentiles from the MPA-JHU PDFs).
+The data are then fit to:
 
@@
 
-\noindent where $\alpha$ and $\beta$ are parameters fit by least-squares algorithm.
+\noindent where $\alpha$ and $\beta$ represent the slope and offset, respectively.
+Values of the fits for each subample are given in Table~\ref{tbl-fits}; we also provide the formal uncertainties $\sigma_\alpha$ and $\sigma_\beta$ in each parameter from the covariance matrix.
 
-\emph{Left to do: revise fits so that galaxy samples are for more robust results (ie, majority response vs.
-just the set flag) and re-run the fits.
-Also come up with a more sensible measure of the uncertainty - the formal covariance elements clearly don't represent the dispersion in the main sequence.}
+\emph{Come up with a more sensible measure of the uncertainty - the formal covariance elements clearly don't represent the dispersion in the main sequence. Interquartile range?}
 
@@
 
-For the control sample, we plot in Figures~\ref{fig-number}-\ref{fig-mergers} the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local ($z<0.1$ and $M_r<-19.5$) SDSS galaxies.
-As demonstrated in previous papers, there is a fairly tight correlation between the stellar mass and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
+For the control sample, we plot in Figures~\ref{fig-number}-\ref{fig-mergers} the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local SDSS galaxies.
+As demonstrated in previous papers, there is a fairly tight correlation between $M_\star$ and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
 The relationship extends over at least 4~orders of magnitude in both $M_\star$ and SFR.
@@
 \includegraphics[angle=0,width=7.0in]{figures/ms_arms_number.pdf}
-\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the number of spiral arms. Both stellar mass and SFR are taken from the MPA-JHU catalog for DR7. 
+\caption{Stellar mass vs.
+star formation rate; grayscale colors are the distribution of all star-forming galaxies from the MPA-JHU catalog.
+Colored points in each panel show spiral galaxies with ``tight'', ``medium'', and ``loose'' spiral arms as identified by morphology flags in GZ2.
+Dotted lines show the weighted least-squares linear fit to the population as split by pitch angle; the solid line is the fit to all star-forming galaxies.
 \label{fig-number}}
@@
 As a result, the star-formation rate is depleted and the contrast of spiral arms against the rest of the disk (which for visual identification is at least in part dependent on bright knots of recent star formation) makes the multiplicity more difficult to identify.
-(\kevin: check colors of these galaxies and see if they lie in the green valley?
-Would be a nice test to see if they're consistent with the red herring model.)
-
-\begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding.pdf}
-\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the relative pitch angle of the spiral arms. 
-\label{fig-winding}}
-\end{figure*}
+{\it (\kevin: check colors of these galaxies and see if they lie in the green valley?
+Would be a nice test to see if they're consistent with the red herring model.)}
 
@@
 
-It should also be mentioned that the galaxies in GZ2 flagged as a function of pitch angle are not representative of the true vote distribution.
+\begin{figure*}
+\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding.pdf}
+\caption{Stellar mass vs.
+star formation rate; grayscale colors are the distribution of all star-forming galaxies as in Figure~\ref{fig-number}.
+From left to right: red, green, and blue points spiral galaxies with ``tight'', ``medium'', and ``loose'' spiral arms as identified by morphology flags in GZ2.
+Dotted lines show the weighted least-squares linear fit to the population as split by pitch angle; the solid line is the fit to all star-forming galaxies.
+\label{fig-winding}}
+\end{figure*}
+
+It should also be noted that the galaxies in GZ2 flagged as a function of pitch angle are not representative of the true vote distribution.
 The raw numbers in Figure~\ref{fig-winding} suggest that most spiral galaxies are either tightly or loosely wound.
 In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the medium option at the 80\% level which sets the flag.
-Plotting the same star-forming main sequence diagram as a function of $p_{medium}$, which more accurately tracks the pitch angle distribution, also closely follows the main star-forming main sequence.
+Plotting the same star-forming main sequence diagram as a function of $p_{\rm medium}$, which more accurately tracks the pitch angle distribution, also closely follows the main star-forming main sequence.
 % Figure ms_arms_winding_weighted_pmed.pdf shows this.
@@
 \includegraphics[angle=0,width=7.0in]{figures/ms_bar_contour.pdf}
-\caption{Stellar mass vs. star formation rate for oblique disk galaxies in GZ2, split by the detection of a galactic bar. 
+\caption{Stellar mass vs.
+star formation rate; grayscale colors are the distribution of all star-forming galaxies as in Figure~\ref{fig-number}.
+Left: blue contours show the distribution of barred galaxies ($p_\textrm{bar}\ge0.4$ for previously-identified disks) from GZ2.
+Right: red contours are the distribution of remaining disk galaxy population with no evidence for a strong bar ($p_\textrm{bar}<0.4$).
+Dotted lines show the weighted least-squares linear fit to the barred/unbarred population; the solid line is the fit to all star-forming galaxies.
 \label{fig-bar}}
@@
 
+Bar results are in rough agreement with the mass-dependent trends seen in \citet{ell11}; strong difference is only seen at $M_\star>10^7~M_\odot$, which is at the very upper end of our range.
+
 Point that has not been made before; self-regulated systems where you can move parts around, but the total amount must be conserved.
@@
 Even that doesn't push it too far off the main sequence, indicating short timescales and higher levels of feedback.
-Figure~\ref{fig-mergers} shows the relation for 3,003~systems of merging galaxies \citep{dar10a}.
+Figure~\ref{fig-mergers} shows the relation for systems of merging galaxies \citep{dar10a}.
 For these systems, there is a small increase in the offset of the $M_\star-SFR$ relation, but none in the slope.
@@
 \caption{Stellar mass vs.
-star formation rate for 2,978~merging galaxies in GZ, as compared to the broader star-forming population.
+star formation rate  as in Figure~\ref{fig-number}.
+for 2,978~merging galaxies in GZ, as compared to the broader star-forming population.
 When fixing the slope of the star-forming main sequence and allowing the offset to vary, mergers have higher SFR of $\sim0.2$~dex.
@@
 
-We thank Lucio Mayer and Rory Smith for useful discussions. This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05}. 
+We thank Rory Smith and Lucio Mayer for useful discussions. This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05}. 
 %The development of Galaxy Zoo 2 was supported by The Leverhulme Trust.

### 2014-07-25 gz_mainsequence.py

@@ -74,7 +74,7 @@ def fit_mass_sfr(sample,weighted=True):
 
     return a,b,v
 
-def plot_fits(label,data,axis,color,lw=2,ls='--',legend=True,verbose=False,weighted=True):
+def plot_fits(label,data,axis,color,lw=2,ls='--',legend=False,verbose=False,weighted=True):
 
     if weighted:
         prefix = ''
@@ -144,8 +144,15 @@ def plot_ms_arms_number(sfr_sample):
         ax.text(6.2,1.0,r'$N_{arms} = $%s' % al, color='k',fontsize=18)
 
         # Plot the linear fits
-        plot_fits(al,n1,ax,c,legend=False,verbose=True,weighted=True)
-        plot_fits('SF galaxies',sfr_sample,ax,'black',lw=1,ls='-',legend=False,weighted=True)
+        plot_fits(al,n1,ax,c)
+        plot_fits('SF galaxies',sfr_sample,ax,'black',lw=1,ls='-')
+
+        '''
+        # Print number of galaxies in each category
+
+        print '%i %s galaxies' % (len(n1),a)
+        '''
+
 
     box = ax.get_position()
     axColorbar = plt.axes([box.x0*1.05 + box.width * 0.95, box.y0, 0.01, box.height*2])
@@ -206,8 +213,14 @@ def plot_ms_bars(sfr_sample,contour=False):
 
         # Plot the best linear fit
 
-        plot_fits(t,b,ax,c,legend=False)
-        plot_fits(t,sfr_sample,ax,'black',lw=1,legend=False)
+        plot_fits(t,b,ax,c)
+        plot_fits(t,sfr_sample,ax,'black',lw=1,ls='-')
+
+        '''
+        # Print counts
+
+        print '%6i %s galaxies' % (len(b),t)
+        '''
 
 
     box = ax.get_position()
@@ -269,8 +282,14 @@ def plot_ms_arms_winding(sfr_sample,weight_by_pmed=False):
 
         # Plot the best linear fits
 
-        plot_fits(arm_label,n1,ax,c,legend=False)
-        plot_fits(arm_label,sfr_sample,ax,'black',lw=1,legend=False)
+        plot_fits(arm_label,n1,ax,c)
+        plot_fits(arm_label,sfr_sample,ax,'black',lw=1,ls='-')
+
+        '''
+        # Print number of galaxies in each category
+
[…]

### 2014-07-26 gz_mainsequence.py
Last edits from Zurich 2014 visit for KWW

@@ -379,3 +379,74 @@ def plot_ms_merger_fraction(sfr_sample):
 
     return None
 
+def plot_ms_greenpeas(sfr_sample):
+
+    # Plot
+
+    fig = plt.figure(4,(10,8))
+    fig.clf()
+
+    fig.subplots_adjust(left=0.08,bottom=0.15,hspace=0,wspace=0)
+
+    mass,sfr,sfr_err = get_mass_sfr(sfr_sample)
+    mass_bins,sfr_bins = bins()
+    h,xedges,yedges = np.histogram2d(mass,sfr,bins=(mass_bins,sfr_bins))
+
+    # Plot star-forming galaxies
+
+    ax = fig.add_subplot(111)
+    h = ax.hist2d(mass,sfr,bins=50,cmap = cm.gray_r, norm=LogNorm())
+    ax.set_xlim(6,11.5)
+    ax.set_ylim(-4,2)
+    ax.set_ylabel('log SFR '+r'$[M_\odot/\mathrm{yr}]$',fontsize=16)
+    ax.set_xlabel('Stellar mass [log '+r'$\/M/M_\odot$]',fontsize=16)
+
+    # Plot green peas
+
+    with fits.open('%s/mergers/mergers_mpajhu_bpt.fits' % ms_path) as f:
+        data = f[1].data
+
+    #sf_mergers = data[(data['bpt'] == 1) & (data['mass_ratio'] <= 3)]
+    sf_mergers = data[(data['bpt'] == 1)]
+
+    sc = ax.scatter(sf_mergers['MEDIAN_MASS'],sf_mergers['MEDIAN_SFR'], c=sf_mergers['mass_ratio'], edgecolor='none',s = 50, marker='.', cmap=matplotlib.cm.RdBu, vmin=1.,vmax=10.)
+
+    ax.text(6.2,1.3,'Mergers', color='black')
+
+    # Plot the best linear fits
+
+    #au,bu = plot_fits('Mergers',sf_mergers,ax,'red')
+    a1,a0 = plot_fits('Star-forming galaxies',sfr_sample,ax,'black',lw=1,ls='-')
+
+    # How many mergers fall above and below?
+
+    diff = sf_mergers['MEDIAN_SFR'] - (a0 + a1*sf_mergers['MEDIAN_MASS'])
+
+    # Fix same slope but different offset. What's the average difference between SF MS and mergers?
+
+    mass,sfr,sfr_err = get_mass_sfr(sf_mergers)
+
[…]

### 2014-07-30 mainsequence_morph.tex
Last edits from Zurich 2014 visit for KWW
Discussion & acknowledgedments
I updated the discussion at the bottom adding some key points on what I
think the result means. Also added my funding acknowledgements

@@
 
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Discussion text from KS}
+Our results show that the star-forming main sequence is remarkably robust to the details of the spatial distribution of star formation \textit{within} galaxies.
+Testing for a wide range of morphological sub-types of star-forming disk galaxies yields no statistically significant difference in the relative position of these sub-types viz a vis the main sequence.
+The number or pitch angle of spiral arms and the presence or absence of a large-scale bar are not correlated with any detectable increase or decrease in the efficiency of star formation.
+The system which regulates star formation in galaxies is thus either not affected by the details of the spatial distribution of star formation, or its regulatory effect is so strong that it wipes out any such effect in a short time.
+
+The most significant forcing event to the galaxy system known -- a major galaxy merger -- has only a slight effect.
+Star formation rates are increased by an average of X in major mergers.
+This shows just how stable the regulatory system in galaxies really is.
+Almost all simulations of galaxy mergers predict a steep increase in the star formation rate during first passage and final coalescence.
+The magnitude of this increase often depends on the details of the simulation, but can range from a factor of 10 to 100.
+In the low redshift universe sampled by SDSS and Galaxy Zoo, we find no evidence for an enhancement of such magnitude.
+This in turn suggests that the current generation of galaxy merger simulations miss a critical feedback mechanisms that prevents runaway peaks in star formation rates during mergers.
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+
 %%%%%%%%%%%%
@@
 
+KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
+
 Funding for the SDSS and SDSS-II has been provided by the Alfred P.

### 2014-08-04 gz_mainsequence.py
Green peas plot added

@@ -403,38 +403,17 @@ def plot_ms_greenpeas(sfr_sample):
 
     # Plot green peas
 
-    with fits.open('%s/mergers/mergers_mpajhu_bpt.fits' % ms_path) as f:
+    with fits.open('%s/greenpeas.fits' % ms_path) as f:
         data = f[1].data
 
-    #sf_mergers = data[(data['bpt'] == 1) & (data['mass_ratio'] <= 3)]
-    sf_mergers = data[(data['bpt'] == 1)]
+    sc = ax.scatter(data['M_STELLAR'],np.log10(data['SFR']), color='green',s = 10, marker='o')
 
-    sc = ax.scatter(sf_mergers['MEDIAN_MASS'],sf_mergers['MEDIAN_SFR'], c=sf_mergers['mass_ratio'], edgecolor='none',s = 50, marker='.', cmap=matplotlib.cm.RdBu, vmin=1.,vmax=10.)
-
-    ax.text(6.2,1.3,'Mergers', color='black')
+    ax.text(6.2,1.3,'Green peas', color='green')
 
     # Plot the best linear fits
 
     #au,bu = plot_fits('Mergers',sf_mergers,ax,'red')
     a1,a0 = plot_fits('Star-forming galaxies',sfr_sample,ax,'black',lw=1,ls='-')
-
-    # How many mergers fall above and below?
-
-    diff = sf_mergers['MEDIAN_SFR'] - (a0 + a1*sf_mergers['MEDIAN_MASS'])
-
-    # Fix same slope but different offset. What's the average difference between SF MS and mergers?
-
-    mass,sfr,sfr_err = get_mass_sfr(sf_mergers)
-
-    rms = []
-    xarr = np.linspace(0,1,100)
-    for x in xarr:
-        rms.append(np.sqrt(np.sum((sfr - (a0 + x + a1*mass))**2)))
-
-    offset = xarr[(np.abs(rms)).argmin()]
-    uline = ax.plot(np.linspace(6,12,100),np.polyval([a1,a0+offset],np.linspace(6,12,100)),color='red',linestyle='--',linewidth=1)
-
-    ax.text(6.2,0.9,'Offset = %.3f dex' % offset, color='black',fontsize=15)
 
     # Set the colorbars and labels
 
@@ -443,10 +422,6 @@ def plot_ms_greenpeas(sfr_sample):
[…]

### 2014-08-11 mainsequence_morph.tex
KWW draft finished; ready for feedback by KS and team

--- 2014-07-25 mainsequence_morph.tex
@@
 Observations at a range of redshifts have established that the star formation rate (SFR) of a galaxy is strongly correlated to its stellar mass ($M_\star$).
-This `main sequence' of star formation is nearly linear and at least at low redshift, has remarkably small scatter (refs).
-Recent observations of star-forming galaxies at high redshifts show that this main sequence remains out to high redshift with the normalisation of the main sequence shifting up so that galaxies of the same $M_\star$ have a higher SFR at high redshift (refs).
+This ``star-forming main sequence'' (SFMS) is nearly linear and at least at low redshift, has remarkably small scatter \citep{bri04}.
+Recent observations of star-forming galaxies at high redshifts show that this main sequence remains out to high redshift, but with its normalisation shifting up so that galaxies of the same $M_\star$ have a higher SFR at high redshift \citep{noe07,dad07}.
 The main sequence has been interpreted by \citet{bou10} and \citet{lil13} as the result of the balancing of inflows of cosmological gas and outflows due the feedback.
@@
 
-As star-forming galaxies exhibit a wide range of physical appearances in optical images, we can ask the natural question of whether the specifics of this physical appearance, and its underlying dynamical processes, have any effect on this homeostasis and therefore the galaxy's location relative to the SFR-$M_\star$ relation.
+As star-forming galaxies exhibit a wide range of physical appearances in optical images, we can ask the natural question of whether the specifics of this physical appearance, and its underlying dynamical processes, have any effect on this homeostasis and therefore the galaxy's location relative to the SFMS.
 If the details of a galaxy's physical appearance are correlated with position relative to the main sequence, then the dynamical processes that give rise to them -- such as bar formation and spiral arm pitch angle -- are a fundamental aspect of the galaxy's regulatory mechanism.
-If on the other hand they are not correlated, then there are two options: either they are simply not relevant, or the regulatory mechanism overcomes them in virtually all circumstances.
+If, on the other hand, these features are not correlated, then there are two options: either galaxy substructure is simply not relevant to the overall $M_\star$-SFR relationship, or the regulatory mechanism overcomes the local effect of substructure in all circumstances.
 This would speak to the strength of the regulator.
@@
 Merging pairs of galaxies are taken from the catalog of \citet{dar10a}, all of which lie in the redshift range $0.005<z<0.1$.
-Post-merger spheroidal galaxies without an obvious, separated companion \citep{car12} are specifically excluded from the sample.
-Detailed classifications of disk morphologies (arm pitch angle, number of spiral arms, presence of a galactic bar) are taken from the Galaxy~Zoo~2 (GZ2) catalog \citep{wil13}.
+Post-merger spheroidal galaxies without an obvious, separated companion are specifically excluded from the sample.
+Detailed classifications of disk morphologies, including arm pitch angle, number of spiral arms, and presence of a galactic bar, are taken from the Galaxy~Zoo~2 (GZ2) catalog \citep{wil13}.
 
@@
  \end{tabular}
-\tablecomments{Parameters are according to Equation~\ref{eqn-linearfit}.\label{tbl-fits}}
+\tablecomments{Parameters $\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit}.\label{tbl-fits}}
 \end{table}
 
-To analyze the $M_\star-SFR$ relationship, we apply a simple linear model for the total sample and subsamples.
+To parametrize the $M_\star-SFR$ relationship, we apply a simple linear model for the total sample and subsamples.
 We apply a least-squares fit where the data are weighted by the uncertainty in SFR (computed as the mean difference in the 16th and 84th percentiles from the MPA-JHU PDFs).
@@
 
-For the control sample, we plot in Figures~\ref{fig-number}-\ref{fig-mergers} the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local SDSS galaxies.
+For a control sample, we plot in Figures~\ref{fig-number}-\ref{fig-mergers} the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local SDSS galaxies.
 As demonstrated in previous papers, there is a fairly tight correlation between $M_\star$ and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
@@
 
-Figure~\ref{fig-number} overplots the $M_\star-SFR$ relationship for disk galaxies separated by their arm multiplicity.
+Figure~\ref{fig-number} overplots SFR as a function of $M_\star$ for disk galaxies separated by their arm multiplicity.
 The GZ2 data separates disk galaxies with visible spiral arms into categories of 1, 2, 3, 4, or more than four spiral arms; there is also an additional option if the number of spiral arms cannot be accurately determined.
@@
 
-1-armed spirals present an interesting case, with the majority of the population lying slightly above the fit to all star-forming spirals.
-This is consistent with the work of \citet{cas13}, who showed that 1-armed spirals in GZ2 are robust indicators of close interactions at projected distances of $r_p < 50~h^{-1}$~kpc.
-The underlying reason is that many ``1-armed spirals'' are in fact caused by bridges or tidal tails from interactions with a nearby companion; we discuss the likely role of merging/interacting galaxies in Figure~\ref{fig-mergers}.
+The one-armed spirals present an interesting case, with the majority of the population lying slightly above the fit to all star-forming spirals.
+This is consistent with the work of \citet{cas13}, who showed that one-armed spirals in GZ2 are robust indicators of close interactions at projected distances of $r_p < 50~h^{-1}$~kpc.
+The underlying reason is that many ``one-armed spirals'' are in fact caused by bridges or tidal tails from interactions with a nearby companion; we discuss the likely role of merging/interacting galaxies in Figure~\ref{fig-mergers}.
 
 Finally, galaxies with an uncertain number of spiral arms (although also with relatively low numbers) fall slightly below the mean star-forming main sequence relation.
-We conjecture that this is a consequence of galaxies that have likely already begun the process of quenching.
+One possibility is that this is a consequence of galaxies that have already begun the process of quenching.
 As a result, the star-formation rate is depleted and the contrast of spiral arms against the rest of the disk (which for visual identification is at least in part dependent on bright knots of recent star formation) makes the multiplicity more difficult to identify.
-{\it (\kevin: check colors of these galaxies and see if they lie in the green valley?
-Would be a nice test to see if they're consistent with the red herring model.)}
+However, the $(u-r)$ colors of these galaxies (uncorrected for dust extinction) are on average significantly bluer than green-valley late-types as identified in \citet{sch14}.
 
@@
 % Figure ms_arms_winding_weighted_pmed.pdf shows this.
-Not sure if we need to put it in the paper?
 
@@
 
-There is no significant difference between any of the morphological categories explored. Statistical test for how ``not different'' the categories are.
-
-This is interpreted as evidence that the regulation of the star formation rate is independent of the details of galactic structure as traced by the dynamics of the spiral arms.
-
-Conditional statements: if the situation above is true, then the following must apply.
-
-Bar results are in rough agreement with the mass-dependent trends seen in \citet{ell11}; strong difference is only seen at $M_\star>10^7~M_\odot$, which is at the very upper end of our range.
-
-Point that has not been made before; self-regulated systems where you can move parts around, but the total amount must be conserved.
-Process as a result cannot be simply regulated locally - the whole system must know about the rate of regulation.
-What does this say about the minimum lifetime of the features as a dynamical timescale $\tau_{dyn}$?
-
-The biggest forcing we can think of for the system is a major merger.
-Even that doesn't push it too far off the main sequence, indicating short timescales and higher levels of feedback.
-Figure~\ref{fig-mergers} shows the relation for systems of merging galaxies \citep{dar10a}.
-For these systems, there is a small increase in the offset of the $M_\star-SFR$ relation, but none in the slope.
-The difference is $\sim0.2$~dex, an increase of only $\sim70\%$ in star-formation rate for a given mass.
-There are a very small number of galaxies whose star formation rates lie more than an order of magnitude above the standard relation, but the numbers are too small to make a significant contribution to the SFR density of the local Universe.
-
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_mergers.pdf}
-\caption{Stellar mass vs.
-star formation rate  as in Figure~\ref{fig-number}.
-for 2,978~merging galaxies in GZ, as compared to the broader star-forming population.
-When fixing the slope of the star-forming main sequence and allowing the offset to vary, mergers have higher SFR of $\sim0.2$~dex.
+\includegraphics[angle=0,width=7.0in]{figures/ms_mergers_both.pdf}
+\caption{\textbf{Left:} Stellar mass vs.
+star formation rate as in Figure~\ref{fig-number} for 2,978~merging galaxies in GZ, compared to the broader star-forming population.
+Merging systems are colour-coded by the mass ratio of the primary-to-secondary galaxy; there is no clear difference in the merging populations with regard to the SFMS when comparing major to minor mergers.
+When fixing the slope of the star-forming main sequence and allowing the offset to vary, mergers have higher SFRs by $\sim0.3$~dex.
+\textbf{Right:} Same as left plot, but binned and colour-coded by merger fraction ($N_\textrm{mergers}/N_\textrm{star-forming galaxies})$.
+Overplotted linear fits are same as before.
+This demonstrates that the galaxies that lie furthest above the SFMS are $>50\%$ mergers.
 \label{fig-mergers}}
@@
 
-These results confirm the trend in specific star formation rate seen by \citet{dar10}.
-We know that this is true at low redshift, but not at higher redshift.
-\citet{rod11} show a significant increase at $1.5<z<2.5$, likely due to the \emph{higher gas fraction} in galaxies at these redshifts.
-Also significant difference in disks at low/high redshift when using disk surface density instead of mass \citep{dad10}.
-\citet{elb11} show that ``compact'' galaxies lie significantly off the SFR-MS using {\it Herschel} data.
-In the local Universe, green pea galaxies are the only objects that significantly exceed the main sequence, as evidenced by their sSFR \citep{car09}.
+Our results show that the star-forming main sequence is remarkably robust to the details of the spatial distribution of star formation \textit{within} galaxies.
+Testing for a wide range of morphological sub-types of star-forming disk galaxies yields no statistically significant difference in the relative position of these sub-types vis-\'a-vis the main sequence.
+Neither the number or pitch angle of spiral arms, or the presence of a large-scale bar are correlated with any detectable increase or decrease in the efficiency of star formation.
+The system which regulates star formation in galaxies is thus either not affected by the details of the spatial distribution of star formation, or its regulatory effect is so strong that it wipes out any such effect in a short time.
 
-Connection between galaxy structure and quenching efficiency - \citet{oma14} found a simple dependence on $B/T$ for SDSS DR7 data.
+The agreement of all sub-varieties of star-forming galaxies is supported by the close agreement to the linear fits to the data for all well-sampled categories (Table~\ref{tbl-fits}).
+This tracks only the slope and offset of the distribution, however, and not its width.
+We thus also compared the sample standard deviation ($\sigma_{SFR}$) as a function of mass of the star-forming galaxy population to its various subsamples.
+The value of $\sigma_{SFR}$ monotonically decreases with mass over the range $6.0<\log(M/M_\odot)<11.5$.
+For all populations examined in this paper, though, the widths of their distributions are consistent with the broader population.
+% Figure to be shown in Appendix?
 
-\citet{abr14} find that the sSFR in galactic disks is independent of mass.
+\citet{abr14} found that by normalizing galaxies by the stellar mass of the disk alone, the slope of the SFMS is consistent with only a linear trend (removing any dependence on mass).
+Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, and/or environment (among other factors).
+Our results show that the neither of the first two factors play dominant roles in controlling $\sigma_{SFR}$, at least as far as major dynamical drivers (such as strong bars or additional arms) are concerned.
+Thus while the overall bulge strength does affect the position of a galaxy on the SFMS \citep{mar09,lan14,oma14}, the structure of the \emph{disk itself} does not.
 
-Check the mergers against the IR-derived star formation rates of \citet{jar13}?
+The lack of any difference in SFR as a function of mass for barred vs.
+unbarred galaxies is in general agreement with \citet{ell11}, who find an increase of $\Delta~\textrm{SFR}\sim0.15$~dex, but only for galaxies with $M_\star>10^{10.7}~M_\odot$.
+This is at the very upper end of the mass range probed in Figure~\ref{fig-bar}.
+If the increase in star formation is limited to the central kpc of the disk (as they demonstrate using fibre SFR measurements), an increase in possible bar-driven SFR increase is seen down to $M_\star=10^{10}~M_\odot$.
+
+Amongst individual galaxies that lie significantly off the SFMS, compact starburst galaxies show the largest increase in SFR at a given mass \citep{elb11}.
+In the local Universe, these include optically-identified ``green pea'' galaxies, which have unusually high sSFR and can lie more than 1~dex above the SFMS \citep{car09}.
+While few known green pea galaxies have detailed imaging available, their most common morphology is in a clumpy arrangement with knots of bright star formation.
+There is thus little evidence for a dynamically-settled disk (in any arrangment) for galaxies in the local Universe lying significantly above the SFMS.
+
+The most significant forcing event to the galaxy system known -- a major galaxy merger -- has only a slight effect.
+Star formation rates are increased by an average of 0.29~dex (less than a factor of 2) in major mergers (Figure~\ref{fig-mergers}).
+\citet{dar10} showed that in the local ($z<0.1$) Universe, galaxies involved in major mergers do induce intense bursts of star formation, but specifically in only the spiral (disc) galaxies taking part and increasing the local sSFR by only a factor $\sim2$.
+This increase in star formation is much stronger in galaxies at $1.5<z<2.5$, likely due to the higher gas fractions \citep{dad10,rod11}.
+
+The location of mergers on the present-day SFMS shows just how stable the regulatory system in galaxies really is.
+Almost all simulations of galaxy mergers predict a steep increase in the star formation rate during both first passage and final coalescence \citep[eg,][]{hop08}.
+The magnitude of this increase often depends on the details of the simulation, but can range from a factor of 10 to 100.
+In the low-redshift universe sampled by SDSS and Galaxy~Zoo, we find no evidence for an enhancement of such magnitude.
+This in turn suggests that the current generation of galaxy merger simulations misses critical feedback mechanisms that prevent runaway peaks in star formation rates during mergers.
+
+\section{Conclusions}
+
+We analyze for the first time the detailed structure of disks in star-forming galaxies as related to their position on the $M_\star$-SFR relation, using morphological classifications from the Galaxy~Zoo~2 project.
+We find that neither the slope nor the dispersion of the star-forming galaxies are affected when splitting the sample into different categories of disks, including barred/unbarred galaxies, the pitch angle of spiral arms, or the number of spiral arms.
+
+The uniformity of disk galaxies along the SFMS, regardless of their kpc-scale structure, argues for the system as a whole being strongly self-regulated.
+While smaller regions of the galaxy can experience (likely temporary) increases in star formation, the amount of star formation in the disk as a whole is conserved.
+This is preserved even for the strongest forcing events, including major mergers; the physics governing the SFMS are primarily driven by the overall mass of the system.
+This means that simulations of galaxy evolution must be able to meet the challenge of simultaneously reproducing the wide range of disk morphologies observed along the Hubble sequence (and in various merger stages) while simultaneously managing feedback so that \emph{all} disk types maintain the same tight relationship to the SFMS.
 

### 2014-08-11 gz_mainsequence.py

@@ -15,12 +15,9 @@ ms_path = '%s/gzmainsequence' % gz_path
 fig_path = '%s/gzmainsequence/figures' % gz_path
 fits_path = '%s/fits' % gz_path
 
-def get_data(mergers=False):
+def get_data():
 
-    if mergers:
-        filename = '%s/mergers/mergers_mpajhu_gz2.fits' % ms_path
-    else:
-        filename = '%s/mpajhu_gz2.fits' % fits_path
+    filename = '%s/mpajhu_gz2.fits' % fits_path
 
     with fits.open(filename) as f:
         data = f[1].data
@@ -51,10 +48,10 @@ def get_mass_sfr(sfr_sample):
 
     return mass,sfr,sfr_err
 
-def bins():
+def bins(mass_min=6,mass_max=13,sfr_min=-5,sfr_max=2,nbins=50):
 
-    mass_bins = np.linspace(6,13,50)
-    sfr_bins = np.linspace(-5,2,50)
+    mass_bins = np.linspace(mass_min,mass_max,nbins)
+    sfr_bins = np.linspace(sfr_min,sfr_max,nbins)
 
     return mass_bins,sfr_bins
     
@@ -334,7 +331,7 @@ def plot_ms_mergers(sfr_sample):
 
     sc = ax.scatter(sf_mergers['MEDIAN_MASS'],sf_mergers['MEDIAN_SFR'], c=sf_mergers['mass_ratio'], edgecolor='none',s = 50, marker='.', cmap=matplotlib.cm.RdBu, vmin=1.,vmax=10.)
 
-    ax.text(6.2,1.3,'Mergers', color='black')
+    ax.text(6.2,1.3,'Mergers', color='black',fontsize=20)
 
     # Plot the best linear fits
 
@@ -374,16 +371,11 @@ def plot_ms_mergers(sfr_sample):
 
     return None
 
-def plot_ms_merger_fraction(sfr_sample):
-
-
-    return None
-
 def plot_ms_greenpeas(sfr_sample):
 
     # Plot
 
-    fig = plt.figure(4,(10,8))
+    fig = plt.figure(5,(10,8))
     fig.clf()
 
     fig.subplots_adjust(left=0.08,bottom=0.15,hspace=0,wspace=0)
@@ -423,5 +415,358 @@ def plot_ms_greenpeas(sfr_sample):
     cb.set_label(r'$N_\mathrm{star-forming\/galaxies}$' ,fontsize=16)
 
[…]

### 2014-08-11 mainsequence_morph.tex
Updated fonts and captions for figures

@@
 We measure the mass-star formation relation in disk galaxies at $z<0.05$, using Galaxy Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
-We examine the number of arms, their average pitch angle, and the presence of a galactic bar, and show that both the slope and dispersion of the SFR-$M_\star$ relation is constant when varying all the above parameters.
+We examine the number of spiral arms, their average pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
+We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only drive the galaxies off the main relation by $\sim0.3$~dex; this is a significant reduction over the increase seen in merging systems at $z>1$.
+Of the galaxies lying significantly above the $M_\star$-SFR relation in the local Universe, more than $50\%$ are mergers.
 We interpret this as evidence that the spiral arms, which are imperfect reflections of the galaxy's current gravitational potential, are either fully independent of the basic quenching relation or are completely overwhelmed by the combination of outflows and feedback.
-The arrangement of the star formation can be changed (as demonstrated by the filling factor of the disk), but the system \emph{as a whole} regulates itself.
-We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only drive the galaxies off the main relation by $\sim0.3$~dex; this is a significant reduction over merging systems at $z>1$.
+The arrangement of the star formation can be changed (as demonstrated by the filling factor of the disk), but the system \emph{as a whole} regulates itself even in the presence of strong dynamical forcing.
 \end{abstract}
@@
 If, on the other hand, these features are not correlated, then there are two options: either galaxy substructure is simply not relevant to the overall $M_\star$-SFR relationship, or the regulatory mechanism overcomes the local effect of substructure in all circumstances.
-This would speak to the strength of the regulator.
+This ultimately relates to the physical processes that control the overall strength of the regulator in each galaxy.
 
@@
 The total sample analyzed contains 52,685 star-forming galaxies.
-These are selected from the GZ2 spectroscopic sample with $z<0.1$, $M_r<-19.5$, and classified as actively star-forming (BPT$=1$) from the MPA-JHU emission line measurements.
+These are selected from the GZ2 spectroscopic sample with $z<0.1$, $M_r<-19.5$, and classified as actively star-forming ($BPT=1$) from the MPA-JHU emission line measurements.
 The average color for the star-forming galaxies is relatively blue, with $(u-r)=1.7\pm0.6$.
-Subsets of the star-forming galaxies are listed in Table~\ref{tbl-fits}.
 
@@
 
-\emph{Come up with a more sensible measure of the uncertainty - the formal covariance elements clearly don't represent the dispersion in the main sequence. Interquartile range?}
-
 %%%%%%%%%%%%
@@
 \includegraphics[angle=0,width=7.0in]{figures/ms_arms_number.pdf}
-\caption{Stellar mass vs.
-star formation rate; grayscale colors are the distribution of all star-forming galaxies from the MPA-JHU catalog.
-Colored points in each panel show spiral galaxies with ``tight'', ``medium'', and ``loose'' spiral arms as identified by morphology flags in GZ2.
-Dotted lines show the weighted least-squares linear fit to the population as split by pitch angle; the solid line is the fit to all star-forming galaxies.
+\caption{Total star formation rate as a function of stellar mass; grayscale colors are the distribution of all star-forming galaxies in SDSS from the MPA-JHU DR7 catalog.
+Colored points in each panel show spiral galaxies with 1, 2, 3, 4, more than four, or ``uncertain'' numbers of spiral arms per galaxy, as identified by GZ2 morphology flags.
+Dotted lines show the weighted least-squares linear fit to each population as split by arm multiplicity; the solid line is the fit to all of the star-forming galaxies.
 \label{fig-number}}
@@
 \includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding.pdf}
-\caption{Stellar mass vs.
-star formation rate; grayscale colors are the distribution of all star-forming galaxies as in Figure~\ref{fig-number}.
-From left to right: red, green, and blue points spiral galaxies with ``tight'', ``medium'', and ``loose'' spiral arms as identified by morphology flags in GZ2.
-Dotted lines show the weighted least-squares linear fit to the population as split by pitch angle; the solid line is the fit to all star-forming galaxies.
+\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.
+From left to right: red, green, and blue points are spiral galaxies with ``tight'', ``medium'', and ``loose'' winding spiral arms as identified by GZ2 morphology flags.
+Dotted lines show the weighted least-squares linear fit as split by pitch angle; the solid line is the fit to all star-forming galaxies.
 \label{fig-winding}}
@@
 \includegraphics[angle=0,width=7.0in]{figures/ms_bar_contour.pdf}
-\caption{Stellar mass vs.
-star formation rate; grayscale colors are the distribution of all star-forming galaxies as in Figure~\ref{fig-number}.
+\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.
 Left: blue contours show the distribution of barred galaxies ($p_\textrm{bar}\ge0.4$ for previously-identified disks) from GZ2.
@@
 \includegraphics[angle=0,width=7.0in]{figures/ms_mergers_both.pdf}
-\caption{\textbf{Left:} Stellar mass vs.
-star formation rate as in Figure~\ref{fig-number} for 2,978~merging galaxies in GZ, compared to the broader star-forming population.
-Merging systems are colour-coded by the mass ratio of the primary-to-secondary galaxy; there is no clear difference in the merging populations with regard to the SFMS when comparing major to minor mergers.
-When fixing the slope of the star-forming main sequence and allowing the offset to vary, mergers have higher SFRs by $\sim0.3$~dex.
-\textbf{Right:} Same as left plot, but binned and colour-coded by merger fraction ($N_\textrm{mergers}/N_\textrm{star-forming galaxies})$.
-Overplotted linear fits are same as before.
-This demonstrates that the galaxies that lie furthest above the SFMS are $>50\%$ mergers.
+\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.
+Left: Coloured points show 2,978~merging galaxies from \citet{dar10a}.
+Mergers are colour-coded by the mass ratio of the primary and secondary galaxies; there is no clear difference in the merging populations with regard to the SFMS when comparing major to minor mergers.
+When fixing the slope of the star-forming main sequence and allowing the offset to vary, mergers (dotted line) have higher SFRs by $\sim0.3$~dex compared to all star-forming galaxies (solid line).
+Right: Star-forming galaxies binned and colour-coded by merger fraction ($N_\textrm{mergers}/N_\textrm{star-forming galaxies})$.
+Overplotted lines are the same as left plot.
+Of the galaxies that lie furthest above the SFMS, more than $50\%$ are unambiguous mergers.
 \label{fig-mergers}}
@@
 
-The most significant forcing event to the galaxy system known -- a major galaxy merger -- has only a slight effect.
-Star formation rates are increased by an average of 0.29~dex (less than a factor of 2) in major mergers (Figure~\ref{fig-mergers}).
-\citet{dar10} showed that in the local ($z<0.1$) Universe, galaxies involved in major mergers do induce intense bursts of star formation, but specifically in only the spiral (disc) galaxies taking part and increasing the local sSFR by only a factor $\sim2$.
-This increase in star formation is much stronger in galaxies at $1.5<z<2.5$, likely due to the higher gas fractions \citep{dad10,rod11}.
+As a comparison to the kpc-scale structures discussed above, we analyze the impact of the most significant forcing event to a galaxy system known -- a major galaxy merger (Figure~\ref{fig-mergers}).
+In these systems (which are in various stages of coalescence) the star formation rates are increased by only an average of 0.29~dex, corresponding to less than a factor of two overall.
+\citet{dar10} showed that in the local ($z<0.1$) Universe, galaxies with intense bursts of star formation are limited to only the spiral (disc) galaxies.
+This increase in star formation for mergers does show a strong evolution in redshift out to at least $1.5<z<2.5$, likely due to the higher gas fractions involved \citep{dad10,rod11}.
 
@@
 
-\clearpage
-
 %%%%%%%%%%%%

### 2014-08-11 gz_mainsequence.py

@@ -129,7 +129,7 @@ def plot_ms_arms_number(sfr_sample):
         if idx < 3:
             ax.get_xaxis().set_ticks([])
         if idx == 0 or idx == 3:
-            ax.set_ylabel('SFR '+r'$[M_\odot/\mathrm{yr}]$',fontsize=16)
+            ax.set_ylabel('SFR '+r'$[\log\/M_\odot/\mathrm{yr}]$',fontsize=16)
         else:
             ax.get_yaxis().set_ticks([])
 
@@ -189,10 +189,10 @@ def plot_ms_bars(sfr_sample,contour=False):
         h2 = ax.hist2d(mass,sfr,bins=50,cmap = cm.gray_r, norm=LogNorm())
         ax.set_xlim(6,11.5)
         ax.set_ylim(-4,2)
-        ax.set_xlabel('Stellar mass (log'+r'$\/M/M_\odot$)',fontsize=20)
+        ax.set_xlabel('Stellar mass (log '+r'$M/M_\odot$)',fontsize=20)
 
         if idx == 0:
-            ax.set_ylabel('SFR '+r'$[M_\odot/\mathrm{yr}]$',fontsize=16)
+            ax.set_ylabel('SFR '+r'$[\log\/M_\odot/\mathrm{yr}]$',fontsize=20)
         else:
             ax.get_yaxis().set_ticks([])
 
@@ -223,7 +223,7 @@ def plot_ms_bars(sfr_sample,contour=False):
     box = ax.get_position()
     axColorbar = plt.axes([box.x0*1.05 + box.width * 0.95, box.y0, 0.01, box.height])
     cb = plt.colorbar(h2[3],cax = axColorbar, orientation="vertical")
-    cb.set_label(r'$N_\mathrm{star-forming\/galaxies}$' ,fontsize=16)
+    cb.set_label(r'$N_\mathrm{star-forming\/galaxies}$' ,fontsize=18)
 
     fig.savefig('%s/ms_bar%s.pdf' % (fig_path,filestr), dpi=200)
 
@@ -254,7 +254,7 @@ def plot_ms_arms_winding(sfr_sample,weight_by_pmed=False):
         ax.set_xlim(6,11.5)
         ax.set_ylim(-4,2)
         if idx == 0:
-            ax.set_ylabel('SFR '+r'$[M_\odot/\mathrm{yr}]$',fontsize=16)
[…]

### 2014-08-12 mainsequence_morph.tex
Updated intro

@@
 
-Discuss (\kevin) seminal work of \citet{pen10a,pen12,pen14a,pen14} on gas regulator model and how mass/environment drive galaxy evolution.
+The fact that star-forming galaxies live on the SFMS is one of the key observations that has been driving the development of new descriptions of how galaxies evolve.
+\citet{pen10a,pen12} argue that galaxies grow in stellar mass during their life as star-forming galaxies on the main sequence before being quenched either by an external mechanism (environment or satellite quenching) or by an internal mechanism (mass quenching).
+This life on the main sequence is thus governed by the action of the regulator balancing gas in- and outflows \citet{lil13}, making it the central process in galaxy evolution.
 

### 2014-09-11 paper/mainsequence_morph.tex
Added potential co-author list, 1st round of comments

--- 2014-08-12 mainsequence_morph.tex
@@
 \author{Kyle Willett\altaffilmark{1}, Kevin Schawinski\altaffilmark{2}, etc.}
+% People who want to be co-authors:
+% Ivy Wong
+% Karen Masters
+% Ramin Skibba
+% Bob Nichol
+% Tom Melvin
+% Edmond Cheung
+% Chris Lintott
+% Bill Keel
+% Sugata Kaviraj
 
@@
 % Hello, @overheardonastroph!
+
+%@arxiver{ms_bar_contour.pdf,ms_mergers_both.pdf}
 
@@
 In this paper, we use the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with the largest database of visual classifications of galaxy structure and morphology ever assembled from the Galaxy Zoo citizen science projects \citep{lin08,lin11,wil13} to test whether galaxy structure affects their star formation properties.
+We use the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
 
@@
 
-Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04}.
+Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04,sal07}.
 We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation.
@@
 This increase in star formation for mergers does show a strong evolution in redshift out to at least $1.5<z<2.5$, likely due to the higher gas fractions involved \citep{dad10,rod11}.
+The projected separation between galaxies in which this occurs, based on both the observed merger fraction and sSFR is $\sim0.1$~Mpc$/h$ \citep{ski09}.
 
@@
 
-We thank Rory Smith and Lucio Mayer for useful discussions. This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05}. 
+We thank Rory Smith and Lucio Mayer for useful discussions.
+This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05} and Astropy, a community-developed core Python package for astronomy \citep{ast13}.
 %The development of Galaxy Zoo 2 was supported by The Leverhulme Trust.

### 2014-09-16 paper/mainsequence_morph.tex
Incorporated comments by RS, OIW, TM

@@
 We examine the number of spiral arms, their average pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
-We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only drive the galaxies off the main relation by $\sim0.3$~dex; this is a significant reduction over the increase seen in merging systems at $z>1$.
+We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only boost the SFR above the main relation by $\sim0.3$~dex; this is a significant reduction over the increase seen in merging systems at $z>1$.
 Of the galaxies lying significantly above the $M_\star$-SFR relation in the local Universe, more than $50\%$ are mergers.
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_arms_number.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/ms_arms_number_weighted_contour.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the distribution of all star-forming galaxies in SDSS from the MPA-JHU DR7 catalog.
-Colored points in each panel show spiral galaxies with 1, 2, 3, 4, more than four, or ``uncertain'' numbers of spiral arms per galaxy, as identified by GZ2 morphology flags.
+Coloured contours in each panel show spiral galaxies weighted by the GZ2 likelihoods of hosting 1, 2, 3, 4, more than four, or ``uncertain'' numbers of spiral arms, respectively.
 Dotted lines show the weighted least-squares linear fit to each population as split by arm multiplicity; the solid line is the fit to all of the star-forming galaxies.
@@
 The GZ2 data separates disk galaxies with visible spiral arms into categories of 1, 2, 3, 4, or more than four spiral arms; there is also an additional option if the number of spiral arms cannot be accurately determined.
-There are a total of 14,179 galaxies with flags for arm multiplicity (indicating a high level of agreement among classifiers) in the GZ2 data.
-Of those, two-armed spirals are by far the most common, comprising 85\% of the total.
-This is also the only multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\sun$ are detected.
+For this analysis, galaxies in each mass/SFR bin is weighted by the vote fraction for the morphology being tested.
+Two-armed spirals are the most common multiplicity in the GZ2 sample.
 
-The fit to the star-forming main sequence for two-armed spirals tighly follows that of that for all spiral galaxies, with both the slope and offset of the linear fits completely consistent with each other (Table~\ref{tbl-fits}).
-Similarly, the fits for 3, 4, and $5+$-armed spirals are also consistent with the main relation (although all three have much lower numbers which affect the quality of the fit).
+The fit to the star-forming main sequence for the six sub-samples of spiral galaxies tightly follows that of that for the total disk population.
+Both the slopes and offsets of each linear fit are completely consistent within the formal fitting errors (Table~\ref{tbl-fits}).
+There are too few galaxies with reliable spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all multiplicities at $10^8<M_\star/M_\sun<10^{11}$.
 
-The one-armed spirals present an interesting case, with the majority of the population lying slightly above the fit to all star-forming spirals.
+The one-armed spirals present an interesting case, with the fit to the weighted population lying slightly \emph{above} that of all star-forming spirals.
 This is consistent with the work of \citet{cas13}, who showed that one-armed spirals in GZ2 are robust indicators of close interactions at projected distances of $r_p < 50~h^{-1}$~kpc.
@@
 
-Finally, galaxies with an uncertain number of spiral arms (although also with relatively low numbers) fall slightly below the mean star-forming main sequence relation.
+The two-armed spirals and those with uncertain multiplicities are the only morphologies that extend slightly below the SFMS.
 One possibility is that this is a consequence of galaxies that have already begun the process of quenching.
@@
 However, the $(u-r)$ colors of these galaxies (uncorrected for dust extinction) are on average significantly bluer than green-valley late-types as identified in \citet{sch14}.
+
+We have repeated the analysis above for the sub-sample of disk galaxies for which the spiral multiplicity is determined with high confidence ($p_\textrm{arms~number} > 0.8$) by GZ2, thus eliminating ``intermediate'' galaxies for which the morphology is uncertain.
+These galaxies ($N=14,148$) is dominated by two-armed spirals, which are the only multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\sun$ are detected.
+Our results for the SFMS are qualitatively the same as when using the weighting scheme, although we note that there are too few examples ($N<10$) of either three- or four-armed spirals for a reliable fit.
+The offset of the one-armed spirals above the SFMS is also significantly more pronounced when using high-confidence morphologies.
 
@@
 In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the medium option at the 80\% level which sets the flag.
-Plotting the same star-forming main sequence diagram as a function of $p_{\rm medium}$, which more accurately tracks the pitch angle distribution, also closely follows the main star-forming main sequence.
-% Figure ms_arms_winding_weighted_pmed.pdf shows this.
+We have extended this analysis by plotting the same star-forming main sequence diagram as a function of $p_\textrm{arms~winding}$, which more accurately tracks the pitch angle distribution.
+In this case, it also closely follows the main star-forming main sequence (Figure~\ref{fig-winding_weighted}).
 
@@
 In other words, the presence of a bar does not affect the galaxy's position on the star-forming main sequence.
+
+The agreement of all sub-varieties of star-forming galaxies is supported by the close agreement to the linear fits to the data for all well-sampled categories (Table~\ref{tbl-fits}).
+This tracks only the slope and offset of the distribution, however, and not its width.
+We thus also compared the sample standard deviation ($\sigma_{SFR}$) as a function of mass of the star-forming galaxy population to its various subsamples.
+The value of $\sigma_{SFR}$ monotonically decreases with mass over the range $6.0<\log(M/M_\odot)<11.5$.
+For all populations examined in this paper, though, the widths of their distributions are consistent with the broader population (Figure~\ref{fig-sigma}).
+
+\begin{figure}
+%\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
+\includegraphics[angle=0,width=3.5in]{figures/sigma_mstar.pdf}
+\caption{Width of the star-forming main sequence ($\sigma$) as a function of stellar mass, as measured by the sample standard deviation.
+Black points represent the entire star-forming population.
+The various disk subsamples are overplotted as lines; colours are the same as the respective plots in Figures~\ref{fig-number}-\ref{fig-bar} and \ref{fig-mergers}.
+Morphological categories or mass ranges with fewer than 10 galaxies/bin are not plotted; this includes all mass ranges for 3-, 4-, and more than 4-armed spirals.
+\label{fig-sigma}}
+\end{figure}
 
@@
 The system which regulates star formation in galaxies is thus either not affected by the details of the spatial distribution of star formation, or its regulatory effect is so strong that it wipes out any such effect in a short time.
-
-The agreement of all sub-varieties of star-forming galaxies is supported by the close agreement to the linear fits to the data for all well-sampled categories (Table~\ref{tbl-fits}).
-This tracks only the slope and offset of the distribution, however, and not its width.
-We thus also compared the sample standard deviation ($\sigma_{SFR}$) as a function of mass of the star-forming galaxy population to its various subsamples.
-The value of $\sigma_{SFR}$ monotonically decreases with mass over the range $6.0<\log(M/M_\odot)<11.5$.
-For all populations examined in this paper, though, the widths of their distributions are consistent with the broader population.
-% Figure to be shown in Appendix?
 
@@
 
+\appendix
+\begin{figure*}
+\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding_weighted.pdf}
+\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-winding}.
+From left to right: colormaps show spiral galaxies weighted by the GZ2 vote fractions for ``tight'', ``medium'', and ``loose'' winding spiral arms.
+Dotted lines show the weighted least-squares linear fit as split by pitch angle; the solid line is the fit to all star-forming galaxies.
+\label{fig-winding_weighted}}
+\end{figure*}
+
 \end{document}

### 2014-09-16 gz_mainsequence.py

@@ -7,12 +7,13 @@ from matplotlib import cm
 from matplotlib.colors import LogNorm
 from matplotlib.font_manager import FontProperties
 from astropy.io import fits
+from scipy.linalg.basic import LinAlgError
 
 plt.ion()
 
 gz_path = '/Users/willettk/Astronomy/Research/GalaxyZoo'
-ms_path = '%s/gzmainsequence' % gz_path
-fig_path = '%s/gzmainsequence/figures' % gz_path
+gzm_path = '%s/gzmainsequence' % gz_path
+fig_path = '%s/paper/figures' % gzm_path
 fits_path = '%s/fits' % gz_path
 
 def get_data():
@@ -55,15 +56,28 @@ def bins(mass_min=6,mass_max=13,sfr_min=-5,sfr_max=2,nbins=50):
 
     return mass_bins,sfr_bins
     
-def fit_mass_sfr(sample,weighted=True):
+def fit_mass_sfr(sample,morph,wbe=False,wbm=False):
 
     # Retrieve mass, star formation rate, and error for subsample from MPA-JHU catalog
     mass,sfr,sfr_err = get_mass_sfr(sample)
 
-    # Use mean difference between 16th and 84th percentiles to the median value for the weights on fit
+    assert wbe != wbm or wbm == False, \
+        'Cannot weight both by error and morphology'
 
-    w = 1./(sfr_err**2)
-    weights = None if weighted else w
+    # Weight #1: mean difference between 16th and 84th percentiles to the median value for the weights on fit
+    if wbe:
+        weights = 1./(sfr_err**2)
+        #print 'Using SFR weights'
+
+    # Weight #2: morphological vote fraction
+    if wbm:
+        weights = sample[(sample['MEDIAN_MASS'] > -99) & (sample['MEDIAN_SFR'] > -99)]['%s_debiased' % morph]
+        #print 'Using morphology weights'
+
+    # Weight #3: unweighted
+    if not wbe and not wbm:
+        weights = None
+        #print 'No weights'
 
     # Find coefficients with polyfit
 
@@ -71,14 +85,14 @@ def fit_mass_sfr(sample,weighted=True):
 
     return a,b,v
 
[…]

### 2014-09-19 paper/mainsequence_morph.tex
Added feedback from RCN, EC

@@
 Figure~\ref{fig-bar} shows the star-forming main sequence for both barred and unbarred galaxies.
-Although the fraction of barred galaxies potentially varies as a function of stellar mass \citep{mas11c}, both the linear fits and ranges of the sub-populations are consistent with all star-forming galaxies.
+Although the fraction of barred galaxies potentially varies as a function of stellar mass \citep{mas11c,che13}, both the linear fits and ranges of the sub-populations are consistent with all star-forming galaxies.
 In other words, the presence of a bar does not affect the galaxy's position on the star-forming main sequence.
@@
 Our results show that the neither of the first two factors play dominant roles in controlling $\sigma_{SFR}$, at least as far as major dynamical drivers (such as strong bars or additional arms) are concerned.
-Thus while the overall bulge strength does affect the position of a galaxy on the SFMS \citep{mar09,lan14,oma14}, the structure of the \emph{disk itself} does not.
+Thus while the overall bulge strength does affect the position of a galaxy on the SFMS \citep{mar09,che12,fan13,lan14,oma14}, the structure of the \emph{disk itself} does not.
 

### 2014-09-19 gz_mainsequence.py

@@ -7,7 +7,10 @@ from matplotlib import cm
 from matplotlib.colors import LogNorm
 from matplotlib.font_manager import FontProperties
 from astropy.io import fits
+
+from scipy.stats import ks_2samp
 from scipy.linalg.basic import LinAlgError
+from astroML.plotting import hist as histML
 
 plt.ion()
 
@@ -15,6 +18,11 @@ gz_path = '/Users/willettk/Astronomy/Research/GalaxyZoo'
 gzm_path = '%s/gzmainsequence' % gz_path
 fig_path = '%s/paper/figures' % gzm_path
 fits_path = '%s/fits' % gz_path
+
+aw_tasks = ['t10_arms_winding_'+r for r in ('a28_tight','a29_medium','a30_loose')]
+an_tasks = ['t11_arms_number_'+r for r in ('a31_1','a32_2','a33_3','a34_4','a36_more_than_4','a37_cant_tell')]
+an_colors = ('red','orange','yellow','green','blue','purple')
+aw_colors = ('red','green','blue')
 
 def get_data():
 
@@ -826,8 +834,6 @@ def fracdev(sfr_sample):
 
     # Find plurality answer for multiplicity question
 
-    an_colors = ('red','orange','yellow','green','blue','purple')
-    aw_colors = ('red','green','blue')
     an_1 = sfr_sample[spiral & \
                        (sfr_sample['t11_arms_number_a31_1_debiased'] >= sfr_sample['t11_arms_number_a32_2_debiased']) & \
                        (sfr_sample['t11_arms_number_a31_1_debiased'] >= sfr_sample['t11_arms_number_a33_3_debiased']) & \
@@ -1010,8 +1016,6 @@ def fracdev_cdf(sfr_sample):
 
     # Find plurality answer for multiplicity question
 
-    an_colors = ('red','orange','yellow','green','blue','purple')
-    aw_colors = ('red','green','blue')
     an_1 = sfr_sample[spiral & \
                        (sfr_sample['t11_arms_number_a31_1_debiased'] >= sfr_sample['t11_arms_number_a32_2_debiased']) & \
                        (sfr_sample['t11_arms_number_a31_1_debiased'] >= sfr_sample['t11_arms_number_a33_3_debiased']) & \
[…]

### 2014-09-27 paper/mainsequence_morph.tex
Starting to volume-limit sample

@@
 % Sugata Kaviraj
+% Brooke Simmons
 
@@
 Of the galaxies lying significantly above the $M_\star$-SFR relation in the local Universe, more than $50\%$ are mergers.
-We interpret this as evidence that the spiral arms, which are imperfect reflections of the galaxy's current gravitational potential, are either fully independent of the basic quenching relation or are completely overwhelmed by the combination of outflows and feedback.
-The arrangement of the star formation can be changed (as demonstrated by the filling factor of the disk), but the system \emph{as a whole} regulates itself even in the presence of strong dynamical forcing.
+We interpret this as evidence that the spiral arms, which are imperfect reflections of the galaxy's current gravitational potential, are either fully independent of the various quenching mechanisms or are completely overwhelmed by the combination of outflows and feedback.
+The arrangement of the star formation can be changed, but the system \emph{as a whole} regulates itself even in the presence of strong dynamical forcing.
 \end{abstract}
@@
 The morphological data is drawn from citizen science classifications in Galaxy~Zoo.
+Detailed classifications of disk morphologies, including arm pitch angle, number of spiral arms, and presence of a galactic bar, are taken from the Galaxy~Zoo~2 (GZ2) catalog \citep{wil13}.
+We use a volume-limited sample with $0.005<z<0.085$; the lower bound removes galaxies with large angular sizes for which fibre-derived quantities do not sample the full disk, while the upper limit is chosen as a compromise between sample size and the effective classification distance of the GZ2 morphologies.
+
 Merging pairs of galaxies are taken from the catalog of \citet{dar10a}, all of which lie in the redshift range $0.005<z<0.1$.
 Post-merger spheroidal galaxies without an obvious, separated companion are specifically excluded from the sample.
-Detailed classifications of disk morphologies, including arm pitch angle, number of spiral arms, and presence of a galactic bar, are taken from the Galaxy~Zoo~2 (GZ2) catalog \citep{wil13}.
 
@@
 We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation.
-Galaxies with low signal-to-noise ratio $(S/N > 3)$ galaxies are removed.
+We retain galaxies classified as star-forming but with low signal-to-noise ratio $(S/N > 3)$.
 For both $M_\star$ and $SFR$, we use median values extracted from the PDF.
@@
 
+We have examined all the populations of galaxies described above (bars, arm pitch angle, arm multiplicity) and measured the differences when using specific star formation rate ($\textrm{sSFR}\equiv\textrm{SFR}/M_\star$) instead of SFR.
+There is no significant change in the results.
+
 %%%%%%%%%%%%
@@
 Our results show that the neither of the first two factors play dominant roles in controlling $\sigma_{SFR}$, at least as far as major dynamical drivers (such as strong bars or additional arms) are concerned.
-Thus while the overall bulge strength does affect the position of a galaxy on the SFMS \citep{mar09,che12,fan13,lan14,oma14}, the structure of the \emph{disk itself} does not.
+Thus while the overall bulge strength does affect the position of a galaxy on the SFMS \citep{mar09,che12,fan13,kav14,lan14,oma14}, the structure of the \emph{disk itself} does not.
 
@@
 The projected separation between galaxies in which this occurs, based on both the observed merger fraction and sSFR is $\sim0.1$~Mpc$/h$ \citep{ski09}.
+Our measurements are consistent with observations of galaxies at $z\simeq2$ \citep{kav13b}, which support a merger-driven increase of only a factor of $\sim2$ in sSFR.
 
@@
 The magnitude of this increase often depends on the details of the simulation, but can range from a factor of 10 to 100.
-In the low-redshift universe sampled by SDSS and Galaxy~Zoo, we find no evidence for an enhancement of such magnitude.
+Observations of mergers in Stripe~82 data, however, limit this increase to between a factor of 2 and 6 \citep{kav14}.
+In the low-redshift universe sampled by SDSS and Galaxy~Zoo, we also find no evidence for an enhancement more than an order of magnitude.
 This in turn suggests that the current generation of galaxy merger simulations misses critical feedback mechanisms that prevent runaway peaks in star formation rates during mergers.

### 2014-09-27 gz_mainsequence.py

@@ -33,49 +33,63 @@ def get_data():
 
     return data
 
-def get_sfr_sample(data):
+def get_sample(data,starforming=True):
 
     # Find starforming galaxies
 
-    sf = (data['bpt'] == 1) #| (data['bpt'] == 2)
-    redshift = data['REDSHIFT'] <= 0.1
-    absmag = data['PETROMAG_MR'] < -19.5
+    sf = (data['bpt'] == 1) | (data['bpt'] == 2)
+    redshift = (data['REDSHIFT'] <= 0.05) & (data['REDSHIFT'] >= 0.005)
+    absmag = data['PETROMAG_MR'] < -19.5        # could use 0.085 and -20.17, or 0.05 and -19.5
 
-    sfr_sample = data[sf & redshift]
+    if starforming:
+        sample = data[sf & redshift & absmag]
+    else:
+        sample = data[redshift & absmag]
 
-    return sfr_sample
+    return sample
 
-def get_mass_sfr(sfr_sample):
+def get_mass_sfr(sf_sample):
 
-    mass_sfr_good = (sfr_sample['MEDIAN_MASS'] > -99) & (sfr_sample['MEDIAN_SFR'] > -99)
+    mass_sfr_good = (sf_sample['MEDIAN_MASS'] > -99) & (sf_sample['MEDIAN_SFR'] > -99)
 
-    mass = sfr_sample[mass_sfr_good]['MEDIAN_MASS']
-    sfr = sfr_sample[mass_sfr_good]['MEDIAN_SFR']
-    sfr16_err = np.abs(sfr_sample[mass_sfr_good]['P16_SFR'] - sfr_sample[mass_sfr_good]['MEDIAN_SFR'])
-    sfr84_err = np.abs(sfr_sample[mass_sfr_good]['P84_SFR'] - sfr_sample[mass_sfr_good]['MEDIAN_SFR']) 
+    mass = sf_sample[mass_sfr_good]['MEDIAN_MASS']
+    sfr = sf_sample[mass_sfr_good]['MEDIAN_SFR']
+    sfr16_err = np.abs(sf_sample[mass_sfr_good]['P16_SFR'] - sf_sample[mass_sfr_good]['MEDIAN_SFR'])
+    sfr84_err = np.abs(sf_sample[mass_sfr_good]['P84_SFR'] - sf_sample[mass_sfr_good]['MEDIAN_SFR']) 
     sfr_err = (sfr16_err + sfr84_err) / 2.
 
[…]

### 2014-11-17 gz_mainsequence.py
Find largest volume-limited size in sample

@@ -7,6 +7,8 @@ from matplotlib import cm
 from matplotlib.colors import LogNorm
 from matplotlib.font_manager import FontProperties
 from astropy.io import fits
+from astropy import cosmology
+from astropy import units as u
 
 from scipy.stats import ks_2samp
 from scipy.linalg.basic import LinAlgError
@@ -24,6 +26,10 @@ an_tasks = ['t11_arms_number_'+r for r in ('a31_1','a32_2','a33_3','a34_4','a36_
 an_colors = ('red','orange','yellow','green','blue','purple')
 aw_colors = ('red','green','blue')
 
+z_lowerlim = 0.005
+z_upperlim = 0.05
+absmag_lim = -19.5
+
 def get_data():
 
     filename = '%s/mpajhu_gz2.fits' % fits_path
@@ -37,9 +43,9 @@ def get_sample(data,starforming=True):
 
     # Find starforming galaxies
 
-    sf = (data['bpt'] == 1) | (data['bpt'] == 2)
-    redshift = (data['REDSHIFT'] <= 0.05) & (data['REDSHIFT'] >= 0.005)
-    absmag = data['PETROMAG_MR'] < -19.5        # could use 0.085 and -20.17, or 0.05 and -19.5
+    sf = (data['bpt'] == 1) #| (data['bpt'] == 2)
+    redshift = (data['REDSHIFT'] <= z_upperlim) & (data['REDSHIFT'] >= z_lowerlim)
+    absmag = data['PETROMAG_MR'] < absmag_lim        # could use 0.085 and -20.17, or 0.05 and -19.5
 
     if starforming:
         sample = data[sf & redshift & absmag]
@@ -242,7 +248,7 @@ def plot_ms_arms_number(sf_sample,weighted=False,contour=False,plot_ssfr=False):
 
     return None
 
-def plot_ms_arms_winding(sf_sample,weighted=False,plot_ssfr=False):
+def plot_ms_arms_winding(sf_sample,weighted=False,contour=False,plot_ssfr=False):
 
     # Plot
 
@@ -310,9 +316,18 @@ def plot_ms_arms_winding(sf_sample,weighted=False,plot_ssfr=False):
 
         # Two sets of plots: one weights histogram by debiased vote fraction per galaxy; other shows discrete categories from GZ2 flags.
         if weighted:
[…]

### 2014-11-23 gz_mainsequence.py
Final sample: no volume limits, BPT=1

@@ -26,8 +26,8 @@ an_tasks = ['t11_arms_number_'+r for r in ('a31_1','a32_2','a33_3','a34_4','a36_
 an_colors = ('red','orange','yellow','green','blue','purple')
 aw_colors = ('red','green','blue')
 
-z_lowerlim = 0.005
-z_upperlim = 0.05
+z_lowerlim = 0.000      # any reason for a lower limit?
+z_upperlim = 0.085      # upper limit of reliable GZ2 classification
 absmag_lim = -19.5
 
 def get_data():
@@ -45,12 +45,14 @@ def get_sample(data,starforming=True):
 
     sf = (data['bpt'] == 1) #| (data['bpt'] == 2)
     redshift = (data['REDSHIFT'] <= z_upperlim) & (data['REDSHIFT'] >= z_lowerlim)
-    absmag = data['PETROMAG_MR'] < absmag_lim        # could use 0.085 and -20.17, or 0.05 and -19.5
+    #absmag = data['PETROMAG_MR'] < absmag_lim        # could use 0.085 and -20.17, or 0.05 and -19.5
 
     if starforming:
-        sample = data[sf & redshift & absmag]
+        #sample = data[sf & redshift & absmag]
+        sample = data[sf & redshift]
     else:
-        sample = data[redshift & absmag]
+        #sample = data[redshift & absmag]
+        sample = data[redshift]
 
     return sample
 
@@ -137,7 +139,7 @@ def plot_fits(label,data,axis,color,morph='t11_arms_number_a31_1',lw=2,ls='--',l
 
     return a,b
 
-def plot_ms_arms_number(sf_sample,weighted=False,contour=False,plot_ssfr=False):
+def plot_ms_arms_number(sf_sample,weighted=False,contour=False,plot_ssfr=False,verbose=False):
 
     # Plot
 
@@ -220,12 +222,12 @@ def plot_ms_arms_number(sf_sample,weighted=False,contour=False,plot_ssfr=False):
 
             cb_label = r'$w_\mathrm{\phi}$'
 
-            plot_fits(al,spirals,ax,c,morph=a,weight_by_err=False,weight_by_morph=True,plot_ssfr=plot_ssfr)
+            plot_fits(al,spirals,ax,c,morph=a,weight_by_err=False,weight_by_morph=True,plot_ssfr=plot_ssfr,verbose=verbose)
         else:
[…]

### 2014-11-23 paper/mainsequence_morph.tex
Minor update
Switched to MNRAS template; final rewrite by KWW

@@
-\documentclass{emulateapj}
+\documentclass[useAMS,usenatbib]{mn2e}
+% mn2e fix: put pageblock in middle of page regardless of actual papersize
+\usepackage[letterpaper,total={17.8cm,24.0cm},centering]{geometry}
+
 %\documentclass[manuscript]{aastex}
@@
 \usepackage{subfigure}
+\usepackage{deluxetable}
 \usepackage{verbatim}
 \usepackage{natbib}
-\usepackage{amsmath}
+\usepackage{amsmath,amssymb}
 \usepackage{color}
-\bibliographystyle{apj}
+\usepackage{hyperref}
+\bibliographystyle{mn2e}
 
-\shorttitle{STAR-FORMING MAIN SEQUENCE GALAXIES AND THEIR MORPHOLOGY}
-\shortauthors{WILLETT ET AL.}
-
-\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
+\newcommand{\mytilde}{\textasciitilde}
 \newcommand{\kevin}{{\color{red}\textbf{Kevin}}}
 
-\begin{document}
-
-\title{The dependence of spiral disk morphology on the star formation-stellar mass relation}
-
-\author{Kyle Willett\altaffilmark{1}, Kevin Schawinski\altaffilmark{2}, etc.}
-% People who want to be co-authors:
-% Ivy Wong
-% Karen Masters
-% Ramin Skibba
-% Bob Nichol
-% Tom Melvin
-% Edmond Cheung
-% Chris Lintott
-% Bill Keel
-% Sugata Kaviraj
-% Brooke Simmons
-
-\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA}
-\altaffiltext{2}{Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 16, CH-8093, Z\"urich, Switzerland}
+\title[Disk galaxy morphology and the star-forming main sequence]{The dependence of spiral disk morphology on the star formation-stellar mass relation}
+\author[Willett et al.]{
+  \parbox[t]{16cm}{
+  Kyle W. Willett$^{1}$\thanks{E-mail: willett@physics.umn.edu},
+  Kevin Schawinski$^{2}$,
+  Edmond Cheung$^{3,4}$,
+  Lucy Fortson$^{1}$,
+  Sugata Kaviraj$^{5,6}$,
+  William C. Keel$^{7}$,
+  Chris J. Lintott$^{6}$,
+  Karen L. Masters$^{8,9}$,
+  Thomas~Melvin$^{8}$,
+  Robert C. Nichol$^{8,9}$,
+  Brooke D. Simmons$^{6}$,
+  Ramin A. Skibba$^{10}$,
+  O. Ivy Wong$^{11}$
+  \\
+  }\\
+$^{1}$School of Physics and Astronomy, University of Minnesota, 116 Church St SE, Minneapolis, MN 55455, USA \\
+$^{2}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 16, CH-8093 Z\"urich, Switzerland \\
+$^{3}$Department of Astronomy and Astrophysics, 1156 High Street, University of California, Santa Cruz, CA 95064, USA\\
+$^{4}$Kavli IPMU (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
+$^{5}$Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Herts, AL10 9AB, UK \\
+$^{6}$Oxford Astrophysics, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK \\
+$^{7}$Department of Physics and Astronomy, University of Alabama, Box 870324, Tuscaloosa, AL 35487, USA \\
+$^{8}$Institute of Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Portsmouth PO1 3FX, UK \\
+$^{9}$SEPnet, South East Physics Network, UK \\
+$^{10}$Center for Astrophysics and Space Sciences, University of California San Diego, 9500 Gilman Dr, San Diego, CA 92093, USA \\
+$^{11}$International Centre for Radio Astronomy Research, University of Western Australia, 35 Stirling Hwy, Crawley, WA 6009, Australia \\
+}
 
@@
 %@arxiver{ms_bar_contour.pdf,ms_mergers_both.pdf}
+
+\begin{document}
+\date{Accepted XXXXXXX}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2014}
+\maketitle
+\label{firstpage}
 
@@
 \begin{abstract}
-We measure the mass-star formation relation in disk galaxies at $z<0.05$, using Galaxy Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
+We measure the mass-star formation relation in disk galaxies at $z<0.05$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
 We examine the number of spiral arms, their average pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
@@
 
-\keywords{galaxies:mergers}
+\begin{keywords}
+galaxies:mergers
+\end{keywords}
 
@@
 
-As star-forming galaxies exhibit a wide range of physical appearances in optical images, we can ask the natural question of whether the specifics of this physical appearance, and its underlying dynamical processes, have any effect on this homeostasis and therefore the galaxy's location relative to the SFMS.
+As star-forming galaxies exhibit a wide range of physical appearances in optical images, the natural question can be asked of whether the specifics of this physical appearance and its underlying dynamical processes have any effect on this homeostasis and therefore the galaxy's location relative to the SFMS.
 If the details of a galaxy's physical appearance are correlated with position relative to the main sequence, then the dynamical processes that give rise to them -- such as bar formation and spiral arm pitch angle -- are a fundamental aspect of the galaxy's regulatory mechanism.
@@
 \citet{pen10a,pen12} argue that galaxies grow in stellar mass during their life as star-forming galaxies on the main sequence before being quenched either by an external mechanism (environment or satellite quenching) or by an internal mechanism (mass quenching).
-This life on the main sequence is thus governed by the action of the regulator balancing gas in- and outflows \citet{lil13}, making it the central process in galaxy evolution.
+This life on the main sequence is thus governed by the action of the regulator balancing gas in- and outflows \citep{lil13}, making it the central process in galaxy evolution.
 
-In this paper, we use the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with the largest database of visual classifications of galaxy structure and morphology ever assembled from the Galaxy Zoo citizen science projects \citep{lin08,lin11,wil13} to test whether galaxy structure affects their star formation properties.
+In this paper, we use data from the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with Galaxy Zoo, the largest database of visual classifications of galaxy structure and morphology ever assembled \citep{lin08,lin11,wil13}, to test whether galaxy structure affects their star formation properties.
 We use the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
@@
 
-Data for all galaxies in this paper comes from optical observations in the SDSS~DR7.
+Photometric and spectroscopic data for all galaxies in this paper comes from optical observations in the SDSS~DR7.
 The morphological data is drawn from citizen science classifications in Galaxy~Zoo.
 Detailed classifications of disk morphologies, including arm pitch angle, number of spiral arms, and presence of a galactic bar, are taken from the Galaxy~Zoo~2 (GZ2) catalog \citep{wil13}.
-We use a volume-limited sample with $0.005<z<0.085$; the lower bound removes galaxies with large angular sizes for which fibre-derived quantities do not sample the full disk, while the upper limit is chosen as a compromise between sample size and the effective classification distance of the GZ2 morphologies.
+Merging pairs of galaxies are taken from the catalog of \citet{dar10a}, all of which lie in the redshift range $0.005<z<0.1$.
+Post-merger spheroidal galaxies without an obvious, separated companion are specifically excluded from our sample.
 
-Merging pairs of galaxies are taken from the catalog of \citet{dar10a}, all of which lie in the redshift range $0.005<z<0.1$.
-Post-merger spheroidal galaxies without an obvious, separated companion are specifically excluded from the sample.
-
-Spiral galaxies are selected according to the following thresholds in the spectroscopic GZ2 sample, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
-We identify sub-classes of spiral structure using the morphology flags as given in the GZ2 catalog; these are designed to be conservative cuts, including only robust examples of each morphological class.
+Spiral galaxies are identified according to the following thresholds in the spectroscopic GZ2 sample, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
+We identify sub-classes of spiral structure by weighting each galaxy according to the fraction of votes received in each morphological category.
 
@@
 We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation.
-We retain galaxies classified as star-forming but with low signal-to-noise ratio $(S/N > 3)$.
+We exclude galaxies classified as star-forming but with low signal-to-noise ratio $(S/N > 3)$.
 For both $M_\star$ and $SFR$, we use median values extracted from the PDF.
@@
 %How many galaxies are there in the total sample? What is the mass, color, and redshift range?
-The total sample analyzed contains 52,685 star-forming galaxies.
-These are selected from the GZ2 spectroscopic sample with $z<0.1$, $M_r<-19.5$, and classified as actively star-forming ($BPT=1$) from the MPA-JHU emission line measurements.
-The average color for the star-forming galaxies is relatively blue, with $(u-r)=1.7\pm0.6$.
+The total sample analyzed in this paper consists of 49,097 star-forming galaxies.
+These are selected from the GZ2 spectroscopic sample with $z<0.085$ (the limit of reliable debiased morphological classification for GZ2) for galaxies classified as actively star-forming ($BPT=1$) from the MPA-JHU emission line measurements.
+The average color for the star-forming galaxies is relatively blue, with $(u-r)=1.6\pm0.4$.
 
-\begin{table} \caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies.}
+\begin{table} 
  \begin{tabular}{@{}lrcrcl}
@@
 \hline						
-SF galaxies  & 52685   & $0.73$  & $-7.19$   & $5.27\times10^{-6}$  & $5.18\times10^{-4}$  \\
+SF galaxies  & 49097  & $0.71$  & $-7.04$   & $5.86\times10^{-6}$  & $5.70\times10^{-4}$  \\
 \hline
-1 arm        & 39      & $0.66$  & $-6.31$  &  $5.11\times10^{-3}$  & $5.14\times10^{-1}$  \\
-2 arms       & 2914    & $0.79$  & $-7.74$  &  $1.11\times10^{-4}$  & $1.14\times10^{-2}$  \\
-3 arms       & 89      & $0.57$  & $-5.47$  &  $4.17\times10^{-3}$  & $4.49\times10^{-1}$  \\
-4 arms       & 9       & $0.35$  & $-3.29$  &  $9.18\times10^{-2}$  & $9.58\times10^{0 }$  \\
-5+ arms      & 9       & $0.64$  & $-6.88$  &  $7.20\times10^{-2}$  & $6.91\times10^{0 }$  \\
-can't tell   & 40      & $0.69$  & $-7.10$  &  $1.06\times10^{-2}$  & $1.04\times10^{0 }$  \\
+1 arm        & 289    & $0.61$  & $-5.81$  &  $6.57\times10^{-3}$  & $6.49\times10^{-1}$  \\
+2 arms       & 5641   & $0.78$  & $-7.65$  &  $1.27\times10^{-4}$  & $1.30\times10^{-2}$  \\
+3 arms       & 997    & $0.54$  & $-5.16$  &  $4.39\times10^{-3}$  & $4.70\times10^{-1}$  \\
+4 arms       & 285    & $0.35$  & $-3.27$  &  $1.15\times10^{-1}$  & $1.19\times10^{ 1}$  \\
+5+ arms      & 289    & $0.64$  & $-6.88$  &  $7.20\times10^{-2}$  & $6.91\times10^{0 }$  \\
+can't tell   & 2017   & $0.69$  & $-7.10$  &  $1.06\times10^{-2}$  & $1.04\times10^{0 }$  \\
 \hline
-tight arms   &  308    & $0.73$  & $-7.26$  &  $1.68\times10^{-3}$  & $1.75\times10^{-1}$  \\
-medium arms  &  44     & $0.80$  & $-7.83$  &  $5.23\times10^{-3}$  & $5.37\times10^{-1}$  \\
-loose arms   &  470    & $0.74$  & $-7.14$  &  $5.16\times10^{-3}$  & $5.18\times10^{-2}$  \\
+tight arms   &  3255  & $0.70$  & $-6.99$  &  $1.79\times10^{-3}$  & $1.86\times10^{-1}$  \\
+medium arms  &  4578  & $0.77$  & $-7.62$  &  $6.81\times10^{-3}$  & $6.87\times10^{-1}$  \\
+loose arms   &  1672  & $0.73$  & $-7.08$  &  $5.81\times10^{-3}$  & $5.76\times10^{-2}$  \\
 \hline
-barred       &  4473   & $0.76$  & $-7.54$  &  $7.60\times10^{-5}$  & $7.57\times10^{-3}$  \\
-unbarred     &  11593  & $0.70$  & $-6.92$  &  $2.65\times10^{-5}$  & $2.66\times10^{-3}$  \\
+barred       &  3199  & $0.75$  & $-7.38$  &  $8.53\times10^{-5}$  & $8.42\times10^{-3}$  \\
+unbarred     &  11846 & $0.69$  & $-6.78$  &  $2.91\times10^{-5}$  & $2.89\times10^{-3}$  \\
 \hline
-merger       &  2978   & --      & $-7.91$  &  --                   & $4.40\times10^{-4}$  \\
+merger       &  2978  & --      & $-6.73$  &  --                   & --                   \\
 \hline
  \end{tabular}
-\tablecomments{Parameters $\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit}.\label{tbl-fits}}
+\caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies.
+$N$ is the number of galaxies with plurality classifications for spiral arm multiplicity and pitch angles, and at a cutoff of $p_{bar}=0.4$ for barred galaxies.
+$\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit}.\label{tbl-fits}}
 \end{table}
@@
 \noindent where $\alpha$ and $\beta$ represent the slope and offset, respectively.
-Values of the fits for each subample are given in Table~\ref{tbl-fits}; we also provide the formal uncertainties $\sigma_\alpha$ and $\sigma_\beta$ in each parameter from the covariance matrix.
+Uncertainties $\sigma_\alpha$ and $\sigma_\beta$ are taken from the covariance matrix for each least-squares fit (Table~\ref{tbl-fits}).
+
+% Volume-limiting on the sample
+
+The sample of galaxies examined here is not explicitly constructed to be volume-limited.
+The main reason for this is that we are comparing effects between sub-samples of galaxies using the same selection functions.
+One possibility is that volume-limiting would deal with galaxies in which the dust content is high enough to obscure all emission lines, even in the presence of significant star formation.
+Such galaxies, typically [U]LIRGs, have very low space-densities at $z<0.1$, and typically lack the regular disk structure needed to categorize it.
+
+In order to address volume-limiting, we have performed a detailed analysis using a series of volume-limits with upper redshift limits out to $z<0.085$ and $M_r < 20.17$.
+All results discussed in this paper agree with data in the volume-limited group.
+However, the significance of fits is smaller in the volume-limited data due to the restricted range in stellar mass ($M_\star\gtrsim10^9$), which affects the accuracy of a linear fit to the SFMS.
+For these reasons, we present results from the full sample of star-forming disks, which increases the sensitivity of our method to potentially small shifts between the morphologically-selected sub-samples.
 
@@
 Both spiral arms and galactic bars can have significant effects on the local properties of a galaxy.
-Dynamical effects compress gas and trigger recent star formation within spiral arms, while longer galactic bars have redder colors and less star formation than the rest of the disk \citep{hoy11}.
+Dynamical effects concentrate gas in spiral arms and redistribute star formation \citep{elm86,foy10}, while longer galactic bars have redder colors and less star formation than the rest of the disk \citep{hoy11}.
 We examine whether these kpc-scale effects can be seen long-term in the galaxy's SFR-mass relationship.
 
-For a control sample, we plot in Figures~\ref{fig-number}-\ref{fig-mergers} the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local SDSS galaxies.
-As demonstrated in previous papers, there is a fairly tight correlation between $M_\star$ and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
+As a control sample, we also analyze the fits to the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local SDSS galaxies (Figures~\ref{fig-number}-\ref{fig-bar},\ref{fig-mergers}).
+As previously demonstrated with SDSS data \citep[e.g.,][]{bri04}, there is a tight correlation between $M_\star$ and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
 The relationship extends over at least 4~orders of magnitude in both $M_\star$ and SFR.
+Fits to the SFMS for all subsamples in this paper are listed in Table~\ref{tbl-fits}.
 
@@
 Coloured contours in each panel show spiral galaxies weighted by the GZ2 likelihoods of hosting 1, 2, 3, 4, more than four, or ``uncertain'' numbers of spiral arms, respectively.
-Dotted lines show the weighted least-squares linear fit to each population as split by arm multiplicity; the solid line is the fit to all of the star-forming galaxies.
+Dotted lines show the weighted least-squares linear fit to each population as split by arm multiplicity; the solid line is the fit to all star-forming galaxies.
 \label{fig-number}}
@@
 
-Figure~\ref{fig-number} overplots SFR as a function of $M_\star$ for disk galaxies separated by their arm multiplicity.
+Figure~\ref{fig-number} shows the SFR as a function of $M_\star$ for disk galaxies separated by their arm multiplicity.
 The GZ2 data separates disk galaxies with visible spiral arms into categories of 1, 2, 3, 4, or more than four spiral arms; there is also an additional option if the number of spiral arms cannot be accurately determined.
 For this analysis, galaxies in each mass/SFR bin is weighted by the vote fraction for the morphology being tested.
-Two-armed spirals are the most common multiplicity in the GZ2 sample.
 
-The fit to the star-forming main sequence for the six sub-samples of spiral galaxies tightly follows that of that for the total disk population.
+The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of that for the total disk population.
 Both the slopes and offsets of each linear fit are completely consistent within the formal fitting errors (Table~\ref{tbl-fits}).
-There are too few galaxies with reliable spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all multiplicities at $10^8<M_\star/M_\sun<10^{11}$.
+There are too few galaxies with reliable spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all multiplicities at $10^8<M_\star/M_\odot<10^{11}$.
 
-The one-armed spirals present an interesting case, with the fit to the weighted population lying slightly \emph{above} that of all star-forming spirals.
+One-armed spiral galaxies present an interesting case, with the fit to the weighted population lying slightly \emph{above} that of all star-forming spirals.
 This is consistent with the work of \citet{cas13}, who showed that one-armed spirals in GZ2 are robust indicators of close interactions at projected distances of $r_p < 50~h^{-1}$~kpc.
-The underlying reason is that many ``one-armed spirals'' are in fact caused by bridges or tidal tails from interactions with a nearby companion; we discuss the likely role of merging/interacting galaxies in Figure~\ref{fig-mergers}.
+The underlying reason is that many ``one-armed spirals'' are in fact caused by bridges or tidal tails from interactions with a nearby companion instead of secular processes.
+We discuss the likely role of merging/interacting galaxies in Section~\ref{sec-discussion} (see Figure~\ref{fig-mergers}).
 
-The two-armed spirals and those with uncertain multiplicities are the only morphologies that extend slightly below the SFMS.
+Two-armed spiral galaxies and those with uncertain multiplicities are the only morphologies that extend slightly below the SFMS.
 One possibility is that this is a consequence of galaxies that have already begun the process of quenching.
@@
 We have repeated the analysis above for the sub-sample of disk galaxies for which the spiral multiplicity is determined with high confidence ($p_\textrm{arms~number} > 0.8$) by GZ2, thus eliminating ``intermediate'' galaxies for which the morphology is uncertain.
-These galaxies ($N=14,148$) is dominated by two-armed spirals, which are the only multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\sun$ are detected.
+These galaxies ($N=14,148$) are dominated by two-armed spirals, which are the only multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\odot$ are detected.
 Our results for the SFMS are qualitatively the same as when using the weighting scheme, although we note that there are too few examples ($N<10$) of either three- or four-armed spirals for a reliable fit.
@@
 The pitch angle of the spiral arms also has no significant change on the star-forming main sequence relation (Figure~\ref{fig-winding}).
-We separate galaxies by their relative pitch angles (defined as ``tight'', ``medium'', and ``loose''); the pitch angle is typically used as one of the primary drivers for separating galaxies along the Hubble tuning fork.
+We separate galaxies by their relative pitch angles (defined as ``tight'', ``medium'', and ``loose''); the pitch angle is typically used as one of the primary parameters for separating galaxies along the Hubble tuning fork.
 \citet{wil13} show, however, that pitch angle only weakly correlates with Hubble type from expert visual classifications, and that the bulge-to-disk ratio is a more important driver.
-All three categories correlate tightly with spiral galaxies in general; we note that the small deviation above the main sequence for loosely-wound galaxies is also consistent with \citet{cas13}, who show that this morphology also correlates with close pairs and interactions.
+There is no significant shift with respect to the SFMS as a function of pitch angle for spiral galaxies.
+We note that the small increase above the main sequence for loosely-wound galaxies is also consistent with \citet{cas13}, who show that this morphology also correlates with close pairs and interactions.
 
@@
 
+\begin{figure*}
+\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding_weighted.pdf}
+\caption{Same as Figure~\ref{fig-winding}, but with colormaps showing all spiral galaxies weighted by the GZ2 vote fractions for ``tight'', ``medium'', and ``loose'' winding spiral arms. 
+\label{fig-winding_weighted}}
+\end{figure*}
+
 It should also be noted that the galaxies in GZ2 flagged as a function of pitch angle are not representative of the true vote distribution.
@@
 In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the medium option at the 80\% level which sets the flag.
-We have extended this analysis by plotting the same star-forming main sequence diagram as a function of $p_\textrm{arms~winding}$, which more accurately tracks the pitch angle distribution.
-In this case, it also closely follows the main star-forming main sequence (Figure~\ref{fig-winding_weighted}).
+An alternative method is to analyze the morphology of spiral galaxies by directly weighting them as a function of the pitch angle categories (Figure~\ref{fig-winding_weighted}), which has the advantage of including all spiral galaxies.
+This shows an even tighter agreement between the samples separated by pitch angle and that of the full star-forming sample.
 
@@
 Finally, we examine the effect of a large-scale galactic bar on the star-forming main sequence.
-This sample is significantly larger than those including spiral arm morphology, since the classification is at a higher level in the GZ2 tree and has only two choices; this results in a higher percentage of consensus classifications that set the flag.
-Figure~\ref{fig-bar} shows the star-forming main sequence for both barred and unbarred galaxies.
-Although the fraction of barred galaxies potentially varies as a function of stellar mass \citep{mas11c,che13}, both the linear fits and ranges of the sub-populations are consistent with all star-forming galaxies.
+This sample has significantly more galaxies than those including spiral arm morphology, since the classification is at a higher level in the GZ2 tree and has only two choices.
+This results in a higher percentage of consensus classifications in the GZ2 catalog.
+Figure~\ref{fig-bar} shows the SFMS for both barred and unbarred galaxies.
+Although the fraction of barred galaxies varies as a function of stellar mass \citep{she08a,cam10,mas11c,che13}, both the linear fits and ranges of the sub-populations are consistent with all star-forming galaxies.
 In other words, the presence of a bar does not affect the galaxy's position on the star-forming main sequence.
@@
 \includegraphics[angle=0,width=3.5in]{figures/sigma_mstar.pdf}
-\caption{Width of the star-forming main sequence ($\sigma$) as a function of stellar mass, as measured by the sample standard deviation.
+\caption{Width of the star-forming main sequence ($\sigma_{SFR}$) as a function of stellar mass, as measured by the sample standard deviation.
 Black points represent the entire star-forming population.
-The various disk subsamples are overplotted as lines; colours are the same as the respective plots in Figures~\ref{fig-number}-\ref{fig-bar} and \ref{fig-mergers}.
-Morphological categories or mass ranges with fewer than 10 galaxies/bin are not plotted; this includes all mass ranges for 3-, 4-, and more than 4-armed spirals.
+Disk subsamples are overplotted as solid lines; colours are the same as the respective plots in Figures~\ref{fig-number}, \ref{fig-winding}, \ref{fig-bar} and \ref{fig-mergers}.
+Morphological categories or mass ranges with fewer than 10 galaxies/bin are not plotted; this includes all galaxies with 3, 4, and 5+ spiral arms.
 \label{fig-sigma}}
@@
 \citet{abr14} found that by normalizing galaxies by the stellar mass of the disk alone, the slope of the SFMS is consistent with only a linear trend (removing any dependence on mass).
-Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, and/or environment (among other factors).
+Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, and/or environment, among other factors.
 Our results show that the neither of the first two factors play dominant roles in controlling $\sigma_{SFR}$, at least as far as major dynamical drivers (such as strong bars or additional arms) are concerned.
@@
 The lack of any difference in SFR as a function of mass for barred vs.
-unbarred galaxies is in general agreement with \citet{ell11}, who find an increase of $\Delta~\textrm{SFR}\sim0.15$~dex, but only for galaxies with $M_\star>10^{10.7}~M_\odot$.
-This is at the very upper end of the mass range probed in Figure~\ref{fig-bar}.
-If the increase in star formation is limited to the central kpc of the disk (as they demonstrate using fibre SFR measurements), an increase in possible bar-driven SFR increase is seen down to $M_\star=10^{10}~M_\odot$.
+unbarred galaxies is in general agreement with \citet{ell11}, who find an increase of $\Delta\textrm{SFR}\sim0.15$~dex, but only for galaxies with $M_\star>10^{10.7}~M_\odot$.
+This is at the very upper end of the mass range probed in our analysis of barred vs.
+unbarred galaxies (Figure~\ref{fig-bar}).
+If the increase in star formation is limited to the central kiloparsec of the disk (as demonstrated using fibre SFR measurements), an increase in possible bar-driven SFR increase is seen down to $M_\star=10^{10}~M_\odot$.
 
@@
 In the local Universe, these include optically-identified ``green pea'' galaxies, which have unusually high sSFR and can lie more than 1~dex above the SFMS \citep{car09}.
-While few known green pea galaxies have detailed imaging available, their most common morphology is in a clumpy arrangement with knots of bright star formation.
+While few green pea galaxies have detailed imaging available, their most common morphology is in a clumpy arrangement with knots of bright star formation.
 There is thus little evidence for a dynamically-settled disk (in any arrangment) for galaxies in the local Universe lying significantly above the SFMS.
@@
 As a comparison to the kpc-scale structures discussed above, we analyze the impact of the most significant forcing event to a galaxy system known -- a major galaxy merger (Figure~\ref{fig-mergers}).
-In these systems (which are in various stages of coalescence) the star formation rates are increased by only an average of 0.29~dex, corresponding to less than a factor of two overall.
+In these systems, which are in various stages of coalescence, star formation rates are increased by only an average of 0.29~dex (less than a factor of two).
 \citet{dar10} showed that in the local ($z<0.1$) Universe, galaxies with intense bursts of star formation are limited to only the spiral (disc) galaxies.
@@
 The location of mergers on the present-day SFMS shows just how stable the regulatory system in galaxies really is.
-Almost all simulations of galaxy mergers predict a steep increase in the star formation rate during both first passage and final coalescence \citep[eg,][]{hop08}.
-The magnitude of this increase often depends on the details of the simulation, but can range from a factor of 10 to 100.
-Observations of mergers in Stripe~82 data, however, limit this increase to between a factor of 2 and 6 \citep{kav14}.
-In the low-redshift universe sampled by SDSS and Galaxy~Zoo, we also find no evidence for an enhancement more than an order of magnitude.
+Almost all simulations of galaxy mergers predict a steep increase in the star formation rate during both first passage and final coalescence \citep[e.g.,][]{hop08}.
+The magnitude of this increase often depends on the details of the simulation, but can range from factors of 10 to 100.
+Observations of mergers in Stripe~82 data, however, limit this increase to between factors of 2 and 6 \citep{kav14}.
+In the low-redshift universe sampled by SDSS and Galaxy~Zoo, we find no evidence for an enhancement more than an order of magnitude.
 This in turn suggests that the current generation of galaxy merger simulations misses critical feedback mechanisms that prevent runaway peaks in star formation rates during mergers.
@@
 
-We analyze for the first time the detailed structure of disks in star-forming galaxies as related to their position on the $M_\star$-SFR relation, using morphological classifications from the Galaxy~Zoo~2 project.
+We analyze for the first time the detailed structure of disks in large samples of star-forming galaxies as related to their position on the $M_\star$-SFR relation.
+This analysis is made possible by using morphological classifications from the Galaxy~Zoo~2 project.
 We find that neither the slope nor the dispersion of the star-forming galaxies are affected when splitting the sample into different categories of disks, including barred/unbarred galaxies, the pitch angle of spiral arms, or the number of spiral arms.
@@
 
-\acknowledgments
+\section*{Acknowledgments}
 
@@
 Their efforts are individually acknowledged at \url{http://authors.galaxyzoo.org}.
-Please contact the authors to request access to research materials discussed in this paper.
 
@@
 This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05} and Astropy, a community-developed core Python package for astronomy \citep{ast13}.
-%The development of Galaxy Zoo 2 was supported by The Leverhulme Trust.
+The development of Galaxy~Zoo~2 was supported by The Leverhulme Trust.
 KWW and LFF would like to acknowledge support from the US National Science Foundation under grant DRL-0941610.
-CJL acknowledges support from the Science and Technology Facilities Council (STFC) Science in Society program.
-KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
-TM acknowledges funding from the STFC ST/J500665/1.
-RCN was partially supported by STFC grant ST/K00090X/1.
-BDS acknowledges support from Worcester College, Oxford, and from the Oxford Martin School program on computational cosmology.
-
 KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.
@@
 
-\appendix
-\begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding_weighted.pdf}
-\caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-winding}.
-From left to right: colormaps show spiral galaxies weighted by the GZ2 vote fractions for ``tight'', ``medium'', and ``loose'' winding spiral arms.
-Dotted lines show the weighted least-squares linear fit as split by pitch angle; the solid line is the fit to all star-forming galaxies.
-\label{fig-winding_weighted}}
-\end{figure*}
-
 \end{document}

### 2014-11-26 paper/mainsequence_morph.tex
Brooke's comments on PDF added; switched author order

@@
 
-\title[Disk galaxy morphology and the star-forming main sequence]{The dependence of spiral disk morphology on the star formation-stellar mass relation}
+\title[Disk galaxy morphology and the star-forming main sequence]{The dependence of the star formation-stellar mass relation on spiral disk morphology}
 \author[Willett et al.]{
@@
   Kevin Schawinski$^{2}$,
-  Edmond Cheung$^{3,4}$,
+  Brooke D. Simmons$^{3}$,
+  Karen L. Masters$^{4,5}$,
+  Sugata Kaviraj$^{3,6}$,
+  Ramin A. Skibba$^{7}$,
+  Thomas Melvin$^{4}$,
+  O. Ivy Wong$^{8}$,
+  Robert C. Nichol$^{4,5}$,
+  Edmond Cheung$^{9,10}$,
+  Chris J. Lintott$^{3}$,
   Lucy Fortson$^{1}$,
-  Sugata Kaviraj$^{5,6}$,
-  William C. Keel$^{7}$,
-  Chris J. Lintott$^{6}$,
-  Karen L. Masters$^{8,9}$,
-  Thomas~Melvin$^{8}$,
-  Robert C. Nichol$^{8,9}$,
-  Brooke D. Simmons$^{6}$,
-  Ramin A. Skibba$^{10}$,
-  O. Ivy Wong$^{11}$
+  William C. Keel$^{11}$
   \\
@@
 $^{2}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 16, CH-8093 Z\"urich, Switzerland \\
-$^{3}$Department of Astronomy and Astrophysics, 1156 High Street, University of California, Santa Cruz, CA 95064, USA\\
-$^{4}$Kavli IPMU (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^{5}$Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Herts, AL10 9AB, UK \\
-$^{6}$Oxford Astrophysics, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK \\
-$^{7}$Department of Physics and Astronomy, University of Alabama, Box 870324, Tuscaloosa, AL 35487, USA \\
-$^{8}$Institute of Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Portsmouth PO1 3FX, UK \\
-$^{9}$SEPnet, South East Physics Network, UK \\
-$^{10}$Center for Astrophysics and Space Sciences, University of California San Diego, 9500 Gilman Dr, San Diego, CA 92093, USA \\
-$^{11}$International Centre for Radio Astronomy Research, University of Western Australia, 35 Stirling Hwy, Crawley, WA 6009, Australia \\
+$^{3}$Oxford Astrophysics, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK \\
+$^{4}$Institute of Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Portsmouth PO1 3FX, UK \\
+$^{5}$SEPnet, South East Physics Network, UK \\
+$^{6}$Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Herts, AL10 9AB, UK \\
+$^{7}$Center for Astrophysics and Space Sciences, University of California San Diego, 9500 Gilman Dr, San Diego, CA 92093, USA \\
+$^{8}$International Centre for Radio Astronomy Research, University of Western Australia, 35 Stirling Hwy, Crawley, WA 6009, Australia \\
+$^{9}$Department of Astronomy and Astrophysics, 1156 High Street, University of California, Santa Cruz, CA 95064, USA\\
+$^{10}$Kavli IPMU (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
+$^{11}$Department of Physics and Astronomy, University of Alabama, Box 870324, Tuscaloosa, AL 35487, USA \\
 }
@@
 We examine the number of spiral arms, their average pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
-We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only boost the SFR above the main relation by $\sim0.3$~dex; this is a significant reduction over the increase seen in merging systems at $z>1$.
+We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only boost the SFR above the main relation by $\sim0.3$~dex; this is significantly smaller than the increase seen in merging systems at $z>1$.
 Of the galaxies lying significantly above the $M_\star$-SFR relation in the local Universe, more than $50\%$ are mergers.
@@
 \begin{keywords}
-galaxies:mergers
+galaxies: spiral, galaxies: star formation, galaxies:mergers
 \end{keywords}
@@
 Observations at a range of redshifts have established that the star formation rate (SFR) of a galaxy is strongly correlated to its stellar mass ($M_\star$).
-This ``star-forming main sequence'' (SFMS) is nearly linear and at least at low redshift, has remarkably small scatter \citep{bri04}.
-Recent observations of star-forming galaxies at high redshifts show that this main sequence remains out to high redshift, but with its normalisation shifting up so that galaxies of the same $M_\star$ have a higher SFR at high redshift \citep{noe07,dad07}.
+This ``star-forming main sequence'' (SFMS) is nearly linear and has remarkably small scatter at low redshifts \citep{bri04}.
+Recent observations of star-forming galaxies at high redshifts show that this main sequence remains out to high redshift, but the normalisation shifts upward so that galaxies of the same $M_\star$ have a higher SFR at high redshift \citep{noe07,dad07}.
 The main sequence has been interpreted by \citet{bou10} and \citet{lil13} as the result of the balancing of inflows of cosmological gas and outflows due the feedback.
@@
 
-As star-forming galaxies exhibit a wide range of physical appearances in optical images, the natural question can be asked of whether the specifics of this physical appearance and its underlying dynamical processes have any effect on this homeostasis and therefore the galaxy's location relative to the SFMS.
+As a star-forming galaxies may exhibit a wide range of physical appearances in optical images, the natural question can be asked of whether the specifics of this physical appearance and its underlying dynamical processes have any effect on this homeostasis and therefore the galaxy's location relative to the SFMS.
 If the details of a galaxy's physical appearance are correlated with position relative to the main sequence, then the dynamical processes that give rise to them -- such as bar formation and spiral arm pitch angle -- are a fundamental aspect of the galaxy's regulatory mechanism.
@@
 \citet{pen10a,pen12} argue that galaxies grow in stellar mass during their life as star-forming galaxies on the main sequence before being quenched either by an external mechanism (environment or satellite quenching) or by an internal mechanism (mass quenching).
-This life on the main sequence is thus governed by the action of the regulator balancing gas in- and outflows \citep{lil13}, making it the central process in galaxy evolution.
+This life on the main sequence is thus governed by the action of the regulator to balance gas in- and outflows \citep{lil13}, making it the central process in galaxy evolution.
 
-In this paper, we use data from the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with Galaxy Zoo, the largest database of visual classifications of galaxy structure and morphology ever assembled \citep{lin08,lin11,wil13}, to test whether galaxy structure affects their star formation properties.
+In this paper, we use data from the Sloan Digital Sky Survey \citep[SDSS;][]{yor00,str02,aba09} in combination with Galaxy Zoo, the largest database of visual classifications of galaxy structure and morphology ever assembled \citep{lin08,lin11,wil13}, to test whether galaxy structure affects their star formation properties.
 We use the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
@@
 Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04,sal07}.
-We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation.
+We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep*{bal81} below the \citet{kau03} demarcation.
 We exclude galaxies classified as star-forming but with low signal-to-noise ratio $(S/N > 3)$.
@@
 Both spiral arms and galactic bars can have significant effects on the local properties of a galaxy.
-Dynamical effects concentrate gas in spiral arms and redistribute star formation \citep{elm86,foy10}, while longer galactic bars have redder colors and less star formation than the rest of the disk \citep{hoy11}.
+Dynamical effects concentrate gas in spiral arms and redistribute star formation \citep{elm86,foy10}, while longer galactic bars have redder colors and less star formation than the rest of the disk \citep{hoy11,mas12a}.
 We examine whether these kpc-scale effects can be seen long-term in the galaxy's SFR-mass relationship.
@@
 
-The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of that for the total disk population.
-Both the slopes and offsets of each linear fit are completely consistent within the formal fitting errors (Table~\ref{tbl-fits}).
+The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of the total disk population.
+Both the slopes and offsets of each linear fit are consistent within the formal fitting errors (Table~\ref{tbl-fits}).
 There are too few galaxies with reliable spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all multiplicities at $10^8<M_\star/M_\odot<10^{11}$.
@@
 Dotted lines show the weighted least-squares linear fit as split by pitch angle; the solid line is the fit to all star-forming galaxies.
+The positive offset in SFR for loosely-wound spiral arms is interpreted as contamination by merging pairs of galaxies (Section~\ref{sec-discussion}).
 \label{fig-winding}}
@@
 We thus also compared the sample standard deviation ($\sigma_{SFR}$) as a function of mass of the star-forming galaxy population to its various subsamples.
-The value of $\sigma_{SFR}$ monotonically decreases with mass over the range $6.0<\log(M/M_\odot)<11.5$.
+The value of $\sigma_{SFR}$ monotonically decreases with increasing mass over the range $6.0<\log(M/M_\odot)<11.5$.
 For all populations examined in this paper, though, the widths of their distributions are consistent with the broader population (Figure~\ref{fig-sigma}).
@@
 \citet{abr14} found that by normalizing galaxies by the stellar mass of the disk alone, the slope of the SFMS is consistent with only a linear trend (removing any dependence on mass).
-Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, and/or environment, among other factors.
+Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the intrinsic dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, and/or environment, among other factors.
 Our results show that the neither of the first two factors play dominant roles in controlling $\sigma_{SFR}$, at least as far as major dynamical drivers (such as strong bars or additional arms) are concerned.
-Thus while the overall bulge strength does affect the position of a galaxy on the SFMS \citep{mar09,che12,fan13,kav14,lan14,oma14}, the structure of the \emph{disk itself} does not.
+Thus while the overall bulge strength does affect the position of a galaxy on the SFMS \citep{mar09,che12a,fan13,kav14,lan14,oma14}, the structure of the \emph{disk itself} does not.
 
@@
 This is preserved even for the strongest forcing events, including major mergers; the physics governing the SFMS are primarily driven by the overall mass of the system.
-This means that simulations of galaxy evolution must be able to meet the challenge of simultaneously reproducing the wide range of disk morphologies observed along the Hubble sequence (and in various merger stages) while simultaneously managing feedback so that \emph{all} disk types maintain the same tight relationship to the SFMS.
+This means that simulations of galaxy evolution must be able to meet the challenge of reproducing the wide range of disk morphologies observed along the Hubble sequence (and in various merger stages) while simultaneously managing feedback so that \emph{all} disk types maintain the same tight relationship to the SFMS.
 

### 2014-12-03 paper/mainsequence_morph.tex
Last set of edits from KS, KLM, OIW, RS

@@
 
-\title[Disk galaxy morphology and the star-forming main sequence]{The dependence of the star formation-stellar mass relation on spiral disk morphology}
+\title[Disk galaxy morphology and the star-forming main sequence]{Galaxy Zoo: the dependence of the star formation-stellar mass relation on spiral disk morphology}
 \author[Willett et al.]{
@@
   Karen L. Masters$^{4,5}$,
-  Sugata Kaviraj$^{3,6}$,
-  Ramin A. Skibba$^{7}$,
+  Ramin A. Skibba$^{6}$,
+  Sugata Kaviraj$^{3,7}$,
   Thomas Melvin$^{4}$,
@@
   Chris J. Lintott$^{3}$,
-  Lucy Fortson$^{1}$,
-  William C. Keel$^{11}$
+  Lucy Fortson$^{1}$
   \\
@@
 $^{5}$SEPnet, South East Physics Network, UK \\
-$^{6}$Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Herts, AL10 9AB, UK \\
-$^{7}$Center for Astrophysics and Space Sciences, University of California San Diego, 9500 Gilman Dr, San Diego, CA 92093, USA \\
+$^{6}$Center for Astrophysics and Space Sciences, University of California San Diego, 9500 Gilman Dr, San Diego, CA 92093, USA \\
+$^{7}$Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Herts, AL10 9AB, UK \\
 $^{8}$International Centre for Radio Astronomy Research, University of Western Australia, 35 Stirling Hwy, Crawley, WA 6009, Australia \\
@@
 $^{10}$Kavli IPMU (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^{11}$Department of Physics and Astronomy, University of Alabama, Box 870324, Tuscaloosa, AL 35487, USA \\
+%$^{11}$Department of Physics and Astronomy, University of Alabama, Box 870324, Tuscaloosa, AL 35487, USA \\
 }
@@
 \begin{abstract}
-We measure the mass-star formation relation in disk galaxies at $z<0.05$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
+We measure the mass-star formation relation in star-forming disk galaxies at $z<0.05$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
 We examine the number of spiral arms, their average pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
@@
 Galaxies self-regulate to remain in a state of homeostasis as they convert baryons from gas to stars.
+This relation is found in all models where the star formation history of star-forming galaxies is relatively flat over cosmic time, and is insensitive to the details of the feedback mechanism \citep{hop14}.
 
@@
 
-The fact that star-forming galaxies live on the SFMS is one of the key observations that has been driving the development of new descriptions of how galaxies evolve.
-\citet{pen10a,pen12} argue that galaxies grow in stellar mass during their life as star-forming galaxies on the main sequence before being quenched either by an external mechanism (environment or satellite quenching) or by an internal mechanism (mass quenching).
-This life on the main sequence is thus governed by the action of the regulator to balance gas in- and outflows \citep{lil13}, making it the central process in galaxy evolution.
+The fact that star-forming galaxies live on the SFMS is one of the key observations that has been driving the development of new descriptions of how galaxies evolve \citep[eg, ][]{sch07b}.
+\citet{pen10a,pen12} argue that galaxies grow in stellar mass during their life as star-forming galaxies on the main sequence before having their star formation quenched either by an external mechanism (`environment quenching') or by an internal mechanism (`mass quenching').
+However, \citet{del12} point out that, because of a `history bias,' galaxies of identical stellar mass may have different environmental histories that are difficult to disentangle, thus making the mass versus environment debate inherently ill-posed \citep[see also ][]{van08b}.
+In addition, Galaxy~Zoo has found that the environmental dependence of galaxy star formation and that of morphology are not equivalent, mainly because of the abundance of quenched spiral galaxies, a large fraction of which are satellite galaxies \citep{ski09,bam09}.
+In any case, life on the main sequence appears to be governed by the action of the regulator to balance gas in- and outflows \citep{lil13}, making it a central process in galaxy evolution.
 
-In this paper, we use data from the Sloan Digital Sky Survey \citep[SDSS;][]{yor00,str02,aba09} in combination with Galaxy Zoo, the largest database of visual classifications of galaxy structure and morphology ever assembled \citep{lin08,lin11,wil13}, to test whether galaxy structure affects their star formation properties.
+In this paper, we use data from the Sloan Digital Sky Survey \citep[SDSS;][]{yor00,str02,aba09} in combination with Galaxy~Zoo, the largest database of visual classifications of galaxy structure and morphology ever assembled \citep{lin08,lin11,wil13}, to test whether galaxy structure affects their star formation properties.
 We use the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
@@
 
-The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of the total disk population.
+The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of the total star-forming disk population.
 Both the slopes and offsets of each linear fit are consistent within the formal fitting errors (Table~\ref{tbl-fits}).
@@
 Although the fraction of barred galaxies varies as a function of stellar mass \citep{she08a,cam10,mas11c,che13}, both the linear fits and ranges of the sub-populations are consistent with all star-forming galaxies.
-In other words, the presence of a bar does not affect the galaxy's position on the star-forming main sequence.
+In other words, the presence of a bar does not affect a star-forming galaxy's position on the SFMS.
 
@@
 Thus while the overall bulge strength does affect the position of a galaxy on the SFMS \citep{mar09,che12a,fan13,kav14,lan14,oma14}, the structure of the \emph{disk itself} does not.
+This is also consistent with recent models in which details of the feedback, which also relate strongly to the galaxy properties, have little effect on the SFMS \citep{hop14}.
 
@@
 This is at the very upper end of the mass range probed in our analysis of barred vs.
-unbarred galaxies (Figure~\ref{fig-bar}).
+unbarred star-forming disks (Figure~\ref{fig-bar}).
 If the increase in star formation is limited to the central kiloparsec of the disk (as demonstrated using fibre SFR measurements), an increase in possible bar-driven SFR increase is seen down to $M_\star=10^{10}~M_\odot$.
+
+The absence of an apparent influence of the bar on the SFMS is still at apparent odds with the anti-correlation between atomic gas mass fraction and the presence of a bar \citep{mas12a}.
+One possible explanation is that strong bars are driven by spiral modes with star formation proceeding radially outward from the center; in that case, the influence of the bar may not be seen in star-formation diagnostics averaged over the entire disk of the galaxy (as used in this paper).
+It is also important to note that the selection of only \emph{star-forming} disk galaxies for this study excludes passive disks, which are known to be significantly redder and more massive than their star-forming counterparts \citep{mas10a,cor12}.
 

### 2014-12-03 paper/mainsequence_morph.tex
Final typo check

@@
 \begin{abstract}
-We measure the mass-star formation relation in star-forming disk galaxies at $z<0.05$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
+We measure the mass-star formation relation in star-forming disk galaxies at $z<0.10$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
 We examine the number of spiral arms, their average pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
@@
 
-As a star-forming galaxies may exhibit a wide range of physical appearances in optical images, the natural question can be asked of whether the specifics of this physical appearance and its underlying dynamical processes have any effect on this homeostasis and therefore the galaxy's location relative to the SFMS.
+As star-forming galaxies may exhibit a wide range of physical appearances in optical images, the natural question can be asked whether the specifics of this morphology and its underlying dynamical processes have any effect on this homeostasis and therefore the galaxy's location relative to the SFMS.
 If the details of a galaxy's physical appearance are correlated with position relative to the main sequence, then the dynamical processes that give rise to them -- such as bar formation and spiral arm pitch angle -- are a fundamental aspect of the galaxy's regulatory mechanism.
@@
 \citet{pen10a,pen12} argue that galaxies grow in stellar mass during their life as star-forming galaxies on the main sequence before having their star formation quenched either by an external mechanism (`environment quenching') or by an internal mechanism (`mass quenching').
-However, \citet{del12} point out that, because of a `history bias,' galaxies of identical stellar mass may have different environmental histories that are difficult to disentangle, thus making the mass versus environment debate inherently ill-posed \citep[see also ][]{van08b}.
-In addition, Galaxy~Zoo has found that the environmental dependence of galaxy star formation and that of morphology are not equivalent, mainly because of the abundance of quenched spiral galaxies, a large fraction of which are satellite galaxies \citep{ski09,bam09}.
+However, \citet{del12} point out that, because of a `history bias,' galaxies of identical stellar mass may have different environmental histories that are difficult to disentangle, thus making the mass versus environment debate inherently ill-posed \citep[see also][]{van08b}.
+In addition, Galaxy~Zoo data has shown that the environmental dependence of galaxy star formation and that of morphology are not equivalent, mainly because of the abundance of quenched spiral galaxies, a large fraction of which are satellite galaxies \citep{ski09,bam09}.
 In any case, life on the main sequence appears to be governed by the action of the regulator to balance gas in- and outflows \citep{lil13}, making it a central process in galaxy evolution.
@@
 
-Spiral galaxies are identified according to the following thresholds in the spectroscopic GZ2 sample, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
-We identify sub-classes of spiral structure by weighting each galaxy according to the fraction of votes received in each morphological category.
-
 Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04,sal07}.
@@
 For both $M_\star$ and $SFR$, we use median values extracted from the PDF.
+
+The spiral nature of the star-forming disk galaxies are identified according to the following thresholds in the GZ2 spectroscopic sample, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
+We identify sub-classes of spiral structure by weighting each galaxy according to the fraction of votes received in each morphological category.
 
@@
 
-As a control sample, we also analyze the fits to the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local SDSS galaxies (Figures~\ref{fig-number}-\ref{fig-bar},\ref{fig-mergers}).
+As a control sample, we also analyze the fits to the underlying star-forming main sequence relation for star-forming disks as measured in a sample of local SDSS galaxies (Figures~\ref{fig-number}-\ref{fig-bar}, \ref{fig-mergers}).
 As previously demonstrated with SDSS data \citep[e.g.,][]{bri04}, there is a tight correlation between $M_\star$ and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
@@
 Both the slopes and offsets of each linear fit are consistent within the formal fitting errors (Table~\ref{tbl-fits}).
-There are too few galaxies with reliable spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all multiplicities at $10^8<M_\star/M_\odot<10^{11}$.
+There are too few individual galaxies with confirmed spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all arm multiplicities at $10^8<M_\star/M_\odot<10^{11}$.
 
@@
 The underlying reason is that many ``one-armed spirals'' are in fact caused by bridges or tidal tails from interactions with a nearby companion instead of secular processes.
-We discuss the likely role of merging/interacting galaxies in Section~\ref{sec-discussion} (see Figure~\ref{fig-mergers}).
+We discuss the likely role of merging/interacting galaxies in Section~\ref{sec-discussion} (also see Figure~\ref{fig-mergers}).
 
@@
 We have repeated the analysis above for the sub-sample of disk galaxies for which the spiral multiplicity is determined with high confidence ($p_\textrm{arms~number} > 0.8$) by GZ2, thus eliminating ``intermediate'' galaxies for which the morphology is uncertain.
-These galaxies ($N=14,148$) are dominated by two-armed spirals, which are the only multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\odot$ are detected.
-Our results for the SFMS are qualitatively the same as when using the weighting scheme, although we note that there are too few examples ($N<10$) of either three- or four-armed spirals for a reliable fit.
+These galaxies ($N=14,148$) are dominated by two-armed spirals, which are the only spiral multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\odot$ are detected.
+The results for the SFMS are qualitatively the same as when using the weighting scheme, although we note that there are too few examples ($N<10$) of either three- or four-armed spirals for a reliable fit.
 The offset of the one-armed spirals above the SFMS is also significantly more pronounced when using high-confidence morphologies.
@@
 There is no significant shift with respect to the SFMS as a function of pitch angle for spiral galaxies.
-We note that the small increase above the main sequence for loosely-wound galaxies is also consistent with \citet{cas13}, who show that this morphology also correlates with close pairs and interactions.
+The small increase above the main sequence for loosely-wound galaxies is also consistent with \citet{cas13}, who show that this morphology also correlates with close pairs and interactions.
 
@@
 Dotted lines show the weighted least-squares linear fit as split by pitch angle; the solid line is the fit to all star-forming galaxies.
-The positive offset in SFR for loosely-wound spiral arms is interpreted as contamination by merging pairs of galaxies (Section~\ref{sec-discussion}).
+The slight positive offset in SFR for loosely-wound spiral arms is interpreted as contamination by merging pairs of galaxies (Section~\ref{sec-discussion}).
 \label{fig-winding}}
@@
 This tracks only the slope and offset of the distribution, however, and not its width.
-We thus also compared the sample standard deviation ($\sigma_{SFR}$) as a function of mass of the star-forming galaxy population to its various subsamples.
+We thus also compare the sample standard deviation ($\sigma_{SFR}$) to the star-forming galaxy population over its various morphological subsamples.
 The value of $\sigma_{SFR}$ monotonically decreases with increasing mass over the range $6.0<\log(M/M_\odot)<11.5$.
@@
 We have examined all the populations of galaxies described above (bars, arm pitch angle, arm multiplicity) and measured the differences when using specific star formation rate ($\textrm{sSFR}\equiv\textrm{SFR}/M_\star$) instead of SFR.
-There is no significant change in the results.
+There is no significant change in any of the results.
 
@@
 In these systems, which are in various stages of coalescence, star formation rates are increased by only an average of 0.29~dex (less than a factor of two).
-\citet{dar10} showed that in the local ($z<0.1$) Universe, galaxies with intense bursts of star formation are limited to only the spiral (disc) galaxies.
+\citet{dar10} showed that at $z<0.1$, galaxies with intense bursts of star formation are limited to only the spiral (disc) galaxies.
 This increase in star formation for mergers does show a strong evolution in redshift out to at least $1.5<z<2.5$, likely due to the higher gas fractions involved \citep{dad10,rod11}.

### 2015-01-29 paper/mainsequence_morph.tex
Adding references from AAS 2015; changed wording on SFMS

@@
 \begin{abstract}
-We measure the mass-star formation relation in star-forming disk galaxies at $z<0.10$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
+We measure the stellar mass-star formation rate relation in star-forming disk galaxies at $z<0.10$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
 We examine the number of spiral arms, their average pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
@@
 Observations at a range of redshifts have established that the star formation rate (SFR) of a galaxy is strongly correlated to its stellar mass ($M_\star$).
-This ``star-forming main sequence'' (SFMS) is nearly linear and has remarkably small scatter at low redshifts \citep{bri04}.
+This ``star-forming main sequence'' (SFMS) is nearly linear and has remarkably small scatter at low redshifts \citep{bri04,sal07}.
 Recent observations of star-forming galaxies at high redshifts show that this main sequence remains out to high redshift, but the normalisation shifts upward so that galaxies of the same $M_\star$ have a higher SFR at high redshift \citep{noe07,dad07}.
@@
 Uncertainties $\sigma_\alpha$ and $\sigma_\beta$ are taken from the covariance matrix for each least-squares fit (Table~\ref{tbl-fits}).
+The low number of high-mass galaxies in this volume also means that we are insensitive to possible turnovers in the SFMS at  $M_\star>10^{10}~M_\odot$ \citep{whi14,lee15}, emphasizing our choice to fit a linear model.
 
@@
 \citet{abr14} found that by normalizing galaxies by the stellar mass of the disk alone, the slope of the SFMS is consistent with only a linear trend (removing any dependence on mass).
-Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the intrinsic dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, and/or environment, among other factors.
+Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the intrinsic dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, environment and/or gas accretion history, among other factors \citep{dut10}.
 Our results show that the neither of the first two factors play dominant roles in controlling $\sigma_{SFR}$, at least as far as major dynamical drivers (such as strong bars or additional arms) are concerned.
@@
 This is also consistent with recent models in which details of the feedback, which also relate strongly to the galaxy properties, have little effect on the SFMS \citep{hop14}.
+Alternatively, this also agrees with models in which the SFMS is the result of stochastic processes, rather than deterministic physics related to galaxy evolution \citep{kel14b}.
 
@@
 
-We thank Rory Smith and Lucio Mayer for useful discussions.
+We thank Rory Smith, Lucio Mayer, and Bruce Elmegreen for useful discussions.
 This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05} and Astropy, a community-developed core Python package for astronomy \citep{ast13}.
 The development of Galaxy~Zoo~2 was supported by The Leverhulme Trust.
-KWW and LFF would like to acknowledge support from the US National Science Foundation under grant DRL-0941610.
+KWW and LFF are supported by the US National Science Foundation under grant DRL-0941610.
 KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1.

### 2015-01-29 gz_mainsequence.py
Plot star-forming galaxies vs. all galaxies to assess completeness

@@ -1802,7 +1802,25 @@ def volume_limited(data):
 
     return None
 
+def sfr_completeness(data):
+
+    allgals = get_sample(data,starforming=False)
+    sf = get_sample(data,starforming=True)
+    mass_all,sfr_all,sfr_err_all,ssfr_all,ssfr_err_all = get_mass_sfr(allgals)
+    mass_sf,sfr_sf,sfr_err_sf,ssfr_sf,ssfr_err_sf = get_mass_sfr(sf)
+
+    # Plot SFR galaxies as grayscale contour
+    mass_bins,sfr_bins,ssfr_bins = bins()
+
+    fig = plt.figure(1,(10,6))
+    fig.clf()
+    ax = fig.add_subplot(111)
+    h = ax.hist2d(mass_sf,sfr_sf,bins=50,cmap = cm.gray_r, norm=LogNorm())
+
+    ax.scatter(mass_all,sfr_all)
+    ax.set_xlim(6,11.5)
+
+    return None
 
 
-    
 

### 2015-01-30 gz_mainsequence.py
Updated to create mass-limited results for all plots

@@ -1,5 +1,7 @@
+# Branch - make all plots using only a lower limit of M_star = 10**8 M_sun
+
 import numpy as np
-import matplotlib
+import time
 
 from matplotlib import rc
 from matplotlib import pyplot as plt
@@ -14,11 +16,14 @@ from scipy.stats import ks_2samp
 from scipy.linalg.basic import LinAlgError
 from astroML.plotting import hist as histML
 
-plt.ion()
+import warnings
+warnings.simplefilter(action = "ignore", category = (FutureWarning,np.RankWarning))
+
+#plt.ion()
 
 gz_path = '/Users/willettk/Astronomy/Research/GalaxyZoo'
 gzm_path = '%s/gzmainsequence' % gz_path
-fig_path = '%s/paper/figures' % gzm_path
+fig_path = '%s/paper/figures/masslim' % gzm_path
 fits_path = '%s/fits' % gz_path
 
 aw_tasks = ['t10_arms_winding_'+r for r in ('a28_tight','a29_medium','a30_loose')]
@@ -29,6 +34,7 @@ aw_colors = ('red','green','blue')
 z_lowerlim = 0.000      # any reason for a lower limit?
 z_upperlim = 0.085      # upper limit of reliable GZ2 classification
 absmag_lim = -19.5
+mass_lim = 1e8
 
 def get_data():
 
@@ -47,12 +53,16 @@ def get_sample(data,starforming=True):
     redshift = (data['REDSHIFT'] <= z_upperlim) & (data['REDSHIFT'] >= z_lowerlim)
     #absmag = data['PETROMAG_MR'] < absmag_lim        # could use 0.085 and -20.17, or 0.05 and -19.5
 
+    # Restrict sample to galaxies above 10**8 M_sun (completeness limit of MPA-JHU; Brinchmann+04)
+    masslim = (data['MEDIAN_MASS'] >= 8.)
+
     if starforming:
         #sample = data[sf & redshift & absmag]
-        sample = data[sf & redshift]
+        sample = data[sf & redshift & masslim]
     else:
         #sample = data[redshift & absmag]
         sample = data[redshift]
+
 
     return sample
 
@@ -80,57 +90,14 @@ def bins(mass_min=6,mass_max=13,sfr_min=-5,sfr_max=2,ssfr_min=-12,ssfr_max=-8,nb
 
     return mass_bins,sfr_bins,ssfr_bins
     
[…]

### 2015-01-30 gz_mainsequence.py
Added verbose tag to show stats for all SF galaxies

@@ -202,7 +202,7 @@ def plot_ms_arms_number(sf_sample,weighted=False,contour=False,plot_ssfr=False,v
         ax.text(6.2,ytextloc,r'$N_{arms} = $%s' % label, color='k',fontsize=18)
 
         # Plot the linear fits for all star-forming galaxies
-        plot_fits('SF galaxies',mass,yval,None,ax,'black',lw=1,ls='-')
+        plot_fits('SF galaxies',mass,yval,None,ax,'black',lw=1,ls='-',verbose=verbose)
         ax.set_xlim(6,11.5)
 
         '''

### 2015-02-03 gz_mainsequence.py
Fixed auto aspect for merger plot

@@ -160,7 +160,7 @@ def plot_ms_arms_number(sf_sample,weighted=False,contour=False,plot_ssfr=False,v
             yval_scatter = morph_sample['MEDIAN_SFR'] - morph_sample['MEDIAN_MASS']
             ytextloc = -11.5
         else:
-            ax.set_ylim(-3.9,2)
+            ax.set_ylim(-2.9,2)
             ylabel='SFR '+r'$[\log\/M_\odot/\mathrm{yr}]$'
             yval_weighted = spirals['MEDIAN_SFR']
             yval_scatter = morph_sample['MEDIAN_SFR']
@@ -170,6 +170,9 @@ def plot_ms_arms_number(sf_sample,weighted=False,contour=False,plot_ssfr=False,v
             ax.set_xlabel('Stellar mass [log '+r'$\/M/M_\odot$]',fontsize=16)
         if idx < 3:
             ax.get_xaxis().set_ticks([])
+        else:
+            ax.get_xaxis().set_ticks([8.,9.,10.,11.])
+
         if idx == 0 or idx == 3:
             ax.set_ylabel(ylabel,fontsize=16)
         else:
@@ -199,11 +202,11 @@ def plot_ms_arms_number(sf_sample,weighted=False,contour=False,plot_ssfr=False,v
 
             plot_fits(label,morph_sample['MEDIAN_MASS'],yval_scatter,None,ax,c,verbose=verbose)
 
-        ax.text(6.2,ytextloc,r'$N_{arms} = $%s' % label, color='k',fontsize=18)
+        ax.text(8.2,ytextloc,r'$N_{arms} = $%s' % label, color='k',fontsize=18)
 
         # Plot the linear fits for all star-forming galaxies
         plot_fits('SF galaxies',mass,yval,None,ax,'black',lw=1,ls='-',verbose=verbose)
-        ax.set_xlim(6,11.5)
+        ax.set_xlim(8,11.5)
 
         '''
         # Print number of galaxies in each category
@@ -274,7 +277,7 @@ def plot_ms_arms_winding(sf_sample,weighted=False,contour=False,plot_ssfr=False,
[…]

### 2015-02-03 paper/mainsequence_morph.tex
Updated publication date to 2015
First set of changes for mass limit

@@
 \usepackage{color}
-\usepackage{hyperref}
+\usepackage[draft]{hyperref}
 \bibliographystyle{mn2e}
@@
 \date{Accepted XXXXXXX}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2014}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}
 \maketitle
@@
 Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04,sal07}.
-We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep*{bal81} below the \citet{kau03} demarcation.
-We exclude galaxies classified as star-forming but with low signal-to-noise ratio $(S/N > 3)$.
-For both $M_\star$ and $SFR$, we use median values extracted from the PDF.
+We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We select only galaxies with $M_\star > 10^8 M_\odot$, for which \citet{bri04} estimate that the MPA-JHU sample is complete.
+Star-forming galaxies are separated from other emission-line galaxies using the standard BPT classification \citep*{bal81} below the \citet{kau03} demarcation.
+Galaxies classified as star-forming but with low signal-to-noise ratio $(S/N > 3)$ are also excluded.
+Both $M_\star$ and $SFR$ are measured using median values extracted from the PDF.
+% Footnote is breaking LaTeX.
 
@@
 %How many galaxies are there in the total sample? What is the mass, color, and redshift range?
-The total sample analyzed in this paper consists of 49,097 star-forming galaxies.
+The total sample analyzed in this paper consists of 48,405 star-forming galaxies.
 These are selected from the GZ2 spectroscopic sample with $z<0.085$ (the limit of reliable debiased morphological classification for GZ2) for galaxies classified as actively star-forming ($BPT=1$) from the MPA-JHU emission line measurements.
@@
 \hline						
-SF galaxies  & 49097  & $0.71$  & $-7.04$   & $5.86\times10^{-6}$  & $5.70\times10^{-4}$  \\
+SF galaxies  & 48405  & $0.72$  & $-7.08$  &  $7.13\times10^{-6}$  & $6.98\times10^{-4}$  \\
 \hline
-1 arm        & 289    & $0.61$  & $-5.81$  &  $6.57\times10^{-3}$  & $6.49\times10^{-1}$  \\
-2 arms       & 5641   & $0.78$  & $-7.65$  &  $1.27\times10^{-4}$  & $1.30\times10^{-2}$  \\
-3 arms       & 997    & $0.54$  & $-5.16$  &  $4.39\times10^{-3}$  & $4.70\times10^{-1}$  \\
-4 arms       & 285    & $0.35$  & $-3.27$  &  $1.15\times10^{-1}$  & $1.19\times10^{ 1}$  \\
-5+ arms      & 289    & $0.64$  & $-6.88$  &  $7.20\times10^{-2}$  & $6.91\times10^{0 }$  \\
-can't tell   & 2017   & $0.69$  & $-7.10$  &  $1.06\times10^{-2}$  & $1.04\times10^{0 }$  \\
+1 arm        & 289    & $0.74$  & $-7.18$  &  $2.70\times10^{-5}$  & $2.69\times10^{-3}$  \\
+2 arms       & 5641   & $0.78$  & $-7.69$  &  $3.70\times10^{-5}$  & $3.78\times10^{-3}$  \\
+3 arms       & 997    & $0.71$  & $-6.99$  &  $4.49\times10^{-5}$  & $4.65\times10^{-3}$  \\
+4 arms       & 285    & $0.71$  & $-7.05$  &  $4.80\times10^{-5}$  & $4.93\times10^{-3}$  \\
+5+ arms      & 289    & $0.80$  & $-8.11$  &  $7.54\times10^{-5}$  & $7.53\times10^{-3}$  \\
+can't tell   & 2017   & $0.77$  & $-7.72$  &  $4.53\times10^{-5}$  & $4.54\times10^{-3}$  \\
 \hline
@@
 $N$ is the number of galaxies with plurality classifications for spiral arm multiplicity and pitch angles, and at a cutoff of $p_{bar}=0.4$ for barred galaxies.
-$\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit}.\label{tbl-fits}}
+$\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit} to data weighted by morphological vote fractions for spiral arm multiplicity and pitch angle, and to subsamples split by morphology for barred/unbarred and merging galaxies.\label{tbl-fits}}
 \end{table}
 
-To parametrize the $M_\star-SFR$ relationship, we apply a simple linear model for the total sample and subsamples.
+To parametrize the $M_\star-SFR$ relationship for the full sample of star-forming galaxies, we apply a simple linear model for the total sample and subsamples.
 We apply a least-squares fit where the data are weighted by the uncertainty in SFR (computed as the mean difference in the 16th and 84th percentiles from the MPA-JHU PDFs).
@@
 \noindent where $\alpha$ and $\beta$ represent the slope and offset, respectively.
-Uncertainties $\sigma_\alpha$ and $\sigma_\beta$ are taken from the covariance matrix for each least-squares fit (Table~\ref{tbl-fits}).
+The formal uncertainties $\sigma_\alpha$ and $\sigma_\beta$ are taken from the covariance matrix for each least-squares fit (Table~\ref{tbl-fits}).
+In fitting subsamples selected by morphology, we apply the same fit to all star-forming galaxies, but weighted by the morphological likelihood in the GZ2 data.
 The low number of high-mass galaxies in this volume also means that we are insensitive to possible turnovers in the SFMS at $M_\star>10^{10}~M_\odot$ \citep{whi14,lee15}, emphasizing our choice to fit a linear model.
@@
 
-The sample of galaxies examined here is not explicitly constructed to be volume-limited.
+The sample of galaxies examined here is not explicitly constructed to be volume-limited (although \citealt{bri04} estimate that SFR and $M_\star$ are essentially complete for the mass and $S/N$ limits employed).
 The main reason for this is that we are comparing effects between sub-samples of galaxies using the same selection functions.
@@
 As previously demonstrated with SDSS data \citep[e.g.,][]{bri04}, there is a tight correlation between $M_\star$ and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
-The relationship extends over at least 4~orders of magnitude in both $M_\star$ and SFR.
+The relationship extends over at least 3~orders of magnitude in both $M_\star$ and SFR.
 Fits to the SFMS for all subsamples in this paper are listed in Table~\ref{tbl-fits}.
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_arms_number_weighted_contour.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_number_weighted_contour.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the distribution of all star-forming galaxies in SDSS from the MPA-JHU DR7 catalog.
@@
 For this analysis, galaxies in each mass/SFR bin is weighted by the vote fraction for the morphology being tested.
-
 The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of the total star-forming disk population.
 Both the slopes and offsets of each linear fit are consistent within the formal fitting errors (Table~\ref{tbl-fits}).
-There are too few individual galaxies with confirmed spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all arm multiplicities at $10^8<M_\star/M_\odot<10^{11}$.
+%There are too few individual galaxies with confirmed spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all arm multiplicities at $10^8<M_\star/M_\odot<10^{11}$.
 
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_winding.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_arms_winding_weighted.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_winding_weighted.pdf}
 \caption{Same as Figure~\ref{fig-winding}, but with colormaps showing all spiral galaxies weighted by the GZ2 vote fractions for ``tight'', ``medium'', and ``loose'' winding spiral arms. 
@@
 %\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
-\includegraphics[angle=0,width=7.0in]{figures/ms_bar_contour.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_bar_contour.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.
@@
 %\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
-\includegraphics[angle=0,width=3.5in]{figures/sigma_mstar.pdf}
+\includegraphics[angle=0,width=3.5in]{figures/masslim/sigma_mstar.pdf}
 \caption{Width of the star-forming main sequence ($\sigma_{SFR}$) as a function of stellar mass, as measured by the sample standard deviation.
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/ms_mergers_both.pdf}
+\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_mergers_both.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.

### 2015-02-04 paper/mainsequence_morph.tex
Completed draft 2 with new mass limits

@@
 Galaxies classified as star-forming but with low signal-to-noise ratio $(S/N > 3)$ are also excluded.
-Both $M_\star$ and $SFR$ are measured using median values extracted from the PDF.
+Both $M_\star$ and SFR are measured using median values extracted from the PDF.
 % Footnote is breaking LaTeX.
@@
 
-Two-armed spiral galaxies and those with uncertain multiplicities are the only morphologies that extend slightly below the SFMS.
-One possibility is that this is a consequence of galaxies that have already begun the process of quenching.
+The only morphologies that extend slightly below the SFMS are those with the highest level of multiplicity (five or more arms).
+The best-fit line for this population has a steeper slope, driven by the galaxies with relatively low SFR at $10^9<M/M_\star<10^{10}$.
+This is a new and unusual result; one possible explanation is that stellar disks in the process of quenching will have fewer bright \mbox{H\,{\sc ii}}~regions and the contrast between the arm and interarm regions is increased.
+This could result in better visibility for older (and potentially overlapping) spatial modes in the galaxy's disk, increasing the measured multiplicity.
+It should be emphasized, though, that 5+-arm spirals represent the smallest morphological group in the sample, and that the associated fit errors in Table~\ref{tbl-fits} are the largest for any multiplicity; simple statistical variance cannot be ruled out as an explanation for the best-fit line to the SFMS.
+
+%One possibility is that this is a consequence of galaxies that have already begun the process of quenching.
 As a result, the star-formation rate is depleted and the contrast of spiral arms against the rest of the disk (which for visual identification is at least in part dependent on bright knots of recent star formation) makes the multiplicity more difficult to identify.
@@
 We have repeated the analysis above for the sub-sample of disk galaxies for which the spiral multiplicity is determined with high confidence ($p_\textrm{arms~number} > 0.8$) by GZ2, thus eliminating ``intermediate'' galaxies for which the morphology is uncertain.
-These galaxies ($N=14,148$) are dominated by two-armed spirals, which are the only spiral multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\odot$ are detected.
+These galaxies ($N=10,035$) are dominated by two-armed spirals, which are the only spiral multiplicity for which significant numbers of galaxies at $M_\star<10^9~M_\odot$ are detected.
 The results for the SFMS are qualitatively the same as when using the weighting scheme, although we note that there are too few examples ($N<10$) of either three- or four-armed spirals for a reliable fit.
@@
 It should also be noted that the galaxies in GZ2 flagged as a function of pitch angle are not representative of the true vote distribution.
-The raw numbers in Figure~\ref{fig-winding} suggest that most spiral galaxies are either tightly or loosely wound.
-In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the medium option at the 80\% level which sets the flag.
+The points in Figure~\ref{fig-winding} would suggest that there are relatively few spiral galaxies overall, and that most are either tightly or loosely wound.
+In fact, the plurality classification for most galaxies is for medium-winding; the spread in votes is typically large, though, and so users rarely agree on the ``medium'' option at the 80\% level which sets the flag.
 An alternative method is to analyze the morphology of spiral galaxies by directly weighting them as a function of the pitch angle categories (Figure~\ref{fig-winding_weighted}), which has the advantage of including all spiral galaxies.
@@
 We thus also compare the sample standard deviation ($\sigma_{SFR}$) to the star-forming galaxy population over its various morphological subsamples.
-The value of $\sigma_{SFR}$ monotonically decreases with increasing mass over the range $6.0<\log(M/M_\odot)<11.5$.
-For all populations examined in this paper, though, the widths of their distributions are consistent with the broader population (Figure~\ref{fig-sigma}).
+The value of $\sigma_{SFR}$ monotonically decreases with increasing mass over the range $8.0<\log(M/M_\odot)<11.5$.
+For all morphological populations examined in this paper, the widths of their distributions are consistent with the broader population (Figure~\ref{fig-sigma}).
 
@@
 
-We have examined all the populations of galaxies described above (bars, arm pitch angle, arm multiplicity) and measured the differences when using specific star formation rate ($\textrm{sSFR}\equiv\textrm{SFR}/M_\star$) instead of SFR.
+We have also examined all the populations of galaxies described above (bars, arm pitch angle, arm multiplicity) and measured the differences when using specific star formation rate ($\textrm{sSFR}\equiv\textrm{SFR}/M_\star$) instead of SFR.
 There is no significant change in any of the results.

### 2015-02-04 response_gzmainsequence.txt
Adding referee report and comments

We thank the reviewer for the thoughtful read and suggestions for improving this manuscript. We have addressed all of the issues, primarily centered on analyzing a smaller sample of galaxies due to concerns about completeness of star formation rates at lower masses. The main scientific conclusion of this paper --- namely that changes in disk morphology do not affect the position of a galaxy on the star-forming main sequence --- have not changed as a result of this new analysis.

A more detailed response and list of the changes is attached below. We hope the manuscript is now ready for publication.

Reviewer's Comments:

Comments to the Author
The paper « Galaxy Zoo: the dependence of the star formation-stellar mass relation on spiral disk morphology » compares the positions of star-forming galaxies of various disk morphologies to the best fitting line of the SFR-M* relation. This study presents an interesting discussion of e.g. the role of multiple arms in disk galaxies but suffers from a major problem that strongly limits the interpretation. All the analysis relies on the comparison of a sub-sample of the galaxies with a reference trend shown in the figures with a black solid line. It is the definition of this line, more precisely its slope and normalization that seems probmematic to me.

Although this is not clearly stated in the text, this line was apparently obtained by fitting the whole sample of star-forming galaxies with no restriction in stellar mass or SFR. I believe that such fit can be misleading for the following reason. There is necessarily a completeness limit in SFR and this can be seen in the distribution of grey squares that represent the full sample in all the figures. Since all figures have overlayed on these gray squares some colored contours or points, the easiest is to look at the middle figure in Fig.2 where the full sample can be best seen. By eye, I would say that the completeness limit (which is obviously above the detection limit) in SFR is above 0.01 Msun/yr and probably not very far from 0.1 Msun/yr. This naturally implies that the stellar mass range around 10^7-10^8 Msun does not provide a robust measurement of the SFR-M* main sequence and should not be used to determine the best-fitting black solid line.

    The original sample used did not have any explicit cut on mass or SFR. 
    We have assessed the completeness of the sample (including a V/V_max test)
    as well as consulting estimates from the original MPA-JHU paper (Brinchmann
    et al. 2004). They state that the sample is complete above stellar masses
    of 10^8 M_sun; we have adopted that same cutoff for all analysis in this
    paper.

    This eliminated 692 galaxies (less than 2%) star-forming galaxies from the
    sample; we have redone all analyses in the paper on this new sample. 
    The bulk of the results have not changed, and new fits and uncertainties
    are given in Table 1.

    Summary of changes:

        - arms number: 2-armed spirals no longer fall below the main sequence.
            5-armed spirals fall slightly below the main sequence, but this
            may be the result of smaller statistical samples. 
        - arm pitch angle: no change
        - bar: no change
        - mergers: slight decrease (5%) in the average SFR increase for a merging
            galaxy, from 0.307 to 0.286 dex.

    We have also put in a more explicit discussion of how the overall
    trend line is fit, including a discussion of weighting, in Section 2.

The authors do not discuss at all the completeness of the sample but this is an important information for the following reason: at low masses, i.e. in the 10^7-8 Msun range, the fraction of galaxies with an enhanced sSFR is artificially enhanced leading to an overestimate of the sSFR in this range and therefore to an underestimate of the slope of the SFR-M* relation. The fact that the slope of the SFR-M* relation is affected by this effect can be seen in Fig.1 where all colored contours in each one of the 6 panels have their barycenter and central contours systematically above the black solid line. I would expect that if the authors were to only fit the full sample in the range where the sample is complete in SFR, they would find a better agreement between their contours and the black line.

    This is confirmed; in particular, the agreement between 2-armed spirals
    and the entire SF population is now closer. The sample of 5+-armed spirals
    is the only morphology to show any offset toward lower SFR at a given mass;
    we discuss tentative reasons for this in Section 3.

    The trend for 1-armed spirals to be slightly increased in SFR per stellar
    mass is confirmed in the mass-limited sample. We interpret this as
    a signal of the presence of merging galaxies and tidal tails, as before.

As a result, we would also expect the point made in the 6th paragraph of Section 3 to be revised. In that paragraph, it is written that two-armed spiral galaxies extend slightly below the SFMS. This statement suffers in my opinion from two uncertainties. First the one that I mentioned above, i.e. the reference line is biased by a domain affected by completeness. Second, this Narms=2 subsample contains 20 times more galaxies than Narms=1 and 6 times more than Narms=3, hence before concluding that the galaxies with Narms=2 include galaxies with low sSFR and interpreting this result, the authors should first make sure that this cannot be explained by a simple statistical effect, namely that one needs a very large sample of galaxies to start sampling the low sSFR galaxies.

    The mild offset in 2-armed spirals does not appear when restricting
    the mass and SFR range of the sample. We have removed the discussion
    of this in Section 3.

In its present stage, the paper is not ready for publication since it does not provide a reliable justification of the slope of the SFR-M* relation for the whole sample of star-forming galaxies which is then used as a reference to discuss the position of various disk morphologies. We suggest that the author clearly establish a range in SFR and M* within which their galaxies fairly sample the SFR-M* relation, determine the slope of their reference trend in this range and not over the full galaxy sample including the very low SFR and M* ranges where the sample is biased due to incompleteness, and then use this new reference trend to make their comparison. If instead the authors consider their sample to fairly sample the SFR-M* relation they should explain why and explain the reason why all their subsamples are systematically biased toward higher sSFR in Fig.1. Finally, if they wish to keep their interpretation of an evidence of quenching of Narms=2 galaxies, they should discuss its statistical meaning, e.g. by randomly selecting in that sample 289 galaxies as in the Narm=1 sample and determining the % of cases where they get such low sSFR.

    As discussed above, our results are now limited to a mass range of
    10^8 < M/M_sun < 10^11.5, with star formation rates limited by the
    corresponding signal-to-noise ratios (10^-3 < SFR/(M_sun/yr) < 10^2). 
    All our analyses in this paper (plus other references in the literature
    that use this sample) indicates that this is a complete sample
    and does not suffer from the biases that would be present in a non-volume-
    limited dataset.

These changes should be very easy to make since they only concern the reference trend and they do not alter the main conclusions of the paper that rely on the comparison of the positions of each subsample, which remain unchanged e.g. in Fig.1 it will remain true that the various colored contours do not exhibit any major difference from one another. Similarly for the barred and unbarred galaxies in Fig.4 which will remain comparable.

    All figures and fits have been revised for the new mass limits.

### 2015-02-09 paper/mainsequence_morph.tex
Small changes; submitted to MNRAS round 2

@@
 \begin{abstract}
-We measure the stellar mass-star formation rate relation in star-forming disk galaxies at $z<0.10$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
-We examine the number of spiral arms, their average pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
+We measure the stellar mass-star formation rate relation in star-forming disk galaxies at $z\le0.085$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
+We examine the number of spiral arms, their relative pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
 We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only boost the SFR above the main relation by $\sim0.3$~dex; this is significantly smaller than the increase seen in merging systems at $z>1$.
@@
 In addition, Galaxy~Zoo data has shown that the environmental dependence of galaxy star formation and that of morphology are not equivalent, mainly because of the abundance of quenched spiral galaxies, a large fraction of which are satellite galaxies \citep{ski09,bam09}.
-In any case, life on the main sequence appears to be governed by the action of the regulator to balance gas in- and outflows \citep{lil13}, making it a central process in galaxy evolution.
+In any case, life on the main sequence appears to be governed by the action of the regulator to balance gas inflows and outflows \citep{lil13}, making the SFMS a central process in galaxy evolution.
 
-In this paper, we use data from the Sloan Digital Sky Survey \citep[SDSS;][]{yor00,str02,aba09} in combination with Galaxy~Zoo, the largest database of visual classifications of galaxy structure and morphology ever assembled \citep{lin08,lin11,wil13}, to test whether galaxy structure affects their star formation properties.
+In this paper, we use data from the Sloan Digital Sky Survey \citep[SDSS;][]{yor00,str02,aba09} in combination with Galaxy~Zoo, the largest database of visual classifications of galaxy structure and morphology ever assembled \citep{lin08,lin11,wil13}, to test whether disk structure affects a galaxy's star formation properties.
 We use the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.
@@
 Galaxies classified as star-forming but with low signal-to-noise ratio $(S/N > 3)$ are also excluded.
-Both $M_\star$ and SFR are measured using median values extracted from the PDF.
-% Footnote is breaking LaTeX.
+Both $M_\star$ and SFR are measured using median values extracted from the probability distribution functions.
 
-The spiral nature of the star-forming disk galaxies are identified according to the following thresholds in the GZ2 spectroscopic sample, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
-We identify sub-classes of spiral structure by weighting each galaxy according to the fraction of votes received in each morphological category.
-
-%How many galaxies are there in the total sample? What is the mass, color, and redshift range?
-The total sample analyzed in this paper consists of 48,405 star-forming galaxies.
-These are selected from the GZ2 spectroscopic sample with $z<0.085$ (the limit of reliable debiased morphological classification for GZ2) for galaxies classified as actively star-forming ($BPT=1$) from the MPA-JHU emission line measurements.
-The average color for the star-forming galaxies is relatively blue, with $(u-r)=1.6\pm0.4$.
+The spiral nature of the star-forming disk galaxies is identified according to the following thresholds in the GZ2 spectroscopic sample, where $p$ is the debiased vote fraction and $N$ the weighted number of total votes: $p_\textrm{features/disk} > 0.430$, $p_\textrm{not~edgeon} > 0.715$, $p_\textrm{spiral}>0.619$, and $N_\textrm{spiral}>20$.
+These cuts are chosen to ensure reliable identification and with enough data points such that spiral substructure has a reasonable estimate of the associated uncertainty.
+Sub-classes of spiral structure are identified by weighting each galaxy according to the fraction of votes received in each morphological category.
 
@@
 \caption{Basic properties of the $M_\star-SFR$ linear fit for GZ2 star-forming galaxies.
-$N$ is the number of galaxies with plurality classifications for spiral arm multiplicity and pitch angles, and at a cutoff of $p_{bar}=0.4$ for barred galaxies.
+$N$ is the number of galaxies with plurality classifications for spiral arm multiplicity and pitch angles, and at a cutoff of $p_{bar}=0.4$ for barred/unbarred galaxies.
 $\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit} to data weighted by morphological vote fractions for spiral arm multiplicity and pitch angle, and to subsamples split by morphology for barred/unbarred and merging galaxies.\label{tbl-fits}}
@@
 
+%How many galaxies are there in the total sample? What is the mass, color, and redshift range?
+The total sample analyzed in this paper consists of 48,405 star-forming galaxies.
+These are selected from the GZ2 spectroscopic sample with $z<0.085$ (the limit of reliable debiased morphological classification for GZ2) for galaxies classified as actively star-forming ($BPT=1$) from the MPA-JHU emission line measurements.
+The average color for the star-forming galaxies is relatively blue, with $(u-r)=1.6\pm0.4$.
+
 To parametrize the $M_\star-SFR$ relationship for the full sample of star-forming galaxies, we apply a simple linear model for the total sample and subsamples.
-We apply a least-squares fit where the data are weighted by the uncertainty in SFR (computed as the mean difference in the 16th and 84th percentiles from the MPA-JHU PDFs).
+We apply a least-squares fit where the data are weighted by the uncertainty in SFR (computed as the mean difference in the $16^{\rm th}$ and $84^{\rm th}$ percentiles from the MPA-JHU PDFs).
 The data are then fit to:
@@
 One possibility is that volume-limiting would deal with galaxies in which the dust content is high enough to obscure all emission lines, even in the presence of significant star formation.
-Such galaxies, typically [U]LIRGs, have very low space-densities at $z<0.1$, and typically lack the regular disk structure needed to categorize it.
+Such galaxies, typically [U]LIRGs, have very low space-densities at $z<0.1$, and typically lack the regular disk structure needed to categorize it for the morphologies considered here.
 
@@
 The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of the total star-forming disk population.
-Both the slopes and offsets of each linear fit are consistent within the formal fitting errors (Table~\ref{tbl-fits}).
+Both the slopes and offsets of each linear fit are consistent within the formal fitting errors in Table~\ref{tbl-fits}.
 %There are too few individual galaxies with confirmed spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all arm multiplicities at $10^8<M_\star/M_\odot<10^{11}$.
@@
 We have also examined all the populations of galaxies described above (bars, arm pitch angle, arm multiplicity) and measured the differences when using specific star formation rate ($\textrm{sSFR}\equiv\textrm{SFR}/M_\star$) instead of SFR.
-There is no significant change in any of the results.
+There is no significant change in any of the morphologically-selected categories as compared to the general SFMS.
 
@@
 
-We analyze for the first time the detailed structure of disks in large samples of star-forming galaxies as related to their position on the $M_\star$-SFR relation.
+We analyze for the first time the detailed structure of disks in large samples of star-forming galaxies in the local Universe as related to their position on the $M_\star$-SFR relation.
 This analysis is made possible by using morphological classifications from the Galaxy~Zoo~2 project.

### 2015-02-09 paper/mainsequence_morph.tex
Adding color for ref response highlights
Highlighted changes in text for referee response

@@
 \newcommand{\mytilde}{\textasciitilde}
-\newcommand{\kevin}{{\color{red}\textbf{Kevin}}}
+
+% Highlight referee response
+\definecolor{titlecol}{rgb}{0,0,1}
+\def\rr{\color{titlecol}}
 
@@
 \begin{abstract}
-We measure the stellar mass-star formation rate relation in star-forming disk galaxies at $z\le0.085$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
-We examine the number of spiral arms, their relative pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
+We measure the {\rr stellar mass-star formation rate relation in star-forming disk galaxies at $z\le0.085$, using Galaxy~Zoo morphologies to examine different populations of spirals as classified by their kiloparsec-scale structure.
+We examine the number of spiral arms, their relative} pitch angle, and the presence of a galactic bar in the disk, and show that both the slope and dispersion of the $M_\star$-SFR relation is constant when varying all the above parameters.
 We also show that mergers (both major and minor), which represent the strongest conditions for increases in star formation at a constant mass, only boost the SFR above the main relation by $\sim0.3$~dex; this is significantly smaller than the increase seen in merging systems at $z>1$.
@@
 Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04,sal07}.
-We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We select only galaxies with $M_\star > 10^8 M_\odot$, for which \citet{bri04} estimate that the MPA-JHU sample is complete.
+We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} {\rr We select only galaxies with $M_\star > 10^8 M_\odot$, for which \citet{bri04} estimate that the MPA-JHU sample is complete.
 Star-forming galaxies are separated from other emission-line galaxies using the standard BPT classification \citep*{bal81} below the \citet{kau03} demarcation.
@@
 Sub-classes of spiral structure are identified by weighting each galaxy according to the fraction of votes received in each morphological category.
+}
 
@@
 $N$ is the number of galaxies with plurality classifications for spiral arm multiplicity and pitch angles, and at a cutoff of $p_{bar}=0.4$ for barred/unbarred galaxies.
-$\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit} to data weighted by morphological vote fractions for spiral arm multiplicity and pitch angle, and to subsamples split by morphology for barred/unbarred and merging galaxies.\label{tbl-fits}}
+{\rr $\alpha$ and $\beta$ are fit according to Equation~\ref{eqn-linearfit} to data weighted by morphological vote fractions for spiral arm multiplicity and pitch angle, and to subsamples split by morphology for barred/unbarred and merging galaxies.}\label{tbl-fits}}
 \end{table}
@@
 \noindent where $\alpha$ and $\beta$ represent the slope and offset, respectively.
-The formal uncertainties $\sigma_\alpha$ and $\sigma_\beta$ are taken from the covariance matrix for each least-squares fit (Table~\ref{tbl-fits}).
+{\rr The formal uncertainties $\sigma_\alpha$ and $\sigma_\beta$ are taken from the covariance matrix for each least-squares fit (Table~\ref{tbl-fits}).
 In fitting subsamples selected by morphology, we apply the same fit to all star-forming galaxies, but weighted by the morphological likelihood in the GZ2 data.
@@
 One possibility is that volume-limiting would deal with galaxies in which the dust content is high enough to obscure all emission lines, even in the presence of significant star formation.
-Such galaxies, typically [U]LIRGs, have very low space-densities at $z<0.1$, and typically lack the regular disk structure needed to categorize it for the morphologies considered here.
+Such galaxies, typically [U]LIRGs, have very low space-densities at $z<0.1$, and typically lack the regular disk structure needed to categorize it for the morphologies considered here.}
 
@@
 As previously demonstrated with SDSS data \citep[e.g.,][]{bri04}, there is a tight correlation between $M_\star$ and SFR, with galaxies in the process of quenching lowering their SFR and falling below the trend.
-The relationship extends over at least 3~orders of magnitude in both $M_\star$ and SFR.
+The relationship extends over at least {\rr 3~orders of magnitude} in both $M_\star$ and SFR.
 Fits to the SFMS for all subsamples in this paper are listed in Table~\ref{tbl-fits}.
@@
 For this analysis, galaxies in each mass/SFR bin is weighted by the vote fraction for the morphology being tested.
-The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of the total star-forming disk population.
+{\rr The fit to the star-forming main sequence for all six sub-samples of spiral galaxies split by arm multiplicity tightly follows that of the total star-forming disk population.
 Both the slopes and offsets of each linear fit are consistent within the formal fitting errors in Table~\ref{tbl-fits}.
@@
 The results for the SFMS are qualitatively the same as when using the weighting scheme, although we note that there are too few examples ($N<10$) of either three- or four-armed spirals for a reliable fit.
-The offset of the one-armed spirals above the SFMS is also significantly more pronounced when using high-confidence morphologies.
+The offset of the one-armed spirals above the SFMS is also significantly more pronounced when using high-confidence morphologies.}
 
@@
 We thus also compare the sample standard deviation ($\sigma_{SFR}$) to the star-forming galaxy population over its various morphological subsamples.
-The value of $\sigma_{SFR}$ monotonically decreases with increasing mass over the range $8.0<\log(M/M_\odot)<11.5$.
-For all morphological populations examined in this paper, the widths of their distributions are consistent with the broader population (Figure~\ref{fig-sigma}).
+The value of $\sigma_{SFR}$ monotonically decreases with increasing mass over the range {\rr $8.0<\log(M/M_\odot)<11.5$.
+For all morphological populations examined in this paper}, the widths of their distributions are consistent with the broader population (Figure~\ref{fig-sigma}).
 
@@
 
-We have also examined all the populations of galaxies described above (bars, arm pitch angle, arm multiplicity) and measured the differences when using specific star formation rate ($\textrm{sSFR}\equiv\textrm{SFR}/M_\star$) instead of SFR.
+We have {\rr also examined all the populations of galaxies described above (bars, arm pitch angle, arm multiplicity) and measured the differences when using specific star formation rate ($\textrm{sSFR}\equiv\textrm{SFR}/M_\star$) instead of SFR.
 There is no significant change in any of the morphologically-selected categories as compared to the general SFMS.
+}
 
@@
 \citet{abr14} found that by normalizing galaxies by the stellar mass of the disk alone, the slope of the SFMS is consistent with only a linear trend (removing any dependence on mass).
-Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the intrinsic dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, environment and/or gas accretion history, among other factors \citep{dut10}.
+Although this correction to the disk stellar mass homogenizes the SFMS for disks with a range of $B/T$, the intrinsic dispersion ($\sigma_{SFR}$) of the sequence must be a result of contributions by bars, disk dynamics, halo heating, AGN activity, {\rr environment and/or gas accretion history, among other factors \citep{dut10}.
 Our results show that the neither of the first two factors play dominant roles in controlling $\sigma_{SFR}$, at least as far as major dynamical drivers (such as strong bars or additional arms) are concerned.
@@
 Alternatively, this also agrees with models in which the SFMS is the result of stochastic processes, rather than deterministic physics related to galaxy evolution \citep{kel14b}.
+}
 
@@
 
-We analyze for the first time the detailed structure of disks in large samples of star-forming galaxies in the local Universe as related to their position on the $M_\star$-SFR relation.
+We analyze for the first time the detailed structure of disks in large samples of star-forming galaxies {\rr in the local Universe }as related to their position on the $M_\star$-SFR relation.
 This analysis is made possible by using morphological classifications from the Galaxy~Zoo~2 project.

### 2015-02-09 gz_mainsequence.py
Count mergers below mass limit

@@ -914,6 +914,10 @@ def fracdev(sf_sample):
         data = f[1].data
 
     sf_mergers = data[(data['bpt'] == 1)]
+    
+    with fits.open('%s/mergers/mergers_mpajhu_bpt.fits' % gzm_path) as f:
+        mdata = f[1].data
+    print 'Mergers: %10i' % np.sum((mdata['bpt'] == 1) & (mdata['MEDIAN_MASS'] >= 8.))
 
     axc = fig.add_subplot(111)    # The big subplot
     axc.spines['top'].set_color('none')

### 2015-02-09 paper/mainsequence_morph.tex
Fixed numbers and fit parameters in Table

@@
 \hline						
-SF galaxies  & 48405  & $0.72$  & $-7.08$  &  $7.13\times10^{-6}$  & $6.98\times10^{-4}$  \\
+SF galaxies  & {\rr 48405  }&{\rr $0.72$  }& {\rr $-7.08$  }& {\rr  $7.13\times10^{-6}$  }& {\rr $6.98\times10^{-4}$ } \\
 \hline                                                                                                               
-1 arm        & 289    & $0.74$  & $-7.18$  &  $2.70\times10^{-5}$  & $2.69\times10^{-3}$  \\
-2 arms       & 5641   & $0.78$  & $-7.69$  &  $3.70\times10^{-5}$  & $3.78\times10^{-3}$  \\
-3 arms       & 997    & $0.71$  & $-6.99$  &  $4.49\times10^{-5}$  & $4.65\times10^{-3}$  \\
-4 arms       & 285    & $0.71$  & $-7.05$  &  $4.80\times10^{-5}$  & $4.93\times10^{-3}$  \\
-5+ arms      & 289    & $0.80$  & $-8.11$  &  $7.54\times10^{-5}$  & $7.53\times10^{-3}$  \\
-can't tell   & 2017   & $0.77$  & $-7.72$  &  $4.53\times10^{-5}$  & $4.54\times10^{-3}$  \\
+1 arm        & {\rr 288    }&{\rr $0.74$  }& {\rr $-7.18$  }& {\rr  $2.70\times10^{-5}$  }& {\rr $2.69\times10^{-3}$ } \\
+2 arms       & {\rr 5635   }&{\rr $0.78$  }& {\rr $-7.69$  }& {\rr  $3.70\times10^{-5}$  }& {\rr $3.78\times10^{-3}$ } \\
+3 arms       & {\rr 995    }&{\rr $0.71$  }& {\rr $-6.99$  }& {\rr  $4.49\times10^{-5}$  }& {\rr $4.65\times10^{-3}$ } \\
+4 arms       & {\rr 283    }&{\rr $0.71$  }& {\rr $-7.05$  }& {\rr  $4.80\times10^{-5}$  }& {\rr $4.93\times10^{-3}$ } \\
+5+ arms      & {\rr 286    }&{\rr $0.80$  }& {\rr $-8.11$  }& {\rr  $7.54\times10^{-5}$  }& {\rr $7.53\times10^{-3}$ } \\
+can't tell   & {\rr 2002   }&{\rr $0.77$  }& {\rr $-7.72$  }& {\rr  $4.53\times10^{-5}$  }& {\rr $4.54\times10^{-3}$ } \\
 \hline                                                                                                               
-tight arms   & 3255   & $0.70$  & $-6.99$  &  $1.79\times10^{-3}$  & $1.86\times10^{-1}$  \\
-medium arms  & 4578   & $0.77$  & $-7.62$  &  $6.81\times10^{-3}$  & $6.87\times10^{-1}$  \\
-loose arms   & 1672   & $0.73$  & $-7.08$  &  $5.81\times10^{-3}$  & $5.76\times10^{-2}$  \\
+tight arms   & {\rr 3239   }&{\rr $0.78$  }& {\rr $-7.74$  }& {\rr  $5.50\times10^{-5}$  }& {\rr $5.66\times10^{-3}$ } \\
+medium arms  & {\rr 4564   }&{\rr $0.78$  }& {\rr $-7.68$  }& {\rr  $4.16\times10^{-5}$  }& {\rr $4.21\times10^{-3}$ } \\
+loose arms   & {\rr 1672   }&{\rr $0.78$  }& {\rr $-7.64$  }& {\rr  $3.21\times10^{-5}$  }& {\rr $3.20\times10^{-3}$ } \\
 \hline                                                                                                               
-barred       & 3199   & $0.75$  & $-7.38$  &  $8.53\times10^{-5}$  & $8.42\times10^{-3}$  \\
-unbarred     & 11846  & $0.69$  & $-6.78$  &  $2.91\times10^{-5}$  & $2.89\times10^{-3}$  \\
+barred       & {\rr 3185   }&{\rr $0.76$  }& {\rr $-7.54$  }& {\rr  $8.97\times10^{-5}$  }& {\rr $8.88\times10^{-3}$ } \\
+unbarred     & {\rr 11746  }&{\rr $0.71$  }& {\rr $-6.99$  }& {\rr  $3.39\times10^{-5}$  }& {\rr $3.38\times10^{-3}$ } \\
 \hline                                                                                                                
-merger       & 2978   & --      & $-6.73$  &  --                   & --                   \\
+merger       & {\rr 2951   }&     --       & {\rr $-6.79$  }&       --                    &      --                    \\
 \hline

### 2015-02-09 paper/mainsequence_morph.tex
Fixed the numbers in Table 1 for mass-limited sample

--- 2015-02-09 paper/mainsequence_morph.tex
@@
 \hline                                                                                   
-1 arm        & 289    & $0.74$  & $-7.18$  &  $2.70\times10^{-5}$  & $2.69\times10^{-3}$  \\
-2 arms       & 5641   & $0.78$  & $-7.69$  &  $3.70\times10^{-5}$  & $3.78\times10^{-3}$  \\
-3 arms       & 997    & $0.71$  & $-6.99$  &  $4.49\times10^{-5}$  & $4.65\times10^{-3}$  \\
-4 arms       & 285    & $0.71$  & $-7.05$  &  $4.80\times10^{-5}$  & $4.93\times10^{-3}$  \\
-5+ arms      & 289    & $0.80$  & $-8.11$  &  $7.54\times10^{-5}$  & $7.53\times10^{-3}$  \\
-can't tell   & 2017   & $0.77$  & $-7.72$  &  $4.53\times10^{-5}$  & $4.54\times10^{-3}$  \\
+1 arm        & 288    & $0.74$  & $-7.18$  &  $2.70\times10^{-5}$  & $2.69\times10^{-3}$  \\
+2 arms       & 5635   & $0.78$  & $-7.69$  &  $3.70\times10^{-5}$  & $3.78\times10^{-3}$  \\
+3 arms       & 995    & $0.71$  & $-6.99$  &  $4.49\times10^{-5}$  & $4.65\times10^{-3}$  \\
+4 arms       & 283    & $0.71$  & $-7.05$  &  $4.80\times10^{-5}$  & $4.93\times10^{-3}$  \\
+5+ arms      & 286    & $0.80$  & $-8.11$  &  $7.54\times10^{-5}$  & $7.53\times10^{-3}$  \\
+can't tell   & 2002   & $0.77$  & $-7.72$  &  $4.53\times10^{-5}$  & $4.54\times10^{-3}$  \\
 \hline                                                                                   
-tight arms   & 3255   & $0.70$  & $-6.99$  &  $1.79\times10^{-3}$  & $1.86\times10^{-1}$  \\
-medium arms  & 4578   & $0.77$  & $-7.62$  &  $6.81\times10^{-3}$  & $6.87\times10^{-1}$  \\
-loose arms   & 1672   & $0.73$  & $-7.08$  &  $5.81\times10^{-3}$  & $5.76\times10^{-2}$  \\
+tight arms   & 3239   & $0.78$  & $-7.74$  &  $5.50\times10^{-5}$  & $5.66\times10^{-3}$  \\
+medium arms  & 4564   & $0.78$  & $-7.68$  &  $4.16\times10^{-5}$  & $4.21\times10^{-3}$  \\
+loose arms   & 1672   & $0.78$  & $-7.64$  &  $3.21\times10^{-5}$  & $3.20\times10^{-3}$  \\
 \hline                                                                                   
-barred       & 3199   & $0.75$  & $-7.38$  &  $8.53\times10^{-5}$  & $8.42\times10^{-3}$  \\
-unbarred     & 11846  & $0.69$  & $-6.78$  &  $2.91\times10^{-5}$  & $2.89\times10^{-3}$  \\
+barred       & 3185   & $0.76$  & $-7.54$  &  $8.97\times10^{-5}$  & $8.88\times10^{-3}$  \\
+unbarred     & 11746  & $0.71$  & $-6.99$  &  $3.39\times10^{-5}$  & $3.38\times10^{-3}$  \\
 \hline                                                                                   
-merger       & 2978   & --      & $-6.73$  &  --                   & --                   \\
+merger       & 2951   & --      & $-6.79$  &  --                                          &      --                    \\
 \hline

### 2015-02-11 paper/mainsequence_morph.tex
All data for accepted MNRAS version

@@
 \newcommand{\mytilde}{\textasciitilde}
-
-% Highlight referee response
-\definecolor{titlecol}{rgb}{0,0,1}
-\def\rr{\color{titlecol}}
 
@@
 $^{10}$Kavli IPMU (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-%$^{11}$Department of Physics and Astronomy, University of Alabama, Box 870324, Tuscaloosa, AL 35487, USA \\
 }
@@
 \begin{document}
-\date{Accepted XXXXXXX}
+\date{Accepted 11 Feb 2015}
 \pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}
@@
 
-%How many galaxies are there in the total sample? What is the mass, color, and redshift range?
 The total sample analyzed in this paper consists of 48,405 star-forming galaxies.
@@
 Both the slopes and offsets of each linear fit are consistent within the formal fitting errors in Table~\ref{tbl-fits}.
-%There are too few individual galaxies with confirmed spiral morphologies at lower masses to do a reliable fit; however, the same relation is reproduced for all arm multiplicities at $10^8<M_\star/M_\odot<10^{11}$.
 
@@
 It should be emphasized, though, that 5+-arm spirals represent the smallest morphological group in the sample, and that the associated fit errors in Table~\ref{tbl-fits} are the largest for any multiplicity; simple statistical variance cannot be ruled out as an explanation for the best-fit line to the SFMS.
-
-%One possibility is that this is a consequence of galaxies that have already begun the process of quenching.
-As a result, the star-formation rate is depleted and the contrast of spiral arms against the rest of the disk (which for visual identification is at least in part dependent on bright knots of recent star formation) makes the multiplicity more difficult to identify.
-However, the $(u-r)$ colors of these galaxies (uncorrected for dust extinction) are on average significantly bluer than green-valley late-types as identified in \citet{sch14}.
 
@@
 \begin{figure*}
-%\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
 \includegraphics[angle=0,width=7.0in]{figures/masslim/ms_bar_contour.pdf}
@@
 \begin{figure}
-%\includegraphics[angle=0,width=7.0in]{figures/ms_bar.pdf}
 \includegraphics[angle=0,width=3.5in]{figures/masslim/sigma_mstar.pdf}

### 2015-02-11 gz_mainsequence.py

@@ -1,4 +1,4 @@
-# Branch - make all plots using only a lower limit of M_star = 10**8 M_sun
+# Mass-limited - all data uses only a lower limit of M_star = 10**8 M_sun
 
 import numpy as np
 import time

### 2015-02-11 paper/mainsequence_morph.tex
Added journal macros and fixed figure paths for arXiv submission

@@
 \bibliographystyle{mn2e}
+
+\input macros.tex
 
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_number_weighted_contour.pdf}
+\includegraphics[angle=0,width=7.0in]{ms_arms_number_weighted_contour.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the distribution of all star-forming galaxies in SDSS from the MPA-JHU DR7 catalog.
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_winding.pdf}
+\includegraphics[angle=0,width=7.0in]{ms_arms_winding.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_arms_winding_weighted.pdf}
+\includegraphics[angle=0,width=7.0in]{ms_arms_winding_weighted.pdf}
 \caption{Same as Figure~\ref{fig-winding}, but with colormaps showing all spiral galaxies weighted by the GZ2 vote fractions for ``tight'', ``medium'', and ``loose'' winding spiral arms. 
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_bar_contour.pdf}
+\includegraphics[angle=0,width=7.0in]{ms_bar_contour.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.
@@
 \begin{figure}
-\includegraphics[angle=0,width=3.5in]{figures/masslim/sigma_mstar.pdf}
+\includegraphics[angle=0,width=3.5in]{sigma_mstar.pdf}
 \caption{Width of the star-forming main sequence ($\sigma_{SFR}$) as a function of stellar mass, as measured by the sample standard deviation.
@@
 \begin{figure*}
-\includegraphics[angle=0,width=7.0in]{figures/masslim/ms_mergers_both.pdf}
+\includegraphics[angle=0,width=7.0in]{ms_mergers_both.pdf}
 \caption{Total star formation rate as a function of stellar mass; grayscale colors are the same as in Figure~\ref{fig-number}.
